### 2013-11-14 paper.tex
Initial commit to repository

\documentclass[10pt,final,journal]{IEEEtran}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{url}

\title{Scaling of Electrode-Electrolyte Interface Model Parameters In Phosphate Buffered Saline}
\author{Mark~H.~Jones,~Jonathan~Scott,~\IEEEmembership{Senior Member,~IEEE}}
\begin{document}
\maketitle

\begin{abstract}
We report how the impedance presented by a platinum electrode scales with the concentration of phosphate buffered saline (PBS). 
We find that the constant phase element of the model scales with approximately the log of concentration, whereas the resistivity is inversely proportional. 
Using a novel DC measurement technique we show that the Faradaic response of a platinum electrode, and thus the safe exposure limit, does not scale with concentration below 900\thinspace mV overpotential across a pair of electrodes. 
We comment upon the appropriateness of PBS as a substitute for the spinal cavity of a sheep.
\end{abstract}

\section{Introduction}
There is considerable interest in the electrical modelling of electrodes. \cite{Cogan2008,Troy2006}
In \cite{Franks2005} a linearised model was presented, and in \cite{ScottSingle2013} a non-linear model
suitable for use with the SPICE circuit simulator was presented. The SPICE model usefully characterises an electrode in a given electrolyte with a small number of parameters.
One major reason for the interest in the electrical impedance of electrodes concerns the design of electronics intended for integration into pacemakers, cochlear implants, spinal cord stimulators, etc. The design of successful circuits depends upon a good understanding of external load impedance, while maximisation of battery life is linked to the use of electrodes whose impedance is well understood.
Having a compact model of an electrode in the appropriate electrolyte allows circuit designers to simulate their designs with valid loads. Knowing the effect upon the model of changes in the electrode or electrolyte would allow designers to anticipate circumstances that will affect the load seen by their circuits. Another appeal of a compact model stems from the fact that electrode characteristics are succinctly and objectively represented by the model parameters. These enable direct comparison of different electrodes, or the change in electrode properties over time. For example, in \cite{Kane13} changes in chronically-implanted electrodes are observed but there is no standard quantitative way of presenting the changes. Similarly, while there is a good understanding of what represents safe exposure, a compact model with parameters permits the prediction of the safety of any given stimulus regime.~\cite{Merrill05}

Electrodes in the laboratory are typically tested in a saline solution selected to mimic the circumstances in which they will operate when implanted.
A 0.1X concentration solution of Phosphate Buffered Saline (PBS) is common in the case of Spinal Cord Stimulators (SCS), while 1.0X PBS is considered more representative of the situation in blood.
In this manuscript we report how the parameters of the non-linear model change as the concentration of saline is varied. We place these parameters in context with a biological measurement made in the spinal cavity of a live sheep.

The electrode used in this work is a commercial linear array of eight platinum electrodes intended for SCS implantation called an ``Octrode''.~\cite{StJudeOctrode} A picture of an Octrode is presented in figure~\ref{fig:octrode}.
The electrical interface model of \cite{Franks2005} and \cite{ScottSingle2013} has two parts, a displacement branch and a Faradaic branch.

\begin{figure}
    \begin{center}
    \includegraphics{graphics/StJudeOctrodeDiagram3}
    \end{center}
    \caption{St. Jude Medical Octrode lead comprised of eight coaxial cylindrical platinum electrodes (1mm in diameter, 3mm long) separated by 4mm insulating spacers.}
    \label{fig:octrode}
\end{figure}

\begin{figure}
    \begin{center}
        \includegraphics[width=230pt]{graphics/interfaceSchematic_noMemristive.eps}
    \end{center}
    \caption{Electrical schematic of the electrode-interface impedance model used in this work. $D_{a}$ and $D_{b}$ represent diodes; $CPE$ and $R_{s}$ represent the constant phase element and series resistance respectively.}
    \label{fig:schematic}
\end{figure}

\section{Resistive Network}
The ingredients of the stock solution of PBS used in this study are given in table~\ref{tab:PBSrecipe}.
Six solutions ranging from 1.0X to 0.025X the concentration of this stock solution have been examined. 
The stock solution had a pH of 7.4 and no pH adjustments were made to the derived solutions.

\begin{table}
    \begin{center}
        \begin{tabular}{|r|l|}
            \hline
            $NaCl$ & $8.0\thinspace g$ \\ \hline
            $KCl$ & $0.2\thinspace g$ \\ \hline
            $Na_{2}HPO_{4}$ & $1.44\thinspace g$ \\ \hline
            $KH_{2}PO_{4}$ & $0.24\thinspace g$ \\ \hline
            Distilled Water & $1.0$\thinspace L \\ \hline
        \end{tabular}
    \end{center}
    \caption{PBS stock solution ingredients}
    \label{tab:PBSrecipe}
\end{table}

The electrical impedance between two electrodes in an electrolyte arises from two interface impedances in series with the resistance due to the bulk of the electrolyte itself. To quantify the impedance presented by a single interface we first need to understand the inter-electrode resistances presented by the electrolyte bulk. As there are always two interface impedances between any two electrodes, inter-electrode resistances cannot be measured in isolation. 
In \cite{ScottSingle2013}, a series of transresistance measurements were used in conjunction with a physical description of the electrode geometry to build up a representative network of resistors. Repeating this work, we can then produce a resistor network that connects each of the 8 electrodes, replicating the resistances due to the solution bulk. Transimpedance measurements were taken at each concentration of PBS and the results are presented in figure~\ref{fig:transresistance}.
A numerical fit was made to the two independent scaling parameters ($R_{eri}$ and $R_{sri}$).  The resulting fit and parameter values are presented in figure~\ref{fig:transresistance} and table~\ref{tab:RESparams} respectively.

\begin{figure}
    \begin{center}
        \includegraphics{graphics/pbs_transimpedance_IEEE}
    \end{center}
    \caption{Trans-resistance measurements (markers) used to generate the resistor mesh and the corresponding fit (lines). Red diamonds indicate results where a stimulus is placed across electrodes 1 and 2. Blue circles represent measurements where the stimulus is placed across electrodes 1 and 8. Each trace represents one of six concentrations of PBS, increasing in transresistance magnitude monotonically from 1.0X to 0.025X.}
    \label{fig:transresistance}
\end{figure}

\begin{table}
    \begin{center}
        \begin{tabular}{|r|l|}
            \hline
            $R_{eri}$ & 0.407 / $\sigma$ \\ \hline
            $R_{sri}$ & 3.71 / $\sigma$ \\ \hline
            $R_{li}$ & $R_{eri}$ $3/4$ \\ \hline
            Depth & 5 layers \\ \hline
            Padding & 3 layers \\ \hline
        \end{tabular}
    \end{center}
    \caption{Resistor mesh parameters. $\sigma$ measured in units of $S/cm$}
    \label{tab:RESparams}
\end{table}

\section{Displacement Parameters}
The linear, or small-signal, part of an electrode-electrolyte interface is represented by a Constant Phase Element (CPE) or fractional capacitor. For simulation purposes this element is realised as an array of R-C branches.~\cite{ScottSingle2013,Morrison59,Elwakil10} Measurement of the CPE is made by sweeping the frequency of a sinusoidal stimulus across electrodes 2 and 7 of the Octrode while measuring the voltage between electrodes 2 and 3. The numbering pattern used to identify each of the electrodes on the Octrode is shown in figure~\ref{fig:octrode}.
Measurements made using this configuration allow for the quantification of a single interface impedance in series with the resistance presented by the bulk solution. 
Figures~\ref{fig:CPE_Magnitude} and~\ref{fig:CPE_Phase} show magnitude and phase measurements of the CPE at each concentration.

As shown in the interface model schematic (figure~\ref{fig:schematic}), the interface contains its own internal series resistance ($R_{S}$). The resistance seen in series with the CPE will therefore be the sum of both the resistance due to the bulk resistivity of the fluid and $R_{S}$, to which we will refer as $R_{S+bulk}$.
In figure~\ref{fig:CPE_Magnitude}, the slope and magnitude of the CPE are visible below 1\thinspace Hz whereas $R_{S+bulk}$  dominates above 1\thinspace kHz; it is clear that the two do not scale similarly.
As the impedance of the CPE and $R_{S+bulk}$ are separable with frequency, these measurements can be used to determine the CPE parameters and $R_{S}$.

Figure~\ref{fig:CPE_Scaling} shows measured data and the corresponding fits for both the CPE magnitude at 0.05\thinspace Hz and $R_{S+bulk}$. 
The resulting model parameters $m$, $k$, and $|Z|\thinspace @\thinspace 1Hz$ are shown in table~\ref{tab:CPEparams}. Here we express the CPE offset parameter as $|Z|\thinspace @ \thinspace 1Hz$, but the fits used $|Z|\thinspace @ \thinspace 0.05Hz$, as data points at this frequency are outside the transitional zone where the impedance of the CPE and that of $R_{S+bulk}$ overlap.

From the results shown in figure~\ref{fig:CPE_Magnitude} we observe that the salinity of the electrolyte does not affect the slope of the CPE's impedance and the magnitude shifts relatively little. This suggests that the CPE does not rely on the added ions but they do have an effect, implying that its behaviour is a property of platinum and $H_{2}O$.

\begin{figure}
    \begin{center}
        \includegraphics{graphics/displacement_impedanceVsFrequency_magnitude}
    \end{center}
    \caption{Magnitude of CPE impedance versus frequency of a sine wave stimulus for six concentrations of PBS. Traces represent simulated data while markers represent measured values.}
    \label{fig:CPE_Magnitude}
\end{figure}

\begin{figure}
    \begin{center}
        \includegraphics{graphics/displacement_impedanceVsFrequency_phase}
    \end{center}
    \caption{Phase shift across the CPE versus frequency of a sine wave stimulus for six concentrations of PBS. Traces represent simulated data while markers represent measured values.}
    \label{fig:CPE_Phase}
\end{figure}

\begin{figure}
    \begin{center}
        \includegraphics{graphics/scalingFactors_Displacement_IEEE}
    \end{center}
    \caption{Simulated and measured values of CPE parameters versus concentration of PBS. $|Z|$ is compared at 0.05\thinspace Hz as measured data is unaffected by $R_{S}$ at this frequency.}
    \label{fig:CPE_Scaling}
\end{figure}

\begin{table}
    \begin{center}
        \begin{tabular}{|r|l|}
            \hline
            $m$ & $1.34$ \\ \hline
            $k$ & $1.773$\\ \hline
            $|Z|\: @\: 1Hz$& $3284 \times concentration^{-0.158}$ \\ \hline
            $R_{S}$ & $13.38 \times concentration^{-0.8397} $\\ \hline
        \end{tabular}
    \end{center}
    \caption{Displacement parameter scaling}
    \label{tab:CPEparams}
\end{table}

\section{Faradaic Parameters}

With parameters fitted for the scaling of both the CPE and $R_{S}$ with PBS concentration, we evaluate Faradaic conduction. The interface model uses two reverse connected diodes to reproduce the exponential behaviour of Faradaic current conduction, implied by the Butler-Volmer equation. We wish to measure this conduction by separating it from the displacement behaviour of the CPE. By using a DC measurement technique, as opposed to cyclic measurements, we are able to separate the effects in time. Like a conventional capacitor, when the voltage across the CPE changes, it responds by absorbing or ejecting charge, causing a spike in current. The CPE will draw negligible current once it has settled and in the case of our model we assume the remaining current conduction to be the result of Faradaic processes. The equation governing current conduction in a diode where the forward voltage across the diode, $V_{D}$, is small is
\begin{equation}
    I = i_{0}  e^{V_{D} / n V_{T}}
\end{equation}
where $V_{T}$ is the thermal voltage and is approximately 25\thinspace mV at a temperature of 300\thinspace K. We wish to find how the saturation current ($i_{0}$) and the ideality factor ($n$) scale as the solution salinity is varied.

Faradaic measurements were made using an Agilent E5270B Precision Measurement Mainframe producing a stepped DC voltage stimulus across electrodes 2 and 6 whilst continuously measuring the output current. We commenced with 1.0X concentration of the stock solution (table~\ref{tab:PBSrecipe}). This solution was progressively diluted in factors of two between each measurement. The solution was mixed continuously by inductive stirrer and the electrode remained submerged throughout the entire process.
A single measurement run involved stepping the voltage across electrodes 2 and 7 from 0.5\thinspace V to 1.2\thinspace V in increments of 0.05\thinspace V; this range was previously determined to capture the onset of Faradaic conduction.

In \cite{Cogan2008} it has been noted that results obtained using cyclic voltammetry are dependant on, among other factors, the measurement sweep rate. This indicates a lack of isolation between displacement and Faradaic mechanisms. Our measurements were repeated using wait-times of 4, 16, 32 and 64 seconds between voltage increments, allowing us to determine the effect of sweep rate. From these measurements and a separate investigation\footnote{A separate measurement of the response of the CPE to voltage increments is shown in figure~\ref{fig:CPE_currentVsTime}. We concluded that the measurement rate did not significantly affect results when using a wait-time of 64 seconds or greater when the applied voltage across both interfaces is beyond 0.7\thinspace V. These measurements were made in still solution and we expect that stirring will cause the CPE to come to equilibrium sooner. The wait time used between increments for this data was 10,000 seconds, of which only the first 250 seconds are shown. We believe these results give confidence to our assumption that a wait-time of 64 seconds is ``long enough''.} we concluded that a wait-time of 64 seconds was sufficient.  
\begin{figure}
    \begin{center}
        \includegraphics{graphics/CPE_currentVsTime}
    \end{center}
    \caption{Current versus time after a stepped voltage increment across a pair of interfaces. Time before 64 seconds is highlighted in grey. Measurements were taken with a wait time of 10,000 seconds between increments.}
    \label{fig:CPE_currentVsTime}
\end{figure}

In figure~\ref{fig:StepResponse_Faradaic}, electrical current measurements are plotted against time (solid lines). Each spike marks the point at which the voltage is incremented. We expect the peak current to be much higher than is shown since each measurement point is the average of 300 samples taken over 1 second. Note that the amount of charge absorbed by the CPE increases with concentration of PBS, but the current for each concentration converges to approximately the same value. Dotted lines have been added that link the electrical current measurements taken 10 seconds after each increment for 0.125X PBS (lower trace) and 1.0X PBS (upper trace). These dotted traces show results typical of cyclic methods, where the electrode overpotential is never constant. This illustrates the benefit of using DC measurements when measuring Faradaic currents.

Figure~\ref{fig:faradaic_logCurrentVsVoltage} shows the settled currents plotted on a log scale, versus the voltage applied across the electrodes. This uses the same data as the previous figure but has been processed so that each point represents the average of the final 24 current measurements at each step. Below 0.9\thinspace V it appears that the concentration of the solution had no identifiable effect on Faradaic conduction as the traces are not monotonic with concentration in this region.  Between 0.9\thinspace V and 1.05\thinspace V (concentration dependent) a transition occurs which results in current conduction becoming dependent on solution concentration.
Above 1.05\thinspace V the traces diverge showing clear dependence upon concentration.

\begin{figure}
    \begin{center}
        \includegraphics{graphics/currentTimeFaradaicCPE_Stacked_IEEE}
    \end{center}
    \caption{Current conduction with 0.05\thinspace V stepped voltage increments from 0.5\thinspace V to 0.9V. Each voltage is held for 64 seconds before being further incremented. Dotted lines connect current measurements occurring 10 seconds after an increment.}
    \label{fig:StepResponse_Faradaic}
\end{figure}

We attribute the change in behaviour between 0.9\thinspace V and 1.05\thinspace V to a transition to diffusion-controlled conduction.
We hypothesise that the charging of the CPE draws available ions to the electrode, creating a layer of high ionic concentration at the surface irrespective of that of the solution bulk. It is this layer that is subsequently consumed by the Faradaic reactions at a rate dependent on the log of the electrode overpotential.  The effect of bulk solution concentration while this layer has formed is negligible until the point at which the layer is consumed faster than it can be replenished. At this stage, and with increasing overpotential, the Faradaic conduction is governed by diffusion of ions from the bulk into the layer, the rate of which increases with the ion concentration in the bulk. We believe this explains the divergence of conduction with concentration between 0.9\thinspace V and 1.05\thinspace V and why there is no observable dependence on bulk ion concentration beforehand.

This hypothesis intimately links the Faradaic component to the CPE, where the latter is a precursor to the former. For the purposes of our model, we are content with placing a limit of 0.9\thinspace V across the pair of interfaces and using the assumption that Faradaic conduction does not change with concentration. Further investigation into modelling this relationship is needed. We hope to publish this in a follow-up paper.

\begin{figure}
    \begin{center}
        \includegraphics{graphics/currentVoltage_logY_IEEE}
    \end{center}
    \caption{Faradaic conduction as a function of voltage applied across electrodes 2 and 7. Samples shown were taken between 40 and 64 seconds after each voltage increment. Error bars indicate spread in measurement results, where 95\% of samples lie within the bars.}
    \label{fig:faradaic_logCurrentVsVoltage}
\end{figure}

\begin{figure}
    \begin{center}
        \includegraphics{graphics/faradaic_currentVsTime_IEEE}
    \end{center}
    \caption{Current versus time for 1.0X PBS overlaid with simulated results of the interface model's response to increasing voltage steps. The model used for simulation includes the CPE, diodes and $R_{S}$.}
    \label{fig:faradaic_currentVsTime}
\end{figure}

\begin{figure}
    \begin{center}
        \includegraphics{graphics/faradaic_currentVsVoltage_IEEE}
    \end{center}
    \caption{Simulated and measured response of the interface model to increasing voltage steps. Measurement points show current values taken at the $64^{th}$ second after each voltage increment.}
    \label{fig:faradaic_currentVsVoltage}
\end{figure}

\begin{table}
    \begin{center}
        \begin{tabular}{|r|l|}
            \hline
            $i0$ & 2.757e-12\\ \hline
            $n$ & 1.36\\ \hline
        \end{tabular}
    \end{center}
    \caption{Faradaic parameters}
    \label{tab:FaradaicParams}
\end{table}

Parameter values for $i_{0}$ and $n$ are presented in table~\ref{tab:FaradaicParams}. These parameters were found by fitting the diode equation to the results shown in figure~\ref{fig:faradaic_currentVsVoltage}.

\section{In-vivo measurements of sheep}

We now test the claim that 0.1X PBS is a reasonable representation of cerebral spinal fluid (CSF).
The displacement measurements were repeated in a live sheep. The sheep was prepared and anaesthetised using the procedures described in \cite{Parker2013}. The measurements are presented in figures~\ref{fig:displacement_sheepCPEMagnitude} and~\ref{fig:displacement_sheepCPEPhase} on top of the array of traces for saline taken from figures~\ref{fig:CPE_Magnitude}
and~\ref{fig:CPE_Phase}. 
Although it is clear that there are complications in vivo, a 0.25X PBS saline offers a good approximation to the resistive part of the trace.
The reactive part would be better modelled by a solution of less than 0.025X concentration.

\begin{figure}
    \begin{center}
        \includegraphics{graphics/displacement-withSheep_impedanceVsFrequency_magnitude}
    \end{center}
    \caption{Comparison between the magnitude of CPE in live sheep (blue circles) against each of the PBS traces from figure~\ref{fig:CPE_Magnitude} (grey lines) and a simulated fit to the sheep data (red trace).}
    \label{fig:displacement_sheepCPEMagnitude}
\end{figure}

\begin{figure}
    \begin{center}
        \includegraphics{graphics/displacement-withSheep_impedanceVsFrequency_phase}
    \end{center}
    \caption{Comparison between the phase response of the CPE in live sheep (blues circles) against each of the PBS traces taken from figure~\ref{fig:CPE_Phase} (grey lines) and a simulated fit to the sheep data (red trace).}
    \label{fig:displacement_sheepCPEPhase}
\end{figure}

\section{Conclusion}

We have used the parameters of a compact electrical model of an implantable electrode as a way of objectively comparing scenarios.
We have measured how changing the concentration of PBS affects the parameters. 
We have drawn direct relationships with concentration sufficient to predict interface characteristics at arbitrary dilutions of PBS. 
We found that the CPE moves much more slowly with concentration whereas the resistance moved almost linearly. 
Using DC measurements we conclude that the salinity of the bulk does not affect Faradaic conduction until a threshold voltage is reached. We hypothesise that this is because the CPE is setting the effective concentration of ions in a localised volume surrounding each electrode. In-vivo measurements of the CPE in sheep spine showed that no single concentration of PBS matches both the CPE and the resistive characteristics at once. Nevertheless, 0.1X PBS is a good compromise.

\begin{thebibliography}{99}

    \bibitem{Cogan2008}
    Stuart~F.~Cogan,
    ``Neural Stimulation and Recording Electrodes'',
    Annu. Rev. Biomed. Eng. 2008. pp275--309.

    \bibitem{Troy2006}
    John~B.~Troy, Donald~R.~Cantrell, Allen~Taflove and Rodney~S.~Ruoff
    ``Modeling the electrode-electrolyte interface for recording and stimulating electrodes'',
    {\em Proceedings of the 28th IEEE EMBS Annual International Conference}
    New York City, USA, Aug. 30, 2006, pp879--881.

\bibitem{Franks2005}
W.~Franks, Iwan~Schenker, Patrik~Schmutz, and Andreas Hierlemann,
``Impedance Characterization and Modeling of Electrodes for Biomedical Applications'',
\emph{IEEE Transactions on Biomedical Engineering},
vol.~52 no.~7, July 2005, pp1295--1302.

\bibitem{ScottSingle2013}
Jonathan Scott and Peter Single,
``Compact Nonlinear Model of an Implantable Electrode Array for Spinal Cord Stimulation (SCS)'',
to be published in
{\em IEEE Transactions on Biomedical Circuits and Systems},
DOI: 10.1109/TBCAS.2013.2270179, 2013.

\bibitem{Kane13}
Sheryl~R.~Kane, Stuart~F.~Cogan, Julia~Ehrlich, Timothy~D.~Plante, Douglas~B.~McCreery and Philip~R.~Troyk,
``Electrical Performance of Penetrating Microelectrodes Chronically Implanted in Cat Cortex``,
{\em IEEE Transactions on Biomedical Engineering},
vol.~60 no.~8, August 2013, pp2153--2160.

\bibitem{Merrill05}
Daniel~R.~Merrill, Maron Bikson and John~G.~R.\ Jefferys,
``Electrical stimulation of excitable tissue: design of efficacious and safe protocols'',
Journal of Neuroscience Methods 141 (2005), pp171--198.

\bibitem{StJudeOctrode}
St.~Jude Medical, Octrode Percutaneous Lead for Neuromodulation,
\url{http://www.sjmneuropro.com/Products/US/Percutaneous-Leads.aspx},
retrieved December 2012.

\bibitem{Morrison59}
Ralph Morrison,
``RC Constant-Argument Driving-Point Admittances'',
{\em IRE Transactions on Circuit Theory},
September 1959, pp310--317.

\bibitem{Elwakil10}
Ahmed~S.~Elwakil,
``Franctional-Order Circuits and Systems: An Emerging Interdisciplinary Research Area''
IEEE Circuits and Systems Magazine, Fourth quarter, 2010, pp40--50.

\bibitem{Parker2013}
Parker J.L., Karantonis D.M., Single P.S., Obradovic M., Laird J., Gorman R.B., Ladd L.A., Cousins M.J.,
``Electrically Evoked Compound Action Potentials Recorded From the Sheep Spinal Cord'', 
Neuromodulation 2013; 16: 295--303.

\end{thebibliography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{graphics/JBSatNICTA.jpg}}]{Jonathan Scott}
(M'80--SM'99) is the Foundation Professor in
Electronic Engineering at the University of Waikato in Hamilton, New
Zealand.  From 1998 to 2006 he was with the Hewlett-Packard,
now Agilent Technologies, Microwave Technology Center in Santa Rosa,
where he was responsible for advanced measurement systems.  In 1997 and
1998 he was Chief Engineer at RF Technology in Sydney.  He was with The
University of Sydney in the Department of Electrical Engineering prior
to 1997.  He is a Professorial Fellow of Macquarie
University.  Professor Scott has authored over 100 refereed
publications and holds a number of patents.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{graphics/MarkJones-Aug13.jpg}}]{Mark Jones}
graduated with a BSc in Physics and a Masters in Microwave Electronics from the University of Waikato in 2008 and 2009.
He is currently studying towards his PhD.
\end{IEEEbiography}

\end{document}

### 2013-11-14 paper.tex
Modified abstract to be over 100 words (now 105). Added information about animal ethics. Reworded part abouot testing PBS as substitute for CSF (as advised by Peter). Changed paper format to match that of Jonathans submission to TBioCAS. Changed blurb about myself to match that of similar transactions. Added acknowledgements for UOW and Saluda.

@@
-\documentclass[10pt,final,journal]{IEEEtran}
+\documentclass[journal, a4paper]{IEEEtran}
+
+\usepackage{cite}
+\usepackage{amsmath}
 \usepackage{amssymb}
@@
 
+\begin{document}
+
 \title{Scaling of Electrode-Electrolyte Interface Model Parameters In Phosphate Buffered Saline}
-\author{Mark~H.~Jones,~Jonathan~Scott,~\IEEEmembership{Senior Member,~IEEE}}
-\begin{document}
+
+\author{Mark~H.~Jones,~Jonathan~Scott,~\IEEEmembership{Senior Member,~IEEE}
+
+\thanks{Mark~H.~Jones is with the School of Electronic Engineering, University of Waikato, New Zealand, e-mail: markjones112358@gmail.com.}%
+
+\thanks{Jonathan Scott is with the School of Electronic Engineering, University of Waikato, New Zealand, e-mail: jonathanscott@iee.org.}
+
+}
+
+\markboth{Transactions on Biomedical Circuits and Systems}
+{Jones \MakeLowercase{\textit{et al.}}: Scaling of Electrode-Electrolyte Interface Model Parameters in Phosphate Buffered Saline\...}
 \maketitle
@@
 Using a novel DC measurement technique we show that the Faradaic response of a platinum electrode, and thus the safe exposure limit, does not scale with concentration below 900\thinspace mV overpotential across a pair of electrodes.
-We comment upon the appropriateness of PBS as a substitute for the spinal cavity of a sheep.
+We compare objective measurements made in saline to those made in the spinal cavity of live sheep. We comment upon the appropriateness of using PBS as a substitute for living sheep.
 \end{abstract}
 
+\begin{IEEEkeywords}
+    Electrical stimulation, Bioelectric phenomena, Biophysics, Bioimpedance, Biomedical electrodes, Biomedical measurements, Implantable biomedical devices
+\end{IEEEkeywords}
+
 \section{Introduction}
-There is considerable interest in the electrical modelling of electrodes. \cite{Cogan2008,Troy2006}
+\IEEEPARstart{T}{here} is considerable interest in the electrical modelling of electrodes. \cite{Cogan2008,Troy2006}
 In \cite{Franks2005} a linearised model was presented, and in \cite{ScottSingle2013} a non-linear model
@@
     \begin{center}
-        \includegraphics[width=230pt]{graphics/interfaceSchematic_noMemristive.eps}
+        \includegraphics[width=230pt]{graphics/interfaceSchematic_noMemristive}
     \end{center}
@@
     \end{center}
-    \caption{Trans-resistance measurements (markers) used to generate the resistor mesh and the corresponding fit (lines).
+    \caption{Transresistance measurements (markers) used to generate the resistor mesh and the corresponding fit (lines).
 Red diamonds indicate results where a stimulus is placed across electrodes 1 and 2.
@@
 
-We now test the claim that 0.1X PBS is a reasonable representation of cerebral spinal fluid (CSF).
-The displacement measurements were repeated in a live sheep.
-The sheep was prepared and anaesthetised using the procedures described in \cite{Parker2013}.
+We now test the claim that 0.1X PBS is a reasonable representation of the spine of a living sheep.
+The displacement measurements were repeated inside the spinal canal of a live sheep, just outside the dura containing CSF.
+The sheep were prepared and anaesthetised using the procedures described in \cite{Parker2013} under the Animal Care and Ethics Committee approval of the Royal North Shore Hospital.
+The study complied with the Australian Code of Practice for the Care and Use of Animals for Scientific Purposes.
 The measurements are presented in figures~\ref{fig:displacement_sheepCPEMagnitude} and~\ref{fig:displacement_sheepCPEPhase} on top of the array of traces for saline taken from figures~\ref{fig:CPE_Magnitude}
@@
 Nevertheless, 0.1X PBS is a good compromise.
+
+\section*{Acknowledgment}
+The authors wish to acknowledge the The University of Waikato for financial support and Saluda Medical for the use of facilities and equipment.
 
@@
 \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{graphics/MarkJones-Aug13.jpg}}]{Mark Jones}
-graduated with a BSc in Physics and a Masters in Microwave Electronics from the University of Waikato in 2008 and 2009.
-He is currently studying towards his PhD.
+received the B.Sc. degree in Physics in 2008 and the M.E. degree in Microwave Electronics in 2009 from The University of Waikato, Hamilton, New Zealand.
+He is working towards a Ph.D. in Electrical Engineering, also at The University of Waikato.
 \end{IEEEbiography}

### 2013-11-20 paper.tex
Added sheep spine diagram to paper

@@
 
+\begin{figure}
+    \begin{center}
+        \includegraphics{graphics/sheepSpine2}
+    \end{center}
+    \caption{Cross section of a sheep spine showing the position of the electrode array relative to the dura. Spotted regions represent cross sectioned vertebrae.}
+    \label{fig:sheepSpine}
+\end{figure}
+
 We now test the claim that 0.1X PBS is a reasonable representation of the spine of a living sheep.
-The displacement measurements were repeated inside the spinal canal of a live sheep, just outside the dura containing CSF.
+The displacement measurements were repeated inside the spinal canal of a live sheep, just outside the dura as shown in figure~\ref{fig:sheepSpine}.
 The sheep were prepared and anaesthetised using the procedures described in \cite{Parker2013} under the Animal Care and Ethics Committee approval of the Royal North Shore Hospital.

### 2013-11-21 paper.tex
Submitted version. Reverted Inkscape graphics to origionals.

@@
 
-\author{Mark~H.~Jones,~Jonathan~Scott,~\IEEEmembership{Senior Member,~IEEE}
+\author{Mark~H.~Jones and Jonathan~Scott,~\IEEEmembership{Senior Member,~IEEE}
 
@@
 
-\thanks{Jonathan Scott is with the School of Electronic Engineering, University of Waikato, New Zealand, e-mail: jonathanscott@iee.org.}
+\thanks{Jonathan Scott is with the School of Electronic Engineering, University of Waikato, New Zealand, e-mail: jonathanscott@ieee.org.}
 
@@
     \begin{center}
-    \includegraphics{graphics/StJudeOctrodeDiagram3}
+    \includegraphics{graphics/StJudeOctrodeDiagram}
     \end{center}
@@
     \begin{center}
-        \includegraphics{graphics/sheepSpine2}
+        \includegraphics{graphics/sheepSpine}
     \end{center}

### 2014-01-12 paper.tex
Added reviewers comments with space to respond to each

@@
 \usepackage{url}
+\usepackage[usenames, dvipsnames]{color}
 
@@
 
+\section*{Reviewer Comments}
+
+\subsection*{Reviewer 1}
+
+{\color{blue}
+I am not very enthusiastic about his paper as it does not contain many novel or original ideas and finding.
+On the electrochemistry side it is superficial and falls back behind published state of the art and textbook knowledge.\\
+{\color{OliveGreen} Our response}\\
+
+1. The interface model as such is not new and has been published extensively.\\
+{\color{OliveGreen} Our response}\\
+
+2.
+The authors do not at all comment on interface polarization, which is particularly important under DC conditions.
+As soon as an electrode carries current, such phenomena become important and relevant.\\
+{\color{OliveGreen} Our response}\\
+
+3.
+To assess the resistivity or impedance of a material between two electrodes, one normally uses a 4-electrode setup with injection of current through the two outer electrodes, while measuring a voltage between the inner ones.
+This is particularly relevant for the measurements in Fig.
+3 and the related and subsequent text.\\
+{\color{OliveGreen} Our response}\\
+
+4.
+The authors never mention the origin of any Faradaic contribution at the electrodes.
+What is the electro- or redox-chemistry that the authors assume to happen??
+Gas formation at the electrodes, electrolysis of the saline, i.e., hydrogen and oxygen formation??\\
+{\color{OliveGreen} Our response}\\
+
+5. Figure 5 is not referenced anywhere in the text. Also the blue variations in the curves are hardly visible.\\
+{\color{OliveGreen} Our response}\\
+
+6. Since the electrode model includes two back-to-back diodes, I think it would be valuable to sweep the voltage from -1.2V to +1.2V.\\
+{\color{OliveGreen} Our response}\\
+
+7.
+There is a big difference between blue dots and red curve in Fig.
+10, except for the "voltage increment time" and "64 seconds after increment".
+This indicates to me that the CPE model is NOT that accurate, as the settling curve is highly correlated to the CPE parameters.\\
+{\color{OliveGreen} Our response}\\
+}
+
+\subsection*{Reviewer 2}
+
+{\color{blue}
+In this manuscript, the authors report how the non-linear electrode-electrolyte interface model parameters change as a function of saline solution concentration.
+This is a very interesting and important subject that could be potentially of great importance for readers of IEEE Transactions on Biomedical Circuits ans Systems.
+The manuscript is well written and adequately referenced.
+However, the reviewer would like to pose a few questions to the authors to clarify some  issues in the manuscript, which should be addressed.\\
+{\color{OliveGreen} Our response}\\
+
+page 2, in text/ table II. The scaling parameters and their meanings should be described more comprehensively. They remain somewhat unclear and meaningless to reader.\\
+{\color{OliveGreen} Our response}\\
+
+page 2 Measurement of the CPE. What was the current density used in EIS measurements?
+What is the effect of chosen current density on CPE impedance (Fig. 5)?
+In addition,  measurement apparatus information is fully lacking.\\
+{\color{OliveGreen} Our response}\\
+
+page 2, line 52. "the magnitude shifts relatively little". However, In Fig. 4, logaritmic scale is used, and the change from 1.0X to 0.025X is almost 50k at the lowest frequencies. 
+please clarify this point.\\
+{\color{OliveGreen} Our response}\\
+
+page 3, in text/ table III. The parameters (m, k..) and their meanings should be described more comprehensively, as well.\\
+{\color{OliveGreen} Our response}\\
+
+Figure 9 (page 4).
+There is a clear difference in behavior of faradic conduction between 0.25X (red curve) and 0.5X (green curve).
+Transient current occur at 0.95V (<0.25X PBS) changing to occur at 1.0 V (>0.5X PBS).
+This behavior has not discussed in manuscript at all.
+Please revise it.\\
+{\color{OliveGreen} Our response}\\
+
+page 4. Referencing (in the text) to the Fig. 10 is lacking (?).\\
+{\color{OliveGreen} Our response}\\
+
+Finally, and most importantly, the part of in vivo measurements are very limited since only one spinal channel measurement has been performed.
+My opinion is that this manuscript could be even better without this uncertain (n=1) result and thus I recommend to leave this part out.\\
+{\color{OliveGreen} Our response}\\
+}
+
+\subsection*{Reviewer 3}
+
+{\color{blue}
+Authors
+The aim of this paper, to find a SPICE model of implanted electrodes, is important and the results presented in the paper are interesting.
+However, as it stands the paper is not well written and must be revised.
+The weaknesses of the paper are an unclear structure, with results and discussion mixed, poor attention to detail and inaccurate use of words.\\
+{\color{OliveGreen} Our response}\\
+
+Concerning the experiments, I have two points to make.
+
+1.
+You do not explain how the impedance measurements have been made (Figs 4, 5 13 & 14).
+I want to know how much charge was being applied to these electrodes at low frequencies (e.g.
+0.05 Hz): what potential excursion occurred was it really a ``small signal''?\\
+{\color{OliveGreen} Our response}\\
+
+2.
+I think that the classical view of the electrochemistry of Pt in saline (as, for example, expressed in your ref 1), is that the electrolysis reactions (oxygen and hydrogen evolution) start with a potential difference of about 1.4V.
+Below this p.d., the likeliest reaction is reduction of oxygen at the cathode which could accompany oxygen evolution from water at the anode.
+Your paper lacks any consideration of the chemistry but this is a important fault in the stepped-current experiment.
+Was the solution in equilibrium with air before the experiment?
+If this is a model for electrodes in vivo, should not the PBS have been in equilibrium with gas with the in vivo partial pressure of oxygen?
+I suggest that you repeat this experiment, at least (i) under air, (ii) under nitrogen, & perhaps (iii) under in vivo partial pressure of oxygen.
+The stirring arrangements ought to be exactly described too because liquid flow may be critical.\\
+{\color{OliveGreen} Our response}\\
+
+Other points
+
+1. P1, top RH col. ``0.1X'' ought to be explained when you first use this form.\\
+{\color{OliveGreen} Our response}\\
+
+2.
+Should the resistor model of the volume conductor from [4] be shown in this paper?
+It would make the paper easier to understand for your reader if you showed the model.
+If you are not going to do so, you might help them by saying something like ``Readers are advised to see [4] to understand the meaning of the parameters in Table II''.\\
+{\color{OliveGreen} Our response}\\
+
+3. You say (p2 line 43) that there are 2 independent scaling factors. Is Rli independent or not? If not, why input it in Table II?\\
+{\color{OliveGreen} Our response}\\
+
+4.
+In the legend of Fig 4 and in paragraph below, you say this is magnitude of the CPE.
+But surely it is not since the sloping lines become horizontal.
+It is the CPE in series with something.
+But what is this something?
+Is it the total series resistance or have you already subtracted the volume resistance (found in section II)?\\
+{\color{OliveGreen} Our response}\\
+
+5.
+The previous point is complicated by your statement that Rs (Fig 2) is an addition to the volume resistance (p2 RH col).
+Why is Rs necessary?
+Is it because the resistance values at high frequencies in Fig 4 are not consistent with the values from the resistor network found in section II?
+If so, this would be very interesting and I would like you to bring this out.\\
+{\color{OliveGreen} Our response}\\
+
+6. P2, col 2, line 24: why 2 & 7?\\
+{\color{OliveGreen} Our response}\\
+
+7.
+P2, col 2, line 53: ``implying that its behaviour is a property of Pt and water''.
+Previous authors have thought this showed that the CPE depended on the geometry (surface roughness) of the electrode.
+Did you mean that, or were you thinking of the electrochemical properties of Pt.
+Please make clearer.\\
+{\color{OliveGreen} Our response}\\
+
+8. You do not explain why, in eq 1, you want to use this form. Why nVt? I suppose it isso you can use a standard SPICE form rather than this suits the data. Is that right?\\
+{\color{OliveGreen} Our response}\\
+
+9. P3, col 2, line 31: why 2 and 6?\\
+{\color{OliveGreen} Our response}\\
+
+10. P3, col 2, line 36. I guess you mean what is usually called a Magnetic Stirrer. Not ``inductive'' surely?\\
+{\color{OliveGreen} Our response}\\
+
+11. P3 footnote. ``The response of the CPE'': this is confusing! Surely this is the response of a pair of electrodes? The CPE is an element of your model.\\
+{\color{OliveGreen} Our response}\\
+
+12. Fig 11 legend ``Simulated and measured response of the interface model''. Surely you mean ``Simulated response of the interface model compared to measurement from the electrodes''?\\
+{\color{OliveGreen} Our response}\\
+
+13. P5, col 2, line 46 ``the CPE is setting''. Again, you are confusing an element of your model with reality.\\
+{\color{OliveGreen} Our response}\\
+
+14.
+P5, col 1, line 49 ``a 0.25X PBS is a good model''.
+This seems a very feeble comment on an interesting result.
+The series resistance part of the in vivo magnitude is a good fit to the 0.25X curve and the slope of the CPS is very similar (though you have exaggerated this by extrapolating nearly 2 decades in frequency below the lowest-frequency measurement).
+But the impedance at low frequencies is about three times too high.
+How do you explain that?
+It cannot be because of the bone and other high-resistivity structures around the electrodes (which would have an effect on the high frequency asymptote).
+So what is it?
+Did you measure the electrodes again in PBS after removing from the sheep?
+Troyk published an interesting paper with measurement from electrodes in brain of zebra finches which showed that anomalous characteristics in vivo vanished as soon as the electrodes were returned to PBS, implying that the phenomenon was not due to some biofilm deposited on the electrodes.\\
+{\color{OliveGreen} Our response}\\
+}
+
+\subsection*{Reviewer 4}
+{\color{blue}
+In this manuscript, the authors studied the impedance of a commercial electrode array as a function of concentration of phosphate buffered saline (PBS), both through simulation and empirical measurements, and compared those results to the impedance measured when the electrode array was implanted into a sheep's spinal cavity.
+From this comparison, they concluded that the current practice of testing spinal cord stimulator in 0.1x of physiologically normal saline is adequate but suggest that no single concentration of PBS captures the frequency dependence of the in vivo measured impedance.\\
+{\color{OliveGreen} Our response}\\
+
+Overall, the paper was brief and to the point, which in this case is actually a determent instead of a benefit.
+Much of the underlying theory and development of parameters appear without informing the reader of their purpose or how they were calculated and/or measured.
+For example, the parameters in Table 2 (and reported to be in Figure 3) are not explained and what their relationship to the remainder of the manuscript is not provided.
+To make this manuscript more approachable to a wider audience, I recommend the authors more fully develop Sections II, III, and IV.
+Further, they should explain their testing in terms of standard electrochemical characterization, detailing their counter, working, and reference electrodes used in measuring impedance.
+As part of this expansion, the references should be increased beyond the present ten references.
+Although their current references include clearly important electrode characterization references (Cogan, Merrill et.
+al, & Kane et.
+al), the information contained in these references are not effectively used to support the authors’ work.\\
+{\color{OliveGreen} Our response}\\
+
+Technically, I found one issue with this paper.
+In Figure 11, the x-axis labels should have 2 digits after the decimal.
+As presently shown, each of the labels 0.6, 0.7, ..., 1.0 are repeated twice on the axis.
+Presumably, the second version of the labels should be 0.65, 0.75, ..., 1.05.\\
+{\color{OliveGreen} Our response}\\
+}
 \end{document}

### 2014-01-13 paper.tex
Update paper.tex
Added more comments to reviewers comments

@@
 On the electrochemistry side it is superficial and falls back behind published state of the art and textbook knowledge.\\
-{\color{OliveGreen} Our response}\\
+{\color{OliveGreen}
+    {\color{Red} Research textbook knowledge and published state of the art relating to electro chemistry in our area.}
+    No response yet.
+}\\
 
 1. The interface model as such is not new and has been published extensively.\\
-{\color{OliveGreen} Our response}\\
+{\color{OliveGreen} 
+    {\color{Red} Review and discuss existing interface models}
+    No response yet.
+}\\
 
@@
 As soon as an electrode carries current, such phenomena become important and relevant.\\
-{\color{OliveGreen} Our response}\\
+{\color{OliveGreen}
+    {\color{Red} Is polarisation a separate mechanism from double layer formation?
+If so, can we address?
+Polarisation will be just as important in cyclic measurement techniques where the cycle time is low.
+Does anyone understand polarisation sufficiently to remove it from measurements?
+Is polarisation not just remaining charge in a layer around an electrode, is it not just the double layer?}
+    No response yet.
+}\\
 
@@
 3 and the related and subsequent text.\\
-{\color{OliveGreen} Our response}\\
+{\color{OliveGreen} 
+    {\color{Red} I don't understand what use doing this would be.
+All voltage dropped between two end electrodes, voltage proportional to total impedance between electrodes.
+The most use you could get from this would be to find how much is dropped across a single interface, which is exactly what we are doing.}
+    No response yet.    
+}\\
 
@@
 Gas formation at the electrodes, electrolysis of the saline, i.e., hydrogen and oxygen formation??\\
-{\color{OliveGreen} Our response}\\
+{\color{OliveGreen}
+    {\color{Red} My assumption is that we don't give a crap what it is, whatever it is, we're modelling it. If you want to know that, look elsewhere.}
+    No response yet.
+}\\
 
 5. Figure 5 is not referenced anywhere in the text. Also the blue variations in the curves are hardly visible.\\
-{\color{OliveGreen} Our response}\\
+{\color{OliveGreen} 
+    {\color{Red} Enhance color variation in Figures 4 and 5 and make a reference to Figure 5}
+    No response yet.
+}\\
 
 6. Since the electrode model includes two back-to-back diodes, I think it would be valuable to sweep the voltage from -1.2V to +1.2V.\\
-{\color{OliveGreen} Our response}\\
+{\color{OliveGreen}
+    {\color{Red} The diodes are identical, this is moving into polarisation territory again.
+In effect, they are both being used (one by + and other by -).
+I don't know what to say about this.
+We wanted to make all the measurements happen in as little time as possible.
+We have data from sweeps in the other direction, not DC though.}
+    No response yet.
+}\\
 
@@
 This indicates to me that the CPE model is NOT that accurate, as the settling curve is highly correlated to the CPE parameters.\\
-{\color{OliveGreen} Our response}\\
+{\color{OliveGreen}
+    {\color{Red} This is true, try and pinpoint exactly why this is happening. Why does the CPE perform so well in the CPE frequency response plots yet so poorly in the Faradaic part?}
+    No response yet.
+}\\
 }
@@
 However, the reviewer would like to pose a few questions to the authors to clarify some  issues in the manuscript, which should be addressed.\\
-{\color{OliveGreen} Our response}\\
 
 page 2, in text/ table II. The scaling parameters and their meanings should be described more comprehensively. They remain somewhat unclear and meaningless to reader.\\
-{\color{OliveGreen} Our response}\\
+{\color{OliveGreen}
+    {\color{Red} Pull in more explination from JonathanScott2013 relating to the resistor mesh}
+    No response yet.
+}\\
 
@@
 In addition,  measurement apparatus information is fully lacking.\\
-{\color{OliveGreen} Our response}\\
+{\color{OliveGreen}
+
+}\\
 

### 2014-01-13 paper.tex
Finishd adding my pre-response-comments/thoughts to the reviewers comments

@@
 
-\thanks{Jonathan Scott is with the School of Electronic Engineering, University of Waikato, New Zealand, e-mail: jonathanscott@ieee.org.}
+\thanks{Jonathan Scott is with the School of Electronic Engineering, University of Waikato, New Zealand.}
 
@@
 What is the effect of chosen current density on CPE impedance (Fig. 5)?
+{\color{OliveGreen}
+    {\color{Red} Estimate current density and investigate possible effects}
+    No response yet.
+}
+
 In addition,  measurement apparatus information is fully lacking.\\
 {\color{OliveGreen}
-
+    {\color{Red} Describe instruments used in measurements or make reference to Jonathans paper}
+    No response yet.
 }\\
@@
 please clarify this point.\\
-{\color{OliveGreen} Our response}\\
+{\color{OliveGreen}
+    {\color{Red} ``shifts relatively little'' meaning at this impedance 50k is small compared to total resistance''}
+    No response yet.
+}\\
 
 page 3, in text/ table III. The parameters (m, k..) and their meanings should be described more comprehensively, as well.\\
-{\color{OliveGreen} Our response}\\
+{\color{OliveGreen} 
+    {\color{Red} Describe the parameters m and k in the resistor network (pull from Jonathans paper and sub-references)}
+    No response yet.
+}\\
 
@@
 Please revise it.\\
-{\color{OliveGreen} Our response}\\
+{\color{OliveGreen}
+    {\color{Red} Should be easy to do, perhaps I make a second graph that shows more of the time data}
+    No response yet.
+}\\
 
 page 4. Referencing (in the text) to the Fig. 10 is lacking (?).\\
-{\color{OliveGreen} Our response}\\
+{\color{OliveGreen}
+    {\color{Red} Include a reference to Figure 10 in the document}
+    No response yet.
+}\\
 
@@
 My opinion is that this manuscript could be even better without this uncertain (n=1) result and thus I recommend to leave this part out.\\
-{\color{OliveGreen} Our response}\\
+{\color{OliveGreen}
+    {\color{Red} Leave sheep in but perhaps show the second measurement (day 1) if possible (4th reviewer found sheep correlation to PBS result interesting).
+Would a separate sheep measurement graph be of use showing all sheep results?
+Or do we hold onto this for the better phantom paper?}
+    No response yet.
+}\\
 }
@@
 The weaknesses of the paper are an unclear structure, with results and discussion mixed, poor attention to detail and inaccurate use of words.\\
-{\color{OliveGreen} Our response}\\
+{\color{OliveGreen}
+    {\color{Red} Revise poor use of words (perhaps relating to model elements/physical elements). Perhaps separate the results and discussion sections.} 
+    No response yet.
+}\\
 
@@
 0.05 Hz): what potential excursion occurred was it really a ``small signal''?\\
-{\color{OliveGreen} Our response}\\
+{\color{OliveGreen}
+    {\color{Red} Estimate the amount of charge being injected in each of the measurements (fits with the current density)}
+    No response yet.
+}\\
 
@@
 The stirring arrangements ought to be exactly described too because liquid flow may be critical.\\
-{\color{OliveGreen} Our response}\\
+{\color{OliveGreen}
+    {\color{Red} This represents a lot of work to redo the measurements.
+Perhaps we make it clear that we don't know the electrochemistry side, that it's simply out of our depth, and any hypothesis we draw based on electrochemistry may harm the validity of our work.
+If we explain more exactly the proceedure we took so as to be more repeatable and hint that we're not interested at this point on the electrochemistry, that we only wish to make the model behave like the solution.}
+    No response yet.
+}
 
@@
 1. P1, top RH col. ``0.1X'' ought to be explained when you first use this form.\\
-{\color{OliveGreen} Our response}\\
+{\color{OliveGreen}
+    {\color{Red} Replace ``A 0.1X concentration'' with ``a one-tenth concentration...'' and explain exactly what that means.}
+    No response yet.
+}\\
 
@@
 If you are not going to do so, you might help them by saying something like ``Readers are advised to see [4] to understand the meaning of the parameters in Table II''.\\
-{\color{OliveGreen} Our response}\\
+{\color{OliveGreen}
+    {\color{Red} Leave until the end, if we have the space then we put it in, otherwise put a better reference to ScottSingle2013}
+    No response yet.
+}\\
 
 3. You say (p2 line 43) that there are 2 independent scaling factors. Is Rli independent or not? If not, why input it in Table II?\\
-{\color{OliveGreen} Our response}\\
+{\color{OliveGreen}
+    {\color{Red} Mention that $R_{li}$ is not independent because of the geometric simplification of the resistor network.
+Mention that for more detail we suggest viewers read the relevant section of ScottSingle2013}
+    No response yet.
+}\\
 
@@
 Is it the total series resistance or have you already subtracted the volume resistance (found in section II)?\\
-{\color{OliveGreen} Our response}\\
+{\color{OliveGreen}
+    {\color{Red} Reword the caption of Fig. 4 to include the series resistance.}
+    No response yet.
+}\\
 
@@
 If so, this would be very interesting and I would like you to bring this out.\\
-{\color{OliveGreen} Our response}\\
+{\color{OliveGreen} 
+    {\color{Red} His reasoning is correct, it is because the impedance does not match at high freq.
+I had the graph with dotted lines to show the difference that Rs made.
+Jonathan, you thought this was too messy and it was removed, should it be added back in again?}
+    No response yet.
+}\\
 
 6. P2, col 2, line 24: why 2 & 7?\\
-{\color{OliveGreen} Our response}\\
+{\color{OliveGreen}
+    {\color{Red} Explain more clearly why electrodes 2 and 7 were chosen (to avoid end effects)}
+    No response yet.
+}\\
 
@@
 Please make clearer.\\
-{\color{OliveGreen} Our response}\\
+{\color{OliveGreen}
+    {\color{Red} We aren't sure of either but further work into the surface area of the electrode via ottonisation should reveal whether surface area is a factor - read: followup publication}
+    No response yet.
+}\\
 
 8. You do not explain why, in eq 1, you want to use this form. Why nVt? I suppose it isso you can use a standard SPICE form rather than this suits the data. Is that right?\\
-{\color{OliveGreen} Our response}\\
+{\color{OliveGreen} 
+    {\color{Red} Investigate other forms, comment on why this has been chosen}
+    No response yet.
+}\\
 
 9. P3, col 2, line 31: why 2 and 6?\\
-{\color{OliveGreen} Our response}\\
+{\color{OliveGreen}
+    {\color{Red} Took resistance measurements of lead and electrode 2 is open circuit inside the electrode. Must have meant 3 and 7, due to damaged electrode 2}
+    No response yet.
+}\\
 
 10. P3, col 2, line 36. I guess you mean what is usually called a Magnetic Stirrer. Not ``inductive'' surely?\\
-{\color{OliveGreen} Our response}\\
+{\color{OliveGreen} 
+    {\color{Red} What I originally thought, I don't know where inductive stirrer came from}
+    No response yet.
+}\\
 
 11. P3 footnote. ``The response of the CPE'': this is confusing! Surely this is the response of a pair of electrodes? The CPE is an element of your model.\\
-{\color{OliveGreen} Our response}\\
+{\color{OliveGreen} 
+    {\color{Red} This must form part of the inaccurate use of words comment. It's not right to say response of a pair of electrodes since there are other effects. Reword.}
+    No response yet.
+}\\
 
 12. Fig 11 legend ``Simulated and measured response of the interface model''. Surely you mean ``Simulated response of the interface model compared to measurement from the electrodes''?\\
-{\color{OliveGreen} Our response}\\
+{\color{OliveGreen}
+    {\color{Red} Yes, this is better. Replace with this.}
+    No response yet.
+}\\
 
 13. P5, col 2, line 46 ``the CPE is setting''. Again, you are confusing an element of your model with reality.\\
-{\color{OliveGreen} Our response}\\
+{\color{OliveGreen}
+    {\color{Red} Correct, maybe a diargam of the hypothesis is required - nobody seemed to dispute the hypothesis. Check there is no ``textbook knowledge'' explanation for this beforehand.}
+    No response yet.
+}\\
 
@@
 Troyk published an interesting paper with measurement from electrodes in brain of zebra finches which showed that anomalous characteristics in vivo vanished as soon as the electrodes were returned to PBS, implying that the phenomenon was not due to some biofilm deposited on the electrodes.\\
-{\color{OliveGreen} Our response}\\
+{\color{OliveGreen}
+    {\color{Red} True, a feeble comment on PBS match.
+It may be worth noting the phase of measured data in sheep indicating that the sheep itself was reactive.
+There may be data at those lower points (to justify extrapolating), check.
+Have we measured the electrodes again since inserting into the sheep, I think we have but check.
+Read the paper by Troyk, comment on applicability.
+Maybe there is test data between sheep in saline showing the electrodes returning to normal, check.}.
+    No response yet.
+}\\
 }
@@
 From this comparison, they concluded that the current practice of testing spinal cord stimulator in 0.1x of physiologically normal saline is adequate but suggest that no single concentration of PBS captures the frequency dependence of the in vivo measured impedance.\\
-{\color{OliveGreen} Our response}\\
 
@@
 For example, the parameters in Table 2 (and reported to be in Figure 3) are not explained and what their relationship to the remainder of the manuscript is not provided. 
+{\color{OliveGreen}
+    {\color{Red} Explain parameters in table two better or refer readers to ScottSingle2013}
+    No response yet.
+}
 To make this manuscript more approachable to a wider audience, I recommend the authors more fully develop Sections II, III, and IV.
 Further, they should explain their testing in terms of standard electrochemical characterization, detailing their counter, working, and reference electrodes used in measuring impedance.
+{\color{OliveGreen}
+    {\color{Red} Try to include any relevant electrochemical information, find out what that is first}
+    No response yet.
+}
 As part of this expansion, the references should be increased beyond the present ten references.
@@
 al), the information contained in these references are not effectively used to support the authors’ work.\\
-{\color{OliveGreen} Our response}\\
+{\color{OliveGreen}
+    {\color{Red} Perhaps Troyk could be added. A search for textbook knowledge and more published state of the art should uncover more references}
+    No response yet.
+}\\
 
@@
 Presumably, the second version of the labels should be 0.65, 0.75, ..., 1.05.\\
-{\color{OliveGreen} Our response}\\
+{\color{OliveGreen}
+    {\color{Red} Definitely, how did I miss that?}
+    No response yet.
+}\\
 }

### 2014-01-13 paper.tex
Enumerated tasks and updated note on reviewer 1

@@
 {\color{OliveGreen}
+    Item 1\\
     {\color{Red} Research textbook knowledge and published state of the art relating to electro chemistry in our area.}
@@
 {\color{OliveGreen}
+    Item 2\\
     {\color{Red} Review and discuss existing interface models}
@@
 {\color{OliveGreen}
+    Item 3\\
     {\color{Red} Is polarisation a separate mechanism from double layer formation?
@@
 {\color{OliveGreen} 
+    Item 4\\
     {\color{Red} I don't understand what use doing this would be.
@@
 {\color{OliveGreen}
-    {\color{Red} My assumption is that we don't give a crap what it is, whatever it is, we're modelling it. If you want to know that, look elsewhere.}
+    Item 5\\
+    {\color{Red} Do we wish to get into this?
+Perhaps we could touch on it (after reviewing electrochemistry literature) but leave it loose and mention that it is not our intention to completely understand the mechanisims at the chemical level, rather to compare an available model with measurements and comment.}
     No response yet.
@@
 {\color{OliveGreen} 
+    Item 6\\
     {\color{Red} Enhance color variation in Figures 4 and 5 and make a reference to Figure 5}
@@
 {\color{OliveGreen}
+    Item 7\\
     {\color{Red} The diodes are identical, this is moving into polarisation territory again.
@@
 {\color{OliveGreen}
+    Item 8\\
     {\color{Red} This is true, try and pinpoint exactly why this is happening. Why does the CPE perform so well in the CPE frequency response plots yet so poorly in the Faradaic part?}
@@
 {\color{OliveGreen}
+    Item 9\\
     {\color{Red} Pull in more explination from JonathanScott2013 relating to the resistor mesh}
@@
 {\color{OliveGreen}
+    Item 10\\
     {\color{Red} Estimate current density and investigate possible effects}
@@
 {\color{OliveGreen}
+    Item 11\\
     {\color{Red} Describe instruments used in measurements or make reference to Jonathans paper}
@@
 {\color{OliveGreen}
+    Item 12\\
     {\color{Red} ``shifts relatively little'' meaning at this impedance 50k is small compared to total resistance''}
@@
 {\color{OliveGreen} 
+    Item 13\\
     {\color{Red} Describe the parameters m and k in the resistor network (pull from Jonathans paper and sub-references)}
@@
 {\color{OliveGreen}
+    Item 14\\
     {\color{Red} Should be easy to do, perhaps I make a second graph that shows more of the time data}
@@
 {\color{OliveGreen}
+    Item 15\\
     {\color{Red} Include a reference to Figure 10 in the document}
@@
 {\color{OliveGreen}
+    Item 16\\ 
     {\color{Red} Leave sheep in but perhaps show the second measurement (day 1) if possible (4th reviewer found sheep correlation to PBS result interesting).
@@
 {\color{OliveGreen}
+    Item 17\\
     {\color{Red} Revise poor use of words (perhaps relating to model elements/physical elements). Perhaps separate the results and discussion sections.} 
@@
 {\color{OliveGreen}
+    Item 18\\
     {\color{Red} Estimate the amount of charge being injected in each of the measurements (fits with the current density)}
@@
 {\color{OliveGreen}
+    Item 19\\
     {\color{Red} This represents a lot of work to redo the measurements.
@@
 {\color{OliveGreen}
+    Item 20\\
     {\color{Red} Replace ``A 0.1X concentration'' with ``a one-tenth concentration...'' and explain exactly what that means.}
@@
 {\color{OliveGreen}
+    Item 21\\
     {\color{Red} Leave until the end, if we have the space then we put it in, otherwise put a better reference to ScottSingle2013}
@@
 {\color{OliveGreen}
+    Item 22\\
     {\color{Red} Mention that $R_{li}$ is not independent because of the geometric simplification of the resistor network.
@@
 {\color{OliveGreen}
+    Item 23\\
     {\color{Red} Reword the caption of Fig. 4 to include the series resistance.}
@@
 {\color{OliveGreen} 
+    Item 24\\
     {\color{Red} His reasoning is correct, it is because the impedance does not match at high freq.
@@
 {\color{OliveGreen}
+    Item 25\\
     {\color{Red} Explain more clearly why electrodes 2 and 7 were chosen (to avoid end effects)}
@@
 {\color{OliveGreen}
+    Item 26\\
     {\color{Red} We aren't sure of either but further work into the surface area of the electrode via ottonisation should reveal whether surface area is a factor - read: followup publication}
@@
 {\color{OliveGreen} 
+    Item 27\\
     {\color{Red} Investigate other forms, comment on why this has been chosen}
@@
 {\color{OliveGreen}
+    Item 28\\
     {\color{Red} Took resistance measurements of lead and electrode 2 is open circuit inside the electrode. Must have meant 3 and 7, due to damaged electrode 2}
@@
 {\color{OliveGreen} 
+    Item 29\\
     {\color{Red} What I originally thought, I don't know where inductive stirrer came from}
@@
 {\color{OliveGreen} 
+    Item 30\\
     {\color{Red} This must form part of the inaccurate use of words comment. It's not right to say response of a pair of electrodes since there are other effects. Reword.}
@@
 {\color{OliveGreen}
+    Item 31\\
     {\color{Red} Yes, this is better. Replace with this.}
@@
 {\color{OliveGreen}
+    Item 32\\
     {\color{Red} Correct, maybe a diargam of the hypothesis is required - nobody seemed to dispute the hypothesis. Check there is no ``textbook knowledge'' explanation for this beforehand.}
@@
 {\color{OliveGreen}
+    Item 33\\
     {\color{Red} True, a feeble comment on PBS match.
@@
 {\color{OliveGreen}
+    Item 34\\
     {\color{Red} Explain parameters in table two better or refer readers to ScottSingle2013}
@@
 {\color{OliveGreen}
+    Item 35\\
     {\color{Red} Try to include any relevant electrochemical information, find out what that is first}
@@
 {\color{OliveGreen}
+    Item 36\\
     {\color{Red} Perhaps Troyk could be added. A search for textbook knowledge and more published state of the art should uncover more references}
@@
 {\color{OliveGreen}
+    Item 37\\
     {\color{Red} Definitely, how did I miss that?}

### 2014-01-21 paper.tex
Item: 6 - Edited paper to include a clearer reference to Figure 5

@@
 Measurements made using this configuration allow for the quantification of a single interface impedance in series with the resistance presented by the bulk solution.
-Figures~\ref{fig:CPE_Magnitude} and~\ref{fig:CPE_Phase} show magnitude and phase measurements of the CPE at each concentration.
+Figure~\ref{fig:CPE_Magnitude} shows the magnitude of the measured response of each of the six PBS concentrations accompanied by simulation results.
+Figure~\ref{fig:CPE_Phase} shows the phase response for the same measurements, again with the simulated response at each concentration.
+The simulated responses are generated using the optimised parameter values presented in Table~\ref{tab:CPEparams}.
+Those values were chosen as they give the closest match to the measured data.
 

### 2014-01-22 paper.tex
Added maximum and minimum current density figures to CPE measurement

@@
 Measurements made using this configuration allow for the quantification of a single interface impedance in series with the resistance presented by the bulk solution.
+Current density during measurements peaked at $11.5\thinspace A/m^{2}$ at 10\thinspace kHz in 1.0X PBS and fell as low as $0.0141\thinspace A/m^{2}$ at 50\thinspace mHz in 0.025X PBS.
 Figure~\ref{fig:CPE_Magnitude} shows the magnitude of the measured response of each of the six PBS concentrations accompanied by simulation results.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Check that these are in the right order!!!
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\bibitem{Weiland2000}
+Weiland~James~D. and Anderson~David~J.,
+``Chronic Neural Stimulation with Thin-Film, Iridium Oxide Electrodes'',
+{\em IEEE Transactions on Biomedical Circuits and Systems},
+vol.~47 no.~7, July 2000, pp911--918
+
 \end{thebibliography}
@@
     {\color{Red} Estimate current density and investigate possible effects}
-    No response yet.
+    Maximum and minimum current density figures added. No comment on effect formed yet. No response yet.
 }

### 2014-01-23 paper.tex
Updated explination of mesh parameters, including R_{sri} being independant. Fixed error mesh parameter table.

@@
 As there are always two interface impedances between any two electrodes, inter-electrode resistances cannot be measured in isolation.
+
 In \cite{ScottSingle2013}, a series of transresistance measurements were used in conjunction with a physical description of the electrode geometry to build up a representative network of resistors.
-Repeating this work, we can then produce a resistor network that connects each of the 8 electrodes, replicating the resistances due to the solution bulk.
-Transimpedance measurements were taken at each concentration of PBS and the results are presented in figure~\ref{fig:transresistance}.
-A numerical fit was made to the two independent scaling parameters ($R_{eri}$ and $R_{sri}$).
+The network in that paper was defined using five parameters: $R_{eri}$, $R_{lri}$, $R_{li}$, mesh depth, and edge depth.
+Readers are advised to read that paper to understand the interpretation of these model parameters.
+Repeating that work, a resistor network that connects each of the eight   electrodes is has been constructed, mimicking the resistances due to the solution bulk.
+The mesh depth and padding values of five columns and three rows, respectively, has been taken directly from \cite{ScottSingle2013}.
+A numerical fit was made to the two independent scaling parameters $R_{eri}$ and $R_{li}$
+\footnote{The values of $R_{eri}$ and $R_{sri}$ are defined by the lengths of the electrode and inter-electrode spacers respectively as described in \cite{ScottSingle2013}.
+The two parameters are proportional to each other by the ratio of their lengths.
+Hence, we define $R_{sri}$ to be 3/4 that of $R_{eri}$ making it a dependant parameter.}.
 The resulting fit and parameter values are presented in figure~\ref{fig:transresistance} and table~\ref{tab:RESparams} respectively.
@@
             $R_{eri}$ & 0.407 / $\sigma$ \\ \hline
-            $R_{sri}$ & 3.71 / $\sigma$ \\ \hline
-            $R_{li}$ & $R_{eri}$ $3/4$ \\ \hline
+            $R_{sri}$ & $R_{eri}$ $3/4$ \\ \hline
+            $R_{li}$ & 3.71 / $\sigma$ \\ \hline
             Depth & 5 layers \\ \hline
@@
 Current density during measurements peaked at $11.5\thinspace A/m^{2}$ at 10\thinspace kHz in 1.0X PBS and fell as low as $0.0141\thinspace A/m^{2}$ at 50\thinspace mHz in 0.025X PBS.
+The stimulus waveform was set at 300\thinspace mV (peak) at each measurement point.
 Figure~\ref{fig:CPE_Magnitude} shows the magnitude of the measured response of each of the six PBS concentrations accompanied by simulation results.
@@
     {\color{Red} Estimate current density and investigate possible effects}
-    Maximum and minimum current density figures added. No comment on effect formed yet. No response yet.
+    Maximum and minimum current density during displacement current measurement added. No comment on effect formed yet. No response yet.
 }
@@
     {\color{Red} Estimate the amount of charge being injected in each of the measurements (fits with the current density)}
-    No response yet.
+    Added current density and peak stimulus voltage information to displacement current measurement. Still needs total charge transfer for both CPE and Faradaic.
 }\\

### 2014-01-29 paper.tex
Item 29: Fixed description of inductive stirrer
Item 32: Changed references to CPE in conclusion

@@
 This solution was progressively diluted in factors of two between each measurement.
-The solution was mixed continuously by inductive stirrer and the electrode remained submerged throughout the entire process.
+The solution was mixed continuously using a standard laborotary grade magnetic stirrer and the electrode remained submerged throughout the entire process.
 A single measurement run involved stepping the voltage across electrodes 2 and 7 from 0.5\thinspace V to 1.2\thinspace V in increments of 0.05\thinspace V; this range was previously determined to capture the onset of Faradaic conduction.
@@
 We have used the parameters of a compact electrical model of an implantable electrode as a way of objectively comparing scenarios.
-We have measured how changing the concentration of PBS affects the parameters.
+We have measured how changing the concentration of PBS affects the parameters of this model.
 We have drawn direct relationships with concentration sufficient to predict interface characteristics at arbitrary dilutions of PBS.
-We found that the CPE moves much more slowly with concentration whereas the resistance moved almost linearly.
+We found that the magnitude of the CPE element moves much more slowly with concentration whereas the resistance moved almost linearly.
 Using DC measurements we conclude that the salinity of the bulk does not affect Faradaic conduction until a threshold voltage is reached.
-We hypothesise that this is because the CPE is setting the effective concentration of ions in a localised volume surrounding each electrode.
-In-vivo measurements of the CPE in sheep spine showed that no single concentration of PBS matches both the CPE and the resistive characteristics at once.
+We hypothesise that this is because the double-layer sets the effective concentration of ions in a localised volume surrounding each electrode.
+In-vivo measurements of platinum electrodes in sheep spine showed that no single concentration of PBS matches both the CPE and the resistive characteristics at once.
 Nevertheless, 0.1X PBS is a good compromise.

### 2014-01-29 paper.tex
Added responses to already completed items

@@
     {\color{Red} Enhance color variation in Figures 4 and 5 and make a reference to Figure 5}
-    No response yet.
+    Graphs redrawn with a wider range of shading to help identify traces.
 }\\
@@
     {\color{Red} What I originally thought, I don't know where inductive stirrer came from}
-    No response yet.
+    Changed mention of inductive stirrer to magnetic stirrer.
 }\\
@@
     {\color{Red} Correct, maybe a diargam of the hypothesis is required - nobody seemed to dispute the hypothesis. Check there is no ``textbook knowledge'' explanation for this beforehand.}
-    No response yet.
+    Changed references to the CPE model element in the conclusion to the electrical double layer.
 }\\

### 2014-01-29 paper.tex
Item 31: Reworded caption for figure 11

@@
     \end{center}
-    \caption{Simulated and measured response of the interface model to increasing voltage steps. Measurement points show current values taken at the $64^{th}$ second after each voltage increment.}
+    \caption{Simulated response of the interface model compared to measurement from the electrodes with a stepped voltage overpotential.
+Measurement points show current values taken at the $64^{th}$ second after each voltage increment.}
     \label{fig:faradaic_currentVsVoltage}
@@
     {\color{Red} Yes, this is better. Replace with this.}
-    No response yet.
+    Yes, that is better - thank you.
 }\\

### 2014-02-03 paper.tex
Item 30: Removed reference to 'Response of CPE in the footnote explaining the 64 second waittime'

@@
 Our measurements were repeated using wait-times of 4, 16, 32 and 64 seconds between voltage increments, allowing us to determine the effect of sweep rate.
-From these measurements and a separate investigation\footnote{A separate measurement of the response of the CPE to voltage increments is shown in figure~\ref{fig:CPE_currentVsTime}.
-We concluded that the measurement rate did not significantly affect results when using a wait-time of 64 seconds or greater when the applied voltage across both interfaces is beyond 0.7\thinspace V.
-These measurements were made in still solution and we expect that stirring will cause the CPE to come to equilibrium sooner.
-The wait time used between increments for this data was 10,000 seconds, of which only the first 250 seconds are shown.
-We believe these results give confidence to our assumption that a wait-time of 64 seconds is ``long enough''.} we concluded that a wait-time of 64 seconds was sufficient.
+From these measurements and those of a separate investigation\footnote{We took measurements of the interface's response to voltage steps when left to settle for 10 000 seconds, of which the first 250\thinspace seconds are shown in figure~\ref{fig:CPE_currentVsTime}.
+Those measurements show a trend of decreasing current stabalisation time as the overpotential steps increase.
+Sixty four seconds after stepping from 0.64\thinspace V to 0.72\thinspace V, the current has stabalised to $95\%$ of its value at 10\,000 seconds.
+At overpotential steps for higher voltages, the settling time is further reduced.
+These measurements were made in still solution and we expect that stirring will reduce the time to equilibrium.} we concluded that a wait-time of 64 seconds was sufficient.
 \begin{figure}
@@
     {\color{Red} This must form part of the inaccurate use of words comment. It's not right to say response of a pair of electrodes since there are other effects. Reword.}
-    No response yet.
+    Removed reference to the CPE element and have better quantified the settling period in that footnote.
 }\\

### 2014-02-03 paper.tex
Item 23: Reworded the caption of Figure 4 to more accuratly describe the situation

@@
     \end{center}
-    \caption{Magnitude of CPE impedance versus frequency of a sine wave stimulus for six concentrations of PBS. Traces represent simulated data while markers represent measured values.}
+    \caption{Magnitude of interfacial impedance between electrodes 2 and 7 against the frequency of a sine wave stimulus for six concentrations of PBS.
+The slope of the CPE is visible the left, whereas the resistance due to the solution bulk appears on the right.
+Traces represent simulated data while markers represent measured values.}
     \label{fig:CPE_Magnitude}
@@
     \end{center}
-    \caption{Phase shift across the CPE versus frequency of a sine wave stimulus for six concentrations of PBS. Traces represent simulated data while markers represent measured values.}
+    \caption{Phase data of interfacial impedance across electrodes 2 and 7 against frequency of a sine wave stimulus. Traces represent simulated data while markers represent measured values.}
     \label{fig:CPE_Phase}
@@
     {\color{Red} Reword the caption of Fig. 4 to include the series resistance.}
-    No response yet.
+    Thank you, have reworded the caption in Figure 4 to more accuratly describe the situation.
 }\\

### 2014-02-04 paper.tex
Item 37: Regraphed figure 11 to have proper number of decimal places on axes
Item 20: Amended used of 0.1X before explaining its meaning

@@
 Electrodes in the laboratory are typically tested in a saline solution selected to mimic the circumstances in which they will operate when implanted.
-A 0.1X concentration solution of Phosphate Buffered Saline (PBS) is common in the case of Spinal Cord Stimulators (SCS), while 1.0X PBS is considered more representative of the situation in blood.
+A solution of Phosphate Buffered Saline (PBS) diluted to one-tenth concentration (0.1X) is common in the case of Spinal Cord Stimulators (SCS), while full concentration (1.0X) PBS is considered more representative of the situation in blood.
 In this manuscript we report how the parameters of the non-linear model change as the concentration of saline is varied.
@@
     \begin{center}
-        \includegraphics{graphics/faradaic_currentVsTime_IEEE}
+        \includegraphics{graphics/faradaic_currentVsTimeIEEE}
     \end{center}
@@
     \begin{center}
-        \includegraphics{graphics/faradaic_currentVsVoltage_IEEE}
+        \includegraphics{graphics/faradaic_currentVsVoltageIEEE}
     \end{center}
@@
     {\color{Red} Replace ``A 0.1X concentration'' with ``a one-tenth concentration...'' and explain exactly what that means.}
-    No response yet.
+    Yes, thank you, see amendment.
 }\\

### 2014-02-04 paper.tex
Item 11: Added details of instruments used to conduct measurements

@@
 Six solutions ranging from 1.0X to 0.025X the concentration of this stock solution have been examined.
-The stock solution had a pH of 7.4 and no pH adjustments were made to the derived solutions.
+The pH of the stock solution was measured (EDT Instruments BA-350) and was found to have pH of 7.4. No pH adjustments were made to the derived solutions.
 
@@
 Readers are advised to read that paper to understand the interpretation of these model parameters.
-Repeating that work, a resistor network that connects each of the eight   electrodes is has been constructed, mimicking the resistances due to the solution bulk.
+Repeating that work, a resistor network that connects each of the eight electrodes is constructed, mimicking the resistances due to the solution bulk.
 The mesh depth and padding values of five columns and three rows, respectively, has been taken directly from \cite{ScottSingle2013}.
@@
 The resulting fit and parameter values are presented in figure~\ref{fig:transresistance} and table~\ref{tab:RESparams} respectively.
+Measurements of the inter-electrode impedance were made using a Tektronix TPS2014 DSO with four fully isolated and floating channels; an Agilent 33220A Function Generator; and a desktop PC controlling the instruments via Python 2.7.
 
@@
 The stimulus waveform was set at 300\thinspace mV (peak) at each measurement point.
+The measurement insturments used are the same as those used to measure the inter-electrode resistance.
 Figure~\ref{fig:CPE_Magnitude} shows the magnitude of the measured response of each of the six PBS concentrations accompanied by simulation results.
@@
 
-Faradaic measurements were made using an Agilent E5270B Precision Measurement Mainframe producing a stepped DC voltage stimulus across electrodes 2 and 6 whilst continuously measuring the output current.
+Faradaic measurements were made using an Agilent E5270B Precision Measurement Mainframe producing a stepped DC voltage stimulus across electrodes [TODO: Item 28] 2 and 6 whilst continuously measuring the output current.
 We commenced with 1.0X concentration of the stock solution (table~\ref{tab:PBSrecipe}).
@@
     {\color{Red} Describe instruments used in measurements or make reference to Jonathans paper}
-    No response yet.
+    Added details of the instruments used to conduct inter-electrode resistance measurements and clarified thier reuse for displacement measurements.
 }\\

### 2014-02-04 paper.tex
No item, added reference

@@
 
+It has been suggested that the primary coupling mechanism between platinum electrodes and phisiological saline is the reversable evolution of gas, probably oxygen, at the platinum surface, which dissolves without bubble formation.\cite{Greatbatch1969} Understanding exact mechanism of displacement or Faradaic charge transfer at the electrode surface is beyond the scope of this work, instead we wish to characterise the electrode/electrolyte system in terms of an electrical model.
+The model separates the Faradaic and displacement characteristics into separate circuit elements, namely the diode and CPE, however we do not suggest that these conduction mechanisims are physically separate.
+
 \begin{figure}
@@
 \section{Resistive Network}
-The ingredients of the stock solution of PBS used in this study are given in table~\ref{tab:PBSrecipe}.
-Six solutions ranging from 1.0X to 0.025X the concentration of this stock solution have been examined.
-The pH of the stock solution was measured (EDT Instruments BA-350) and was found to have pH of 7.4. No pH adjustments were made to the derived solutions.
+Six solutions ranging from 1.0X to 0.025X the concentration of a stock PBS solution have been examined.
+The ingredients of that stock solution are given in table~\ref{tab:PBSrecipe}.
+The pH level of the stock was measured, using a calibrated EDT Instruments BA-350 pH meter, to have a pH of 7.4. No pH adjustments were made to the derived solutions.
 
@@
 The CPE will draw negligible current once it has settled and in the case of our model we assume the remaining current conduction to be the result of Faradaic processes.
+{\color{blue} In \cite{Greatbatch1969} it is shown that the stirring of an air-saturated solution of physiological saline reduces the settling time of platinum electrodes to stimulus transients; with both situations eventually settling to the same impedance.}
 The equation governing current conduction in a diode where the forward voltage across the diode, $V_{D}$, is small is
@@
 This solution was progressively diluted in factors of two between each measurement.
-The solution was mixed continuously using a standard laborotary grade magnetic stirrer and the electrode remained submerged throughout the entire process.
+The solution was mixed continuously using a standard laborotary grade magnetic stirrer.
+The solution was in equlibriumm with air prior to and during measurement and the electrodes remained submerged at all times.
 A single measurement run involved stepping the voltage across electrodes 2 and 7 from 0.5\thinspace V to 1.2\thinspace V in increments of 0.05\thinspace V; this range was previously determined to capture the onset of Faradaic conduction.
@@
 At overpotential steps for higher voltages, the settling time is further reduced.
-These measurements were made in still solution and we expect that stirring will reduce the time to equilibrium.} we concluded that a wait-time of 64 seconds was sufficient.
+These measurements were made in still solution and we expect stirring will further reduce settling time.} we concluded that a wait-time of 64 seconds was sufficient.
 \begin{figure}
@@
 retrieved December 2012.
+
+\bibitem{Greatbatch1969}
+W.~Greatbatch, B.~Piersma, F.~D.~Shannon, and S.W.~Calhoon, S. W.
+``Polarization phenomena relating to physiological electrodes'',
+Annals of the New York Academy of Sciences,
+167(2), 1969 pp722-744.
 
@@
     {\color{Red} Estimate the amount of charge being injected in each of the measurements (fits with the current density)}
-    Added current density and peak stimulus voltage information to displacement current measurement. Still needs total charge transfer for both CPE and Faradaic.
+    Instrumentation for CPE measurements have been added.
+I have also added current density and peak stimulus voltage information to displacement current measurement.
+[TODO: Calculate and add total charge transfer for both CPE and Faradaic].
 }\\

### 2014-02-05 paper.tex
Coloured edits in document. Inserted references to newly-found literature

@@
 Electrodes in the laboratory are typically tested in a saline solution selected to mimic the circumstances in which they will operate when implanted.
+{
+    \color{blue}
+    % Item 20
 A solution of Phosphate Buffered Saline (PBS) diluted to one-tenth concentration (0.1X) is common in the case of Spinal Cord Stimulators (SCS), while full concentration (1.0X) PBS is considered more representative of the situation in blood.
-In this manuscript we report how the parameters of the non-linear model change as the concentration of saline is varied.
-We place these parameters in context with a biological measurement made in the spinal cavity of a live sheep.
+}
+In this manuscript we report how the parameters of a non-linear model change as the concentration of saline is varied.
+{\color{blue} We refine a series of measurements compatible with commercially available medical electrodes in physiological saline that allow us to describe the impedance with minimal parameters.} We place these parameters in context with a biological measurement made in the spinal cavity of a live sheep.
 
@@
 The electrical interface model of \cite{Franks2005} and \cite{ScottSingle2013} has two parts, a displacement branch and a Faradaic branch.
+{\color{blue} While Scott and Single \cite{ScottSingle2013} incorporate a memristor into their model, it has been omitted here for simplicity.
+Its contribution is limited to situations where diffusion limited Faradaic reactions come into play, a situation that stimulator implants are designed to avoid.}
 
-It has been suggested that the primary coupling mechanism between platinum electrodes and phisiological saline is the reversable evolution of gas, probably oxygen, at the platinum surface, which dissolves without bubble formation.\cite{Greatbatch1969} Understanding exact mechanism of displacement or Faradaic charge transfer at the electrode surface is beyond the scope of this work, instead we wish to characterise the electrode/electrolyte system in terms of an electrical model.
-The model separates the Faradaic and displacement characteristics into separate circuit elements, namely the diode and CPE, however we do not suggest that these conduction mechanisims are physically separate.
+{
+    \color{blue}
+It has been suggested that the primary coupling mechanism between platinum electrodes and physiological saline is the reversible evolution of gas, probably oxygen, at the platinum surface, which dissolves without bubble formation.\cite{Greatbatch1969} Understanding exact mechanism of displacement or Faradaic charge transfer at the electrode surface is beyond the scope of this work, instead we wish to characterise the electrode/electrolyte system in terms of parameters that may be fed into an electrical model.
+}
 
@@
 The ingredients of that stock solution are given in table~\ref{tab:PBSrecipe}.
+{
+    \color{blue}
+    % Item 11
     The pH level of the stock was measured, using a calibrated EDT Instruments BA-350 pH meter, to have a pH of 7.4. No pH adjustments were made to the derived solutions.
-
+}
 \begin{table}
@@
 Repeating that work, a resistor network that connects each of the eight electrodes is constructed, mimicking the resistances due to the solution bulk.
+{
+    \color{blue}
 The mesh depth and padding values of five columns and three rows, respectively, has been taken directly from \cite{ScottSingle2013}.
@@
 Hence, we define $R_{sri}$ to be 3/4 that of $R_{eri}$ making it a dependant parameter.}.
+}
 The resulting fit and parameter values are presented in figure~\ref{fig:transresistance} and table~\ref{tab:RESparams} respectively. 
+{
+    \color{blue}
+    % Item 11
 Measurements of the inter-electrode impedance were made using a Tektronix TPS2014 DSO with four fully isolated and floating channels; an Agilent 33220A Function Generator; and a desktop PC controlling the instruments via Python 2.7.
+}
 
@@
 \section{Displacement Parameters}
-The linear, or small-signal, part of an electrode-electrolyte interface is represented by a Constant Phase Element (CPE) or fractional capacitor.
-For simulation purposes this element is realised as an array of R-C branches.~\cite{ScottSingle2013,Morrison59,Elwakil10} Measurement of the CPE is made by sweeping the frequency of a sinusoidal stimulus across electrodes 2 and 7 of the Octrode while measuring the voltage between electrodes 2 and 3.
+{
+    % Identifying reactions
+    \color{blue}
+Displacement currents are responsible for capacitive behaviour at interfacial boundaries.
+They are brought about by the redistribution of charge in response to applied fields, however they may also be a result of reversible Faradaic reactions at the surface of the electrode.
+Such reactions involving water and platinum, as identified in \cite{Horch2004}, include:
+    \begin{eqnarray}
+        Pt + H_{2}O &\Leftrightarrow& PtO + 2\cdot H^{+} + 2 \cdot e^{-}\\
+        Pt + H^{+} & \Leftrightarrow & Pt-H\\
+        Pt + H_{2}O + e^{-} &\Leftrightarrow& Pt-H+OH^{-}
+    \end{eqnarray}
+
+This displacement mechanism is capable of transferring charge between electrical and biological systems without damaging electrodes or tissue. \cite{Horch2004}
+This behaviour is modelled by way of a Constant Phase Element (CPE); also known as a fractional capacitor.
+}
+For simulation purposes this element is realised as an array of R-C branches.~\cite{ScottSingle2013,Morrison59,Elwakil10} We measured displacement currents by sweeping the frequency of a sinusoidal stimulus across electrodes 2 and 7 of the Octrode while measuring the voltage between electrodes 2 and 3.
 The numbering pattern used to identify each of the electrodes on the Octrode is shown in figure~\ref{fig:octrode}.
 Measurements made using this configuration allow for the quantification of a single interface impedance in series with the resistance presented by the bulk solution.
+{
+    \color{blue}
 Current density during measurements peaked at $11.5\thinspace A/m^{2}$ at 10\thinspace kHz in 1.0X PBS and fell as low as $0.0141\thinspace A/m^{2}$ at 50\thinspace mHz in 0.025X PBS.
@@
 The measurement insturments used are the same as those used to measure the inter-electrode resistance.
+}
+{
+    \color{blue)
+    % Item 6
     Figure~\ref{fig:CPE_Magnitude} shows the magnitude of the measured response of each of the six PBS concentrations accompanied by simulation results.
@@
 Those values were chosen as they give the closest match to the measured data.
-
+}
 As shown in the interface model schematic (figure~\ref{fig:schematic}), the interface contains its own internal series resistance ($R_{S}$).
@@
 For the purposes of our model, we are content with placing a limit of 0.9\thinspace V across the pair of interfaces and using the assumption that Faradaic conduction does not change with concentration.
-Further investigation into modelling this relationship is needed.
+Further investigation into modelling this relationship is needed in order to extend the model into the diffusion controlled scenario.
 We hope to publish this in a follow-up paper.
@@
 \begin{thebibliography}{99}
+
+    \bibitem{Horch2004}
+    K.~W.~Horsch and G.~S.~Gurpreet
+    ``Neuroprosthetics: theory and practice'',
+    World Scientific, 2004.
 
@@
     {\color{Red} Research textbook knowledge and published state of the art relating to electro chemistry in our area.}
-    No response yet.
+    This response has concerned us and we have subsequently invested considerable effort in broadening our search of published state-of-the-art.
+Where possible we have included references to electrochemistry literature from any areas we are dealing with in this revision.
+During this expansion we were unable to find anything that subtracts from the novelty of this work.
+That said, our work is concerned primarily with the electrical side of an interface impedance and more specifically with that of an implanted electrode.
+Our intention is to be able to encapsulate the electrical aspect of the interface and surrounding electrolyte in a purely mathematical construct, regardless of the chemistry at play.
 }\\

### 2014-02-10 paper.tex
Added graph showing charge injection during CPE measurements

@@
 }
-For simulation purposes this element is realised as an array of R-C branches.~\cite{ScottSingle2013,Morrison59,Elwakil10} We measured displacement currents by sweeping the frequency of a sinusoidal stimulus across electrodes 2 and 7 of the Octrode while measuring the voltage between electrodes 2 and 3.
-The numbering pattern used to identify each of the electrodes on the Octrode is shown in figure~\ref{fig:octrode}.
-Measurements made using this configuration allow for the quantification of a single interface impedance in series with the resistance presented by the bulk solution.
+For simulation purposes this element is realised as an array of R-C branches.~\cite{ScottSingle2013,Morrison59,Elwakil10} We measure displacement currents by sweeping the frequency of a sinusoidal stimulus across electrodes 2 and 7 of the Octrode while measuring the voltage between electrodes 2 and 3 (numbering shown in Fig.~\ref{fig:octrode}).
+This allows for the measurement of a single interface impedance in series with the resistance presented by the bulk solution. 
+\begin{figure}
+    \begin{center}
+        \includegraphics{graphics/chargeInjectionVsFrequency.pdf}
+    \end{center}
+    \caption{\color{blue} Charge injected during CPE measurment for each of the six concentrations of PBS. Calculated using an effective surface area of 14\thinspace mm$^{2}$}
+    \label{fig:chargeInjectionVsFrequency}
+\end{figure}
 {
@@
 Here we express the CPE offset parameter as $|Z|\thinspace @ \thinspace 1Hz$, but the fits used $|Z|\thinspace @ \thinspace 0.05Hz$, as data points at this frequency are outside the transitional zone where the impedance of the CPE and that of $R_{S+bulk}$ overlap.
-
-From the results shown in figure~\ref{fig:CPE_Magnitude} we observe that the salinity of the electrolyte does not affect the slope of the CPE's impedance and the magnitude shifts relatively little.
+{
+    \color{blue} Results presented in Fig.~\ref{fig:CPE_Magnitude} show an linear shift with salinity at higher frequencies, where we are seeing the resistive component of the solution bulk.
+At lower frequencies the $|Z|$ shifts relatively little compared to the nearly 2 orders of magnitude seen in the resistive region.
+Here we are seeing what appears to be more like a log relationship.
+}
 This suggests that the CPE does not rely on the added ions but they do have an effect, implying that its behaviour is a property of platinum and $H_{2}O$.
@@
     {\color{Red} Estimate current density and investigate possible effects}
-    Maximum and minimum current density during displacement current measurement added. No comment on effect formed yet. No response yet.
+    Have added a new figure to show the current density during CPE measurement.
 }
@@
     {\color{Red} Describe instruments used in measurements or make reference to Jonathans paper}
-    Added details of the instruments used to conduct inter-electrode resistance measurements and clarified thier reuse for displacement measurements.
+    Added missing details of instrumentation used to conduct inter-electrode resistance measurements and clarified thier reuse for displacement measurements.
 }\\

### 2014-02-10 paper.tex
Added extra reference, reworded displacement/polarisation discussion and added new possible reversable faradaic reaction

--- 2014-02-05 paper.tex
@@
 Displacement currents are responsible for capacitive behaviour at interfacial boundaries.
-They are brought about by the redistribution of charge in response to applied fields, however they may also be a result of reversible Faradaic reactions at the surface of the electrode.
-Such reactions involving water and platinum, as identified in \cite{Horch2004}, include:
+They are brought about by the redistribution of charge in response to applied fields, i.e.
+a charged electrode will attract or repel $Cl^{-}$ from its surface and reorientate polar molecules in the surrounding solution.
+This capacitive behaviour may also be a result of electrode polarisation in the form of reversible Faradaic reactions at the surface of the electrode.
+Such reactions involving water and platinum, as identified in \cite{Horch2004,Mohtashami2011}, include:
     \begin{eqnarray}
-        Pt + H_{2}O &\Leftrightarrow& PtO + 2\cdot H^{+} + 2 \cdot e^{-}\\
+        Pt + H_{2}O &\Leftrightarrow& PtO + 2 H^{+} + 2 e^{-}\\
+        PtO + H_{2}O &\Leftrightarrow& PtO_{2} + 2 H^{+} + 2e^{-}\\
         Pt + H^{+} & \Leftrightarrow & Pt-H\\
@@
 
+    \bibitem{Mohtashami2011}
+    Saba~Mohtashami,
+    ``ELECTROCHEMICAL PROPERTIES OF FLEXIBLE ELECTRODES FOR IMPLANTED NEUROMUSCULAR EXCITATION APPLICATIONS'',
+    Open Acess Dissertations and Theses (2011), Paper 6152
+
     \bibitem{Horch2004}
-    K.~W.~Horsch and G.~S.~Gurpreet
+    K.~W.~Horsch and G.~S.~Gurpreet,
     ``Neuroprosthetics: theory and practice'',

### 2014-02-10 paper.tex
Finished addressing the 1st reviewers notes and concerns.

@@
 \section{Faradaic Parameters}
-
+{
+    \color{blue}
+    Our model uses two reverse connected diodes to represent Faradaic current conduction between electrode and electrolyte.
+Specifically we use the diodes to model irreversible Faradaic reactions.
+Any reversible reactions, those producing reactants bound to the surface of the electrode, are encapsulated by the displacement branch (CPE) of the model.
+    Possible irreversible Faradaic reactions for platinum electrodes in saline are:
+    \begin{eqnarray}
+        Pt + 4Cl^{-} &\Rightarrow& [PtCl_{4}]^{2-} + 2 e^{-}\\
+        2H_{2}O + 2 e^{-} &\Rightarrow& H_{2}\uparrow + 2OH^{-}\\
+        2H_{2}O &\Rightarrow& O_{2}\uparrow + 4H^{+} + 4e^{-}\\
+        2Cl^{-} &\Rightarrow& Cl_{2}\uparrow + 2e^{-}\\
+        Cl^{-} + H_{2}O &\Rightarrow& ClO^{-} + 2H^{+} + 2e^{-}
+    \end{eqnarray} 
+}
 With parameters fitted for the scaling of both the CPE and $R_{S}$ with PBS concentration, we evaluate Faradaic conduction.
@@
 
-Faradaic measurements were made using an Agilent E5270B Precision Measurement Mainframe producing a stepped DC voltage stimulus across electrodes [TODO: Item 28] 2 and 6 whilst continuously measuring the output current.
-We commenced with 1.0X concentration of the stock solution (table~\ref{tab:PBSrecipe}).
-This solution was progressively diluted in factors of two between each measurement.
-The solution was mixed continuously using a standard laborotary grade magnetic stirrer.
-The solution was in equlibriumm with air prior to and during measurement and the electrodes remained submerged at all times.
+Faradaic measurements were made using an Agilent E5270B Precision Measurement Mainframe producing a stepped DC voltage stimulus across electrodes 3 and 7 whilst continuously measuring the output current.
+{
+    \color{blue}
+    The use of electrodes 3 and 7 was made because the connection to electrode 2 in our Octrode had been damaged.
+This alteration has no impact on the validity of results as all other electrodes are left to float.
+}
+
+Measurements commenced with a 4.5 litre solution of 1.0X PBS which was progressively diluted in factors of two between each measurement.
+The solution was mixed continuously using a standard laboratory grade magnetic stirrer.
+The solution was in equilibrium with air prior to and during measurement and the electrodes remained submerged at all times.
 A single measurement run involved stepping the voltage across electrodes 2 and 7 from 0.5\thinspace V to 1.2\thinspace V in increments of 0.05\thinspace V; this range was previously determined to capture the onset of Faradaic conduction.
@@
 In figure~\ref{fig:StepResponse_Faradaic}, electrical current measurements are plotted against time (solid lines).
-Each spike marks the point at which the voltage is incremented.
-We expect the peak current to be much higher than is shown since each measurement point is the average of 300 samples taken over 1 second.
+Each spike marks the point at which the voltage is incremented by 50\thinspace mV.
 Note that the amount of charge absorbed by the CPE increases with concentration of PBS, but the current for each concentration converges to approximately the same value.
@@
 
-We attribute the change in behaviour between 0.9\thinspace V and 1.05\thinspace V to a transition to diffusion-controlled conduction.
-We hypothesise that the charging of the CPE draws available ions to the electrode, creating a layer of high ionic concentration at the surface irrespective of that of the solution bulk.
-It is this layer that is subsequently consumed by the Faradaic reactions at a rate dependent on the log of the electrode overpotential.
-The effect of bulk solution concentration while this layer has formed is negligible until the point at which the layer is consumed faster than it can be replenished.
-At this stage, and with increasing overpotential, the Faradaic conduction is governed by diffusion of ions from the bulk into the layer, the rate of which increases with the ion concentration in the bulk.
-We believe this explains the divergence of conduction with concentration between 0.9\thinspace V and 1.05\thinspace V and why there is no observable dependence on bulk ion concentration beforehand.
-
-This hypothesis intimately links the Faradaic component to the CPE, where the latter is a precursor to the former.
-For the purposes of our model, we are content with placing a limit of 0.9\thinspace V across the pair of interfaces and using the assumption that Faradaic conduction does not change with concentration.
-Further investigation into modelling this relationship is needed in order to extend the model into the diffusion controlled scenario.
-We hope to publish this in a follow-up paper.
-
 \begin{figure}
@@
 
-\begin{figure}
-    \begin{center}
-        \includegraphics{graphics/faradaic_currentVsVoltageIEEE}
-    \end{center}
-    \caption{Simulated response of the interface model compared to measurement from the electrodes with a stepped voltage overpotential.
+%\begin{figure}
+%    \begin{center}
+%        \includegraphics{graphics/faradaic_currentVsVoltageIEEE}
+%    \end{center}
+%    \caption{Simulated response of the interface model compared to measurement from the electrodes with a stepped voltage overpotential.
 Measurement points show current values taken at the $64^{th}$ second after each voltage increment.}
-    \label{fig:faradaic_currentVsVoltage}
-\end{figure}
+%    \label{fig:faradaic_currentVsVoltage}
+%\end{figure}
 
@@
 
-Parameter values for $i_{0}$ and $n$ are presented in table~\ref{tab:FaradaicParams}.
+%Parameter values for $i_{0}$ and $n$ are presented in table~\ref{tab:FaradaicParams}.
 These parameters were found by fitting the diode equation to the results shown in figure~\ref{fig:faradaic_currentVsVoltage}.
 
+We attribute the change in behaviour between 0.9\thinspace V and 1.05\thinspace V to a transition to diffusion-controlled conduction.
+We hypothesise that the charging of the CPE draws available ions to the electrode, creating a layer of high ionic concentration at the surface irrespective of that of the solution bulk.
+It is this layer that is subsequently consumed by the Faradaic reactions at a rate dependent on the log of the electrode overpotential.
+The effect of bulk solution concentration while this layer has formed is negligible until the point at which the layer is consumed faster than it can be replenished.
+At this stage, and with increasing overpotential, the Faradaic conduction is governed by diffusion of ions from the bulk into the layer, the rate of which increases with the ion concentration in the bulk.
+We believe this explains the divergence of conduction with concentration between 0.9\thinspace V and 1.05\thinspace V and why there is no observable dependence on bulk ion concentration beforehand.
+For the purposes of our model, we are content with placing a limit of 0.9\thinspace V across the pair of interfaces and using the assumption that Faradaic conduction does not change with concentration.
+
+{
+    \color{blue}
+Figure~\ref{fig:faradaic_currentVsTime} shows a subset of the data used in Fig.~\ref{fig:StepResponse_Faradaic} (the 1.0X PBS trace) to show the fit between simulated and measured data.
+Here the simulation contains fitted diode parameters, shown in table~\ref{tab:FaradaicParams}, which give rise to the exponentially increasing steady state current.
+It is apparent from this trace that the temporal response of the CPE does not match the transient decay curves seen in the Faradaic measurements, something the CPE should predict.
+These transient decay curves appear to have time-constant that decreases with each subsequent measurement.
+This variable time-constant phenomena is especially clear when looking back at figure~\ref{fig:CPE_currentVsTime}.
+Although the Faradaic response transients appear to approach the time-constant predicted by the CPE, there is clearly behaviour not completely described by the CPE.
+
+We hope to extend this model into a diffusion controlled conduction scenario and extend the CPE element to mimic the variable time-constant behaviour in a follow up paper.
+}
 \section{In-vivo measurements of sheep}
@@
     Saba~Mohtashami,
-    ``ELECTROCHEMICAL PROPERTIES OF FLEXIBLE ELECTRODES FOR IMPLANTED NEUROMUSCULAR EXCITATION APPLICATIONS'',
+    ``Electrochemical Properties of Flexible Electrodes for Implanted Neuromuscular Excitation Applications'',
     Open Acess Dissertations and Theses (2011), Paper 6152
@@
     Item 1\\
-    {\color{Red} Research textbook knowledge and published state of the art relating to electro chemistry in our area.}
     This response has concerned us and we have subsequently invested considerable effort in broadening our search of published state-of-the-art.
@@
 That said, our work is concerned primarily with the electrical side of an interface impedance and more specifically with that of an implanted electrode.
-Our intention is to be able to encapsulate the electrical aspect of the interface and surrounding electrolyte in a purely mathematical construct, regardless of the chemistry at play.
+Our intention is to be able to encapsulate the electrical aspect of the interface and surrounding electrolyte in an equivalent electrical circuit, regardless of the chemistry at play.
 }\\
@@
     Item 2\\
-    {\color{Red} Review and discuss existing interface models}
-    No response yet.
+    Correct, there are many published interfacial models.
+This model differentiates itself from those by being compact.
+Compact in the sense that it can be entered into any common electronic circuit simulator and used to make predictions about impedance.
+This is especially important for elecronic engineers designing medical impalant devices.
 }\\
@@
     Item 3\\
-    {\color{Red} Is polarisation a separate mechanism from double layer formation?
-If so, can we address?
-Polarisation will be just as important in cyclic measurement techniques where the cycle time is low.
-Does anyone understand polarisation sufficiently to remove it from measurements?
-Is polarisation not just remaining charge in a layer around an electrode, is it not just the double layer?}
-    No response yet.
+    We have lumped the effects of polarisation into the response of the displacement element in the model (CPE).
+The introduction to the Displacement Parameters section has been updated to include mention of polarisation.
+Our technique for measuring Faradaic reactions, namely to apply a DC voltage and wait until current transients settle before making a measurement, has been choosen to minimise any contribution from polarisation effects.
 }\\
@@
     Item 4\\
-    {\color{Red} I don't understand what use doing this would be.
-All voltage dropped between two end electrodes, voltage proportional to total impedance between electrodes.
-The most use you could get from this would be to find how much is dropped across a single interface, which is exactly what we are doing.}
-    No response yet.    
+    We are not so much interested in knowing the resistivity of the solution as we are in knowing the resistance between any pair of electrodes for the specific electrode array.
+The difference being that we expect the geometry of the electrode array, being comprised of 8 cylindrical coaxially placed electrodes as shown in Fig.~1, to determine the resistance in a non-trivial way.
+Using the transimedance measurements we can construct a mesh that represents the geometry of the electrodes and the resistivity of the solution.
+Another benefit in the method chosen is that it does not rely on knowing the electrode geometry and is therefore more versatile.
 }\\
@@
     Item 5\\
-    {\color{Red} Do we wish to get into this?
-Perhaps we could touch on it (after reviewing electrochemistry literature) but leave it loose and mention that it is not our intention to completely understand the mechanisims at the chemical level, rather to compare an available model with measurements and comment.}
-    No response yet.
+    Relevant Faradaic reactions, both reversible and irreversible, have been added both to the displacement/polarisation and Faradaic sections.
 }\\
@@
     Item 6\\
-    {\color{Red} Enhance color variation in Figures 4 and 5 and make a reference to Figure 5}
-    Graphs redrawn with a wider range of shading to help identify traces.
+    Graphs redrawn with a wider range of shading to help identify traces and referenced on page 3 (now figure \ref{fig:CPE_Phase}).
 }\\
@@
     Item 7\\
-    {\color{Red} The diodes are identical, this is moving into polarisation territory again.
-In effect, they are both being used (one by + and other by -).
-I don't know what to say about this.
-We wanted to make all the measurements happen in as little time as possible.
-We have data from sweeps in the other direction, not DC though.}
-    No response yet.
+    The measurements involving the back-to-back diodes are those measuring the contribution from irreversible Faradaic reactions.
+These measurements involve two active electrodes while the remaining electrodes and the electrolyte have a floating potentials.
+Sweeping the voltage from -1.2V to +1.2V in this case would be the equivalent of swapping the terminals halfway through the sweep.
+Physically this would not be the same as polarisation effects would linger, however we are only interested in the steady state Faradaic conduction where we assume polarisation and displacement effects are negligible.
 }\\
@@
     Item 8\\
-    {\color{Red} This is true, try and pinpoint exactly why this is happening. Why does the CPE perform so well in the CPE frequency response plots yet so poorly in the Faradaic part?}
-    No response yet.
+    We have addressed this discrepancy on page 5.
+The frequency response of the CPE is still valid, which is what we had fitted the parameters.
+We agree that the time-domain response of the CPE may need further work.
+Thank you for your time and critique.
 }\\
@@
     Item 10\\
-    {\color{Red} Estimate current density and investigate possible effects}
-    Have added a new figure to show the current density during CPE measurement.
+    Added a new figure to show the current density during CPE measurement.
 }
@@
     Item 11\\
-    {\color{Red} Describe instruments used in measurements or make reference to Jonathans paper}
-    Added missing details of instrumentation used to conduct inter-electrode resistance measurements and clarified thier reuse for displacement measurements.
+    Added missing details of instrumentation used to conduct inter-electrode resistance measurements and clarified their reuse for displacement measurements.
 }\\
@@
     Item 18\\
-    {\color{Red} Estimate the amount of charge being injected in each of the measurements (fits with the current density)}
     Instrumentation for CPE measurements have been added.
@@
     Item 20\\
-    {\color{Red} Replace ``A 0.1X concentration'' with ``a one-tenth concentration...'' and explain exactly what that means.}
     Yes, thank you, see amendment.
@@
     Item 23\\
-    {\color{Red} Reword the caption of Fig. 4 to include the series resistance.}
-    Thank you, have reworded the caption in Figure 4 to more accuratly describe the situation.
+    Thank you, have reworded the caption in Figure 4 to more accurately describe the situation.
 }\\
@@
     Item 29\\
-    {\color{Red} What I originally thought, I don't know where inductive stirrer came from}
     Changed mention of inductive stirrer to magnetic stirrer.
@@
     Item 30\\
-    {\color{Red} This must form part of the inaccurate use of words comment. It's not right to say response of a pair of electrodes since there are other effects. Reword.}
     Removed reference to the CPE element and have better quantified the settling period in that footnote.
@@
     Item 31\\
-    {\color{Red} Yes, this is better. Replace with this.}
     Yes, that is better - thank you.
@@
     Item 32\\
-    {\color{Red} Correct, maybe a diargam of the hypothesis is required - nobody seemed to dispute the hypothesis. Check there is no ``textbook knowledge'' explanation for this beforehand.}
     Changed references to the CPE model element in the conclusion to the electrical double layer.

### 2014-02-10 paper.tex
Added comment to reviewer

@@
     Item 9\\
-    {\color{Red} Pull in more explination from JonathanScott2013 relating to the resistor mesh}
-    No response yet.
+    We have encouraged the reader to review ScottSingle2013 in order to understand the interpretation of the given parameters.
+{\color{red} Should I just say they are resistances of elements in a resistor mesh?}
 }\\
@@
     Item 12\\
-    {\color{Red} ``shifts relatively little'' meaning at this impedance 50k is small compared to total resistance''}
-    No response yet.
+    Have reworded this slightly to convey that the shift in the CPE response is small relative to the shift in the resistance in the solution bulk. We are referring to a relative difference, a factor.
+    {\color{red} I don't know how better to explain this, The difference between 9 000 000 and 1 000 000 000 is small compared to the difference between 20 and 2000}
 }\\

### 2014-02-10 paper.tex
Updated reviewer comments

@@
 }
-For simulation purposes this element is realised as an array of R-C branches.~\cite{ScottSingle2013,Morrison59,Elwakil10} We measure displacement currents by sweeping the frequency of a sinusoidal stimulus across electrodes 2 and 7 of the Octrode while measuring the voltage between electrodes 2 and 3 (numbering shown in Fig.~\ref{fig:octrode}).
+{
+    \color{blue}
+For simulation purposes this element is realised as an array of R-C branches.~\cite{ScottSingle2013,Morrison59,Elwakil10} where the value of each R-C pair is chosen to set the slope of impedance relative to frequency.
+The placement of R-C pairs within the CPE is determined by the parameters $m$ and $k$, where $k$ determines the spacing, or density, of R-C branches and $m$ determines the resulting slope.
+}
+We measure displacement currents by sweeping the frequency of a sinusoidal stimulus across electrodes 2 and 7 of the Octrode while measuring the voltage between electrodes 2 and 3 (numbering shown in Fig.~\ref{fig:octrode}).
 This allows for the measurement of a single interface impedance in series with the resistance presented by the bulk solution. 
@@
     \end{center}
-    \caption{\color{blue} Charge injected during CPE measurment for each of the six concentrations of PBS. Calculated using an effective surface area of 14\thinspace mm$^{2}$}
+    \caption{\color{blue} Charge injected during CPE measurement for each of the six concentrations of PBS. Calculated using an effective surface area of 14\thinspace mm$^{2}$}
     \label{fig:chargeInjectionVsFrequency}
@@
 The stimulus waveform was set at 300\thinspace mV (peak) at each measurement point.
-The measurement insturments used are the same as those used to measure the inter-electrode resistance.
+The measurement instruments used are the same as those used to measure the inter-electrode resistance.
 }
@@
     \color{blue)
-    % Item 6
-    Figure~\ref{fig:CPE_Magnitude} shows the magnitude of the measured response of each of the six PBS concentrations accompanied by simulation results.
+        {\color{red} something weird going on here} Figure~\ref{fig:CPE_Magnitude} shows the magnitude of the measured response of each of the six PBS concentrations accompanied by simulation results.
 Figure~\ref{fig:CPE_Phase} shows the phase response for the same measurements, again with the simulated response at each concentration.
@@
 From these measurements and those of a separate investigation\footnote{We took measurements of the interface's response to voltage steps when left to settle for 10 000 seconds, of which the first 250\thinspace seconds are shown in figure~\ref{fig:CPE_currentVsTime}.
-Those measurements show a trend of decreasing current stabalisation time as the overpotential steps increase.
+Those measurements show a trend of decreasing current stabilisation time as the overpotential steps increase.
 Sixty four seconds after stepping from 0.64\thinspace V to 0.72\thinspace V, the current has stabalised to $95\%$ of its value at 10\,000 seconds.
@@
 
-%\begin{figure}
-%    \begin{center}
-%        \includegraphics{graphics/faradaic_currentVsVoltageIEEE}
-%    \end{center}
-%    \caption{Simulated response of the interface model compared to measurement from the electrodes with a stepped voltage overpotential.
+\begin{figure}
+    \begin{center}
+        \includegraphics{graphics/faradaic_currentVsVoltageIEEE}
+    \end{center}
+    \caption{Simulated response of the interface model compared to measurement from the electrodes with a stepped voltage overpotential.
 Measurement points show current values taken at the $64^{th}$ second after each voltage increment.}
-%    \label{fig:faradaic_currentVsVoltage}
-%\end{figure}
+    \label{fig:faradaic_currentVsVoltage}
+\end{figure}
 
@@
     \color{blue}
-Figure~\ref{fig:faradaic_currentVsTime} shows a subset of the data used in Fig.~\ref{fig:StepResponse_Faradaic} (the 1.0X PBS trace) to show the fit between simulated and measured data.
+    Figure~\ref{fig:faradaic_currentVsTime} shows a subset of the data used in Fig.~\ref{fig:StepResponse_Faradaic} (the 1.0X PBS trace) to show the fit between simulated and measured data in the time domain.
 Here the simulation contains fitted diode parameters, shown in table~\ref{tab:FaradaicParams}, which give rise to the exponentially increasing steady state current.
@@
 This variable time-constant phenomena is especially clear when looking back at figure~\ref{fig:CPE_currentVsTime}.
-Although the Faradaic response transients appear to approach the time-constant predicted by the CPE, there is clearly behaviour not completely described by the CPE.
+Although the Faradaic response transients appear to approach the time-constant predicted by the CPE, there is still behaviour not completely described by the CPE.
+The match between fitted diode parameters ($n$ and $i_{0}$) and the measurement data 64 seconds after each voltage increment has been plotted in figure~\ref{fig:faradaic_currentVsVoltage}.
+This graph plots current conducted at 64 seconds after each step in terms of voltage applied across electrodes 3 and 7.
 
-We hope to extend this model into a diffusion controlled conduction scenario and extend the CPE element to mimic the variable time-constant behaviour in a follow up paper.
+In future we hope to extend this model into a diffusion controlled conduction scenario and extend the CPE element to better reproduce the time domain response, which we hope to publish in a follow-up paper.
 }
@@
     Item 12\\
-    Have reworded this slightly to convey that the shift in the CPE response is small relative to the shift in the resistance in the solution bulk. We are referring to a relative difference, a factor.
-    {\color{red} I don't know how better to explain this, The difference between 9 000 000 and 1 000 000 000 is small compared to the difference between 20 and 2000}
+    Have reworded this slightly to convey that the shift in the CPE response is small relative to the shift in the resistance in the solution bulk.
+We are referring to a relative difference, a gain in conductivity as a factor of the current conductivity.
+    {\color{red} Help! I don't know how better to explain this, The difference between 9 000 000 and 1 000 000 000 is small compared to the difference between 20 and 2000}
 }\\
@@
     Item 13\\
-    {\color{Red} Describe the parameters m and k in the resistor network (pull from Jonathans paper and sub-references)}
-    No response yet.
+    Sure, we have added a quick interpretation for the parameters $m$ and $k$ in the text.
 }\\
@@
     Item 15\\
-    {\color{Red} Include a reference to Figure 10 in the document}
-    No response yet.
+    Thank you, we have updated discussion of Faradaic Parameters to include the results from what is now figure~\ref{fig:faradaic_currentVsTime}.
 }\\
@@
 Would a separate sheep measurement graph be of use showing all sheep results?
-Or do we hold onto this for the better phantom paper?}
+Jonathans response: Put more sheep data in, put some error bars on.}
     No response yet.
@@
     Item 20\\
-    Yes, thank you, see amendment.
+    Fixed.
 }\\
@@
     {\color{Red} Leave until the end, if we have the space then we put it in, otherwise put a better reference to ScottSingle2013}
-    No response yet.
+    We have advised the reader to read ScottSingle2013 to understand the interpretation of the mesh generation parameters, where they would find the radial volume model.
 }\\
@@
     Item 22\\
-    {\color{Red} Mention that $R_{li}$ is not independent because of the geometric simplification of the resistor network.
-Mention that for more detail we suggest viewers read the relevant section of ScottSingle2013}
-    No response yet.
+    Footnote added to sentence in question that describes our defining of $R_{sri}$ in terms of $R_{eri}$. 
 }\\
@@
     Item 37\\
-    {\color{Red} Definitely, how did I miss that?}
-    No response yet.
+    Thank you very much. See updated figure (now figure~\ref{fig:faradaic_currentVsVoltage}).
 }\\

### 2014-02-10 paper.tex
Jonathans edits

@@
 Using a novel DC measurement technique we show that the Faradaic response of a platinum electrode, and thus the safe exposure limit, does not scale with concentration below 900\thinspace mV overpotential across a pair of electrodes.
-We compare objective measurements made in saline to those made in the spinal cavity of live sheep. We comment upon the appropriateness of using PBS as a substitute for living sheep.
+We compare objective measurements made in saline to those made in the spinal cavity of live sheep. We comment upon the appropriateness of using PBS as a substitute for in-vivo measurements.
 \end{abstract}
@@
     \color{blue}
-It has been suggested that the primary coupling mechanism between platinum electrodes and physiological saline is the reversible evolution of gas, probably oxygen, at the platinum surface, which dissolves without bubble formation.\cite{Greatbatch1969} Understanding exact mechanism of displacement or Faradaic charge transfer at the electrode surface is beyond the scope of this work, instead we wish to characterise the electrode/electrolyte system in terms of parameters that may be fed into an electrical model.
+It has been suggested that the primary coupling mechanism between platinum electrodes and physiological saline is the reversible evolution of gas, probably oxygen, at the platinum surface, which dissolves without bubble formation.\cite{Greatbatch1969} Understanding the exact mechanism of displacement or Faradaic charge transfer at the electrode surface is beyond the scope of this work.
+Rather we wish to characterise the electrode/electrolyte system in terms of parameters that may be fed into an electrical model.
 }
@@
 The network in that paper was defined using five parameters: $R_{eri}$, $R_{lri}$, $R_{li}$, mesh depth, and edge depth.
-Readers are advised to read that paper to understand the interpretation of these model parameters.
+Readers are referred to \cite{ScottSingle2013} for the interpretation of these model parameters.
 Repeating that work, a resistor network that connects each of the eight electrodes is constructed, mimicking the resistances due to the solution bulk.
@@
 
+\pagebreak
 \section{Displacement Parameters}
@@
 For simulation purposes this element is realised as an array of R-C branches.~\cite{ScottSingle2013,Morrison59,Elwakil10} where the value of each R-C pair is chosen to set the slope of impedance relative to frequency.
-The placement of R-C pairs within the CPE is determined by the parameters $m$ and $k$, where $k$ determines the spacing, or density, of R-C branches and $m$ determines the resulting slope.
+The placement of R-C pairs within the CPE is determined by Morrison's parameters $m$ and $k$, where $k$ determines the spacing, or density, of R-C branches and $m$ determines the resulting slope.
 }
@@
 Current density during measurements peaked at $11.5\thinspace A/m^{2}$ at 10\thinspace kHz in 1.0X PBS and fell as low as $0.0141\thinspace A/m^{2}$ at 50\thinspace mHz in 0.025X PBS.
-The stimulus waveform was set at 300\thinspace mV (peak) at each measurement point.
-The measurement instruments used are the same as those used to measure the inter-electrode resistance.
+The charge injected is shown in figure~\ref{fig:chargeInjectionVsFrequency}.
+The stimulus waveform was set at 300\thinspace mV (peak) at each measurement point. The measurement instruments used are the same as those used to measure the inter-electrode resistance.
 }
 {
-    \color{blue)
-        {\color{red} something weird going on here} Figure~\ref{fig:CPE_Magnitude} shows the magnitude of the measured response of each of the six PBS concentrations accompanied by simulation results.
+    \color{blue}
+Figure~\ref{fig:CPE_Magnitude} shows the magnitude of the measured response of each of the six PBS concentrations accompanied by simulation results.
 Figure~\ref{fig:CPE_Phase} shows the phase response for the same measurements, again with the simulated response at each concentration.
@@
 {
-    \color{blue} Results presented in Fig.~\ref{fig:CPE_Magnitude} show an linear shift with salinity at higher frequencies, where we are seeing the resistive component of the solution bulk.
-At lower frequencies the $|Z|$ shifts relatively little compared to the nearly 2 orders of magnitude seen in the resistive region.
-Here we are seeing what appears to be more like a log relationship.
+    \color{blue} The data presented in Fig.~\ref{fig:CPE_Magnitude} show a large, linear, relative shift of $|Z|$ with salinity at higher frequencies, where the resistive component of the solution dominates.
+Conversely, at lower frequencies where the $|Z|$ changes with frequency, the relative change is closer to logarithmic. This region is modeled by the CPE. 
 }
@@
 1.
-You do not explain how the impedance measurements have been made (Figs 4, 5 13 & 14).
+You do not explain how the impedance measurements have been made (Figs 4, 5 13 \& 14).
 I want to know how much charge was being applied to these electrodes at low frequencies (e.g.
@@
 If this is a model for electrodes in vivo, should not the PBS have been in equilibrium with gas with the in vivo partial pressure of oxygen?
-I suggest that you repeat this experiment, at least (i) under air, (ii) under nitrogen, & perhaps (iii) under in vivo partial pressure of oxygen.
+I suggest that you repeat this experiment, at least (i) under air, (ii) under nitrogen, \& perhaps (iii) under in vivo partial pressure of oxygen.
 The stirring arrangements ought to be exactly described too because liquid flow may be critical.\\
@@
 
-6. P2, col 2, line 24: why 2 & 7?\\
+6. P2, col 2, line 24: why 2 \& 7?\\
 {\color{OliveGreen}
@@
 Although their current references include clearly important electrode characterization references (Cogan, Merrill et.
-al, & Kane et.
+al, \& Kane et.
 al), the information contained in these references are not effectively used to support the authors’ work.\\
@@
 }
+
 \end{document}

### 2014-02-11 paper.tex
Regraphed sheep data and added error bars

@@
 The study complied with the Australian Code of Practice for the Care and Use of Animals for Scientific Purposes.
-The measurements are presented in figures~\ref{fig:displacement_sheepCPEMagnitude} and~\ref{fig:displacement_sheepCPEPhase} on top of the array of traces for saline taken from figures~\ref{fig:CPE_Magnitude}
-and~\ref{fig:CPE_Phase}.
+{\color{blue} Four measurements taken at regular invervals over a period of 30 minutes} are presented in figures~\ref{fig:displacement_sheepCPEMagnitude} and~\ref{fig:displacement_sheepCPEPhase} on top of the array of traces for saline taken from figures~\ref{fig:CPE_Magnitude} and~\ref{fig:CPE_Phase}.
 Although it is clear that there are complications in vivo, a 0.25X PBS saline offers a good approximation to the resistive part of the trace.
@@
     \end{center}
-    \caption{Comparison between the magnitude of CPE in live sheep (blue circles) against each of the PBS traces from figure~\ref{fig:CPE_Magnitude} (grey lines) and a simulated fit to the sheep data (red trace).}
+    \caption{Comparison between the magnitude of CPE in live sheep {\color{blue}(blue error bars)} against each of the PBS traces from figure~\ref{fig:CPE_Magnitude} (grey lines) and a simulated fit to the sheep data (red trace).}
     \label{fig:displacement_sheepCPEMagnitude}
@@
     \end{center}
-    \caption{Comparison between the phase response of the CPE in live sheep (blues circles) against each of the PBS traces taken from figure~\ref{fig:CPE_Phase} (grey lines) and a simulated fit to the sheep data (red trace).}
+    \caption{Comparison between the phase response of the CPE in live sheep {\color{blue}(blue error bars)} against each of the PBS traces taken from figure~\ref{fig:CPE_Phase} (grey lines) and a simulated fit to the sheep data (red trace).}
     \label{fig:displacement_sheepCPEPhase}
@@
     We have encouraged the reader to review ScottSingle2013 in order to understand the interpretation of the given parameters. 
-{\color{red} Should I just say they are resistances of elements in a resistor mesh?}
 }\\
@@
     Item 16\\ 
-    {\color{Red} Leave sheep in but perhaps show the second measurement (day 1) if possible (4th reviewer found sheep correlation to PBS result interesting).
-Would a separate sheep measurement graph be of use showing all sheep results?
-Jonathans response: Put more sheep data in, put some error bars on.}
-    No response yet.
+    Graph of sheep response to displacement stimulus has been updated to include four separate measurements taken on the second day of sheep measurement.
+The first day gave results typical of these but we ran into connection problems leading to intermittent data hence they have been omitted.
 }\\
@@
     Item 28\\
-    {\color{Red} Took resistance measurements of lead and electrode 2 is open circuit inside the electrode. Must have meant 3 and 7, due to damaged electrode 2}
-    No response yet.
+    The mention of the use of electrodes 2 and 6 was a mistake. We actually used electrodes 3 and 7 due to damage to the electrode array we were using. See updated explination on page 4.
 }\\
@@
     Item 36\\
-    {\color{Red} Perhaps Troyk could be added. A search for textbook knowledge and more published state of the art should uncover more references}
-    No response yet.
-}\\
+    {\color{Red} Perhaps Troyk could be added. References have been extended to include a Masters Theses and Neuroprosthetics: Theory and practise book}
+}
 

### 2014-02-11 paper.tex
Regraph charge injection and recalculate current density

@@
     \begin{center}
-        \includegraphics{graphics/chargeInjectionVsFrequency.pdf}
+        \includegraphics{graphics/chargeInjectionVsFrequency_magnitude}
     \end{center}
-    \caption{\color{blue} Charge injected during CPE measurement for each of the six concentrations of PBS. Calculated using an effective surface area of 14\thinspace mm$^{2}$}
+    \caption{\color{blue} Charge injected per phase during CPE measurement for each of the six concentrations of PBS. Calculated using a geometric surface area of 10\thinspace mm$^{2}$}
     \label{fig:chargeInjectionVsFrequency}
@@
     \color{blue}
-Current density during measurements peaked at $11.5\thinspace A/m^{2}$ at 10\thinspace kHz in 1.0X PBS and fell as low as $0.0141\thinspace A/m^{2}$ at 50\thinspace mHz in 0.025X PBS.
-The charge injected is shown in figure~\ref{fig:chargeInjectionVsFrequency}.
+    The geometric current density during measurements peaked at 22.59\thinspace mA/cm$^{2}$ at 5300\thinspace kHz in 1.0X PBS and fell as low as 27.66\thinspace $\mu$A/cm$^{2}$ at 50\thinspace mHz in 0.025X PBS.
+Charge injection per phase is shown in figure~\ref{fig:chargeInjectionVsFrequency} for each solution.
 The stimulus waveform was set at 300\thinspace mV (peak) at each measurement point. The measurement instruments used are the same as those used to measure the inter-electrode resistance.

### 2014-02-11 paper.tex
Unsure what happened in this edit

@@
 Figure~\ref{fig:CPE_Scaling} shows measured data and the corresponding fits for both the CPE magnitude at 0.05\thinspace Hz and $R_{S+bulk}$.
-The resulting model parameters $m$, $k$, and $|Z|\thinspace @\thinspace 1Hz$ are shown in table~\ref{tab:CPEparams}.
+The model parameters $m$, $k$, $|Z|\thinspace @\thinspace 1Hz$, and $R_S$ are shown in table~\ref{tab:CPEparams}, with $|Z|\thinspace @\thinspace 1Hz$, and $R_S$ given as functions of concentration.
 Here we express the CPE offset parameter as $|Z|\thinspace @ \thinspace 1Hz$, but the fits used $|Z|\thinspace @ \thinspace 0.05Hz$, as data points at this frequency are outside the transitional zone where the impedance of the CPE and that of $R_{S+bulk}$ overlap.
@@
 Conversely, at lower frequencies where the $|Z|$ changes with frequency, the relative change is closer to logarithmic. This region is modeled by the CPE. 
+This suggests that the CPE does not chiefly rely on the added salt ions, but they do have some effect. 
+Instead, the constant-phase charge effect must arise from phenonema not associated with the salt ions.
 }
-This suggests that the CPE does not rely on the added ions but they do have an effect, implying that its behaviour is a property of platinum and $H_{2}O$.
 
@@
 \section{Faradaic Parameters}
+
+With parameters fitted for the scaling of both the CPE and $R_{S}$ with PBS concentration, we turn to Faradaic conduction. 
 {
@@
 Specifically we use the diodes to model irreversible Faradaic reactions.
-Any reversible reactions, those producing reactants bound to the surface of the electrode, are encapsulated by the displacement branch (CPE) of the model.
+(Any reversible reactions, those producing reactants bound to the surface of the electrode, are encapsulated by the displacement branch (CPE) of the model.)
     Possible irreversible Faradaic reactions for platinum electrodes in saline are:
@@
 }
-With parameters fitted for the scaling of both the CPE and $R_{S}$ with PBS concentration, we evaluate Faradaic conduction.
-The interface model uses two reverse connected diodes to reproduce the exponential behaviour of Faradaic current conduction, implied by the Butler-Volmer equation.
+The interface model uses the diodes to reproduce the exponential behaviour of Faradaic current conduction implied by the Butler-Volmer equation.
 We wish to measure this conduction by separating it from the displacement behaviour of the CPE.
@@
 
-Faradaic measurements were made using an Agilent E5270B Precision Measurement Mainframe producing a stepped DC voltage stimulus across electrodes 3 and 7 whilst continuously measuring the output current.
-{
-    \color{blue}
-    The use of electrodes 3 and 7 was made because the connection to electrode 2 in our Octrode had been damaged.
+Faradaic measurements were made using an Agilent E5270B Precision Measurement Mainframe producing a stepped DC voltage stimulus whilst continuously measuring the output current. 
+%{
+%    \color{blue}
+%    The use of electrodes 3 and 7 was made because the connection to electrode 2 in our Octrode had been damaged.
 This alteration has no impact on the validity of results as all other electrodes are left to float.
-}
+%}
 
@@
 The solution was in equilibrium with air prior to and during measurement and the electrodes remained submerged at all times.
-A single measurement run involved stepping the voltage across electrodes 2 and 7 from 0.5\thinspace V to 1.2\thinspace V in increments of 0.05\thinspace V; this range was previously determined to capture the onset of Faradaic conduction.
+A single measurement run involved stepping the voltage across the electrodes from 0.5\thinspace V to 1.2\thinspace V in increments of 0.05\thinspace V; this range was previously determined to capture the onset of Faradaic conduction.
 
@@
 The match between fitted diode parameters ($n$ and $i_{0}$) and the measurement data 64 seconds after each voltage increment has been plotted in figure~\ref{fig:faradaic_currentVsVoltage}.
-This graph plots current conducted at 64 seconds after each step in terms of voltage applied across electrodes 3 and 7.
 
-In future we hope to extend this model into a diffusion controlled conduction scenario and extend the CPE element to better reproduce the time domain response, which we hope to publish in a follow-up paper.
+In future we hope to extend this model into a diffusion controlled conduction scenario and extend the CPE element to better reproduce the time domain response.
 }
@@
 The displacement measurements were repeated inside the spinal canal of a live sheep, just outside the dura as shown in figure~\ref{fig:sheepSpine}.
-The sheep were prepared and anaesthetised using the procedures described in \cite{Parker2013} under the Animal Care and Ethics Committee approval of the Royal North Shore Hospital.
+The sheep were prepared and anaesthetised using the procedures described in \cite{Parker2013} under the Animal Care and Ethics Committee approval of the Royal North Shore Hospital, Sydney.
 The study complied with the Australian Code of Practice for the Care and Use of Animals for Scientific Purposes.
@@
 Jonathan, you thought this was too messy and it was removed, should it be added back in again?}
+% No sadly not interesting just related to the fact that interface has its own internal resitance.
     No response yet.
@@
     Item 25\\
+% Because consistent with prev pub plus it doesnt matter which STRESS THIS.
     {\color{Red} Explain more clearly why electrodes 2 and 7 were chosen (to avoid end effects)}
@@
     Item 33\\
+% We can dial up shift in cpe and bulk resistance to create a better match using available chemical reagenre.
+we hope to synth a superior phantom through combos of saline solvets and hydrolysed cellulose.
+we anticipate crateing a superios phantom using.
+one of the goals of one of our industrial partners.
     {\color{Red} True, a feeble comment on PBS match.
@@
 For example, the parameters in Table 2 (and reported to be in Figure 3) are not explained and what their relationship to the remainder of the manuscript is not provided.
+
 {\color{OliveGreen}
@@
     {\color{Red} Explain parameters in table two better or refer readers to ScottSingle2013}
-    No response yet.
+    We have expanded the explanation in the manuscript, and referred interested readers to the source.
 }
@@
     Item 35\\
+% No reference elect possible in an implated scenario.
+Much of problem stems fro trad.
+electchem are inepplicable or impodssible.
+much or ou rreviewers arises fro fact that we are operating ni  an scenario far fro trad electrochem labs.
     {\color{Red} Try to include any relevant electrochemical information, find out what that is first}
@@
     Item 36\\
+% In response to numersios reviewese commnets we have added citations we hope we have more thoroughly put more thoro pointers to the literature in  nour manuscript...
+After extensice ...
+we have added citations
     {\color{Red} Perhaps Troyk could be added. References have been extended to include a Masters Theses and Neuroprosthetics: Theory and practise book}

### 2014-02-11 paper.tex
Added mention of the purpose of Rs, edited reviewer comments

@@
 Measurements of the inter-electrode impedance were made using a Tektronix TPS2014 DSO with four fully isolated and floating channels; an Agilent 33220A Function Generator; and a desktop PC controlling the instruments via Python 2.7.
+
+It should be noted that the resistive mesh created in this step models only the restitivity of the solution bulk.
+This means that no resistive contribution from the electrode/electrolyte interface is included in these measurements as voltage measurements are always across pairs of non-driven electrodes.
+We determine the fixed resistance of a single inteface, $R_{S}$, when fitting parameters to the displacement component.
 }
@@
 
-\pagebreak
+%\pagebreak
 \section{Displacement Parameters}
@@
     \caption{Magnitude of interfacial impedance between electrodes 2 and 7 against the frequency of a sine wave stimulus for six concentrations of PBS.
-The slope of the CPE is visible the left, whereas the resistance due to the solution bulk appears on the right.
+The slope of the CPE is visible the left, whereas the resistance due to $R_{S+bulk}$ appears on the right.
 Traces represent simulated data while markers represent measured values.}
@@
 {\color{OliveGreen}
-    Item 1\\
     This response has concerned us and we have subsequently invested considerable effort in broadening our search of published state-of-the-art.
@@
 {\color{OliveGreen}
-    Item 2\\
     Correct, there are many published interfacial models.
@@
 {\color{OliveGreen}
-    Item 3\\
     We have lumped the effects of polarisation into the response of the displacement element in the model (CPE).
@@
 {\color{OliveGreen} 
-    Item 4\\
     We are not so much interested in knowing the resistivity of the solution as we are in knowing the resistance between any pair of electrodes for the specific electrode array.
@@
 {\color{OliveGreen}
-    Item 5\\
     Relevant Faradaic reactions, both reversible and irreversible, have been added both to the displacement/polarisation and Faradaic sections.
@@
 {\color{OliveGreen} 
-    Item 6\\
     Graphs redrawn with a wider range of shading to help identify traces and referenced on page 3 (now figure \ref{fig:CPE_Phase}).
@@
 {\color{OliveGreen}
-    Item 7\\
     The measurements involving the back-to-back diodes are those measuring the contribution from irreversible Faradaic reactions.
@@
 {\color{OliveGreen}
-    Item 8\\
     We have addressed this discrepancy on page 5.
@@
 {\color{OliveGreen}
-    Item 9\\
     We have encouraged the reader to review ScottSingle2013 in order to understand the interpretation of the given parameters. 
@@
 {\color{OliveGreen}
-    Item 10\\
     Added a new figure to show the current density during CPE measurement.
@@
 {\color{OliveGreen}
-    Item 11\\
     Added missing details of instrumentation used to conduct inter-electrode resistance measurements and clarified their reuse for displacement measurements.
@@
 {\color{OliveGreen}
-    Item 12\\
-    Have reworded this slightly to convey that the shift in the CPE response is small relative to the shift in the resistance in the solution bulk.
+    This has been reworded to convey that the shift in the CPE response is small relative to the shift in the resistance in the solution bulk.
 We are referring to a relative difference, a gain in conductivity as a factor of the current conductivity.
-    {\color{red} Help! I don't know how better to explain this, The difference between 9 000 000 and 1 000 000 000 is small compared to the difference between 20 and 2000}
 }\\
@@
 {\color{OliveGreen} 
-    Item 13\\
     Sure, we have added a quick interpretation for the parameters $m$ and $k$ in the text.
@@
 {\color{OliveGreen}
-    Item 14\\
     {\color{Red} Should be easy to do, perhaps I make a second graph that shows more of the time data}
@@
 {\color{OliveGreen}
-    Item 15\\
     Thank you, we have updated discussion of Faradaic Parameters to include the results from what is now figure~\ref{fig:faradaic_currentVsTime}.
@@
 {\color{OliveGreen}
-    Item 16\\ 
     Graph of sheep response to displacement stimulus has been updated to include four separate measurements taken on the second day of sheep measurement.
@@
 {\color{OliveGreen}
-    Item 17\\
-    {\color{Red} Revise poor use of words (perhaps relating to model elements/physical elements). Perhaps separate the results and discussion sections.} 
-    No response yet.
+    With respect to the comment on poor attention to detail and innaccurate use of words, we have revised the manuscript to include more detail both in regards to experimental setup, the electrochemistry and model elements.
+We have chosen to mix the discussion with results as the model parameters are derived along with the measurments, which are required before moving to each subsiquent step.
 }\\
@@
 {\color{OliveGreen}
-    Item 18\\
-    Instrumentation for CPE measurements have been added.
-I have also added current density and peak stimulus voltage information to displacement current measurement.
-[TODO: Calculate and add total charge transfer for both CPE and Faradaic].
+    We have added maximum and minimum current density calculations, peak stimulus voltage information and added a plot showing the amount of charge injected during measurment of displacement currents.
 }\\
@@
     Item 19\\
-    {\color{Red} This represents a lot of work to redo the measurements.
-Perhaps we make it clear that we don't know the electrochemistry side, that it's simply out of our depth, and any hypothesis we draw based on electrochemistry may harm the validity of our work.
-If we explain more exactly the proceedure we took so as to be more repeatable and hint that we're not interested at this point on the electrochemistry, that we only wish to make the model behave like the solution.}
-    No response yet.
+    This manuscript is primarily concerned with modelling the behaviour of electrodes in a bath of saline.
+Phisiological solutions of saline are routinely used to mimic the impedances seen by an implant by designers in order to verify their designs and test any control logic.
+In spinal cord stimulation 0.1X PBS is used but there is no way to tell how accurate a phantom such a solution is for the a real spinal column.
+This paper seeks to answer that question in a way that allows implant designers to broadly compare the behavior of their in-vitro experiments with in-vivo behavior.
+While controlling the partial pressure of oxygen in the PBS bath definitely appears to be of importance to the general field of in-vivo electrode modelling, we feel the results within this manuscript are of importance to those using solutions of PBS to verify electrical designs and models.
 }
@@
 {\color{OliveGreen}
-    Item 20\\
     Fixed.
@@
 {\color{OliveGreen}
-    Item 22\\
     Footnote added to sentence in question that describes our defining of $R_{sri}$ in terms of $R_{eri}$. 
@@
 {\color{OliveGreen}
-    Item 23\\
-    Thank you, have reworded the caption in Figure 4 to more accurately describe the situation.
+    The caption in Figure 4 has been reworded to more accurately describe the situation. Yes this graph is showing the CPE in series with both the inter-electrode resistance and $R_{S}$.
 }\\
@@
 {\color{OliveGreen} 
-    Item 24\\
-    {\color{Red} His reasoning is correct, it is because the impedance does not match at high freq.
-I had the graph with dotted lines to show the difference that Rs made.
-Jonathan, you thought this was too messy and it was removed, should it be added back in again?}
-% No sadly not interesting just related to the fact that interface has its own internal resitance.
-    No response yet.
+    The requirement of $R_{S}$ has been clarified at the end of Section II. This was not made very clear in our original submission, thank you for pointing this out.
 }\\
@@
 {\color{OliveGreen}
-    Item 25\\
-% Because consistent with prev pub plus it doesnt matter which STRESS THIS.
-    {\color{Red} Explain more clearly why electrodes 2 and 7 were chosen (to avoid end effects)}
-    No response yet.
+    The choice of electrodes was arbitrary.
+We felt that electrodes 2 and 7 were a good compromise between good separation and avoiding any end effects.
+This was the same pair as used by Scott \& Single 2013 from which we have based our measurements.
 }\\
@@
 {\color{OliveGreen}
-    Item 26\\
-    {\color{Red} We aren't sure of either but further work into the surface area of the electrode via ottonisation should reveal whether surface area is a factor - read: followup publication}
-    No response yet.
+    We have cleaned this statement up. See end of section III.
 }\\
@@
 {\color{OliveGreen} 
-    Item 27\\
-    {\color{Red} Investigate other forms, comment on why this has been chosen}
-    No response yet.
+    That is correct. This equation is the standard diode equation found in any electronic engineering textbook.
 }\\
@@
 {\color{OliveGreen}
-    Item 28\\
-    The mention of the use of electrodes 2 and 6 was a mistake. We actually used electrodes 3 and 7 due to damage to the electrode array we were using. See updated explination on page 4.
+    Again a totally arbitrary choice, we fit the model to whichever pair we use.
+We actually used electrodes 7 and 3, the mention of electrodes 2 and 6 was a mistake.
+Thank you for bringing that to our attention.
 }\\
@@
 {\color{OliveGreen} 
-    Item 29\\
     Changed mention of inductive stirrer to magnetic stirrer.
@@
 {\color{OliveGreen} 
-    Item 30\\
     Removed reference to the CPE element and have better quantified the settling period in that footnote.
@@
 {\color{OliveGreen}
-    Item 31\\
     Yes, that is better - thank you.
@@
 {\color{OliveGreen}
-    Item 32\\
     Changed references to the CPE model element in the conclusion to the electrical double layer.
@@
 one of the goals of one of our industrial partners.
-    {\color{Red} True, a feeble comment on PBS match.
-It may be worth noting the phase of measured data in sheep indicating that the sheep itself was reactive.
-There may be data at those lower points (to justify extrapolating), check.
-Have we measured the electrodes again since inserting into the sheep, I think we have but check.
-Read the paper by Troyk, comment on applicability.
-Maybe there is test data between sheep in saline showing the electrodes returning to normal, check.}.
+
     No response yet.

### 2014-02-11 paper.tex
Lingering changes

--- 2014-02-11 paper.tex
@@
     \begin{center}
-        \includegraphics{graphics/chargeInjectionVsFrequency_magnitude}
+        \includegraphics{graphics/chargeInjectionVsFrequency.pdf}
     \end{center}
-    \caption{\color{blue} Charge injected per phase during CPE measurement for each of the six concentrations of PBS. Calculated using a geometric surface area of 10\thinspace mm$^{2}$}
+    \caption{\color{blue} Charge injected during CPE measurement for each of the six concentrations of PBS. Calculated using an effective surface area of 14\thinspace mm$^{2}$}
     \label{fig:chargeInjectionVsFrequency}
@@
     \color{blue}
-    The geometric current density during measurements peaked at 22.59\thinspace mA/cm$^{2}$ at 5300\thinspace kHz in 1.0X PBS and fell as low as 27.66\thinspace $\mu$A/cm$^{2}$ at 50\thinspace mHz in 0.025X PBS.
-Charge injection per phase is shown in figure~\ref{fig:chargeInjectionVsFrequency} for each solution.
+Current density during measurements peaked at $11.5\thinspace A/m^{2}$ at 10\thinspace kHz in 1.0X PBS and fell as low as $0.0141\thinspace A/m^{2}$ at 50\thinspace mHz in 0.025X PBS.
+The charge injected is shown in figure~\ref{fig:chargeInjectionVsFrequency}.
 The stimulus waveform was set at 300\thinspace mV (peak) at each measurement point. The measurement instruments used are the same as those used to measure the inter-electrode resistance.
@@
 The study complied with the Australian Code of Practice for the Care and Use of Animals for Scientific Purposes.
-{\color{blue} Four measurements taken at regular invervals over a period of 30 minutes} are presented in figures~\ref{fig:displacement_sheepCPEMagnitude} and~\ref{fig:displacement_sheepCPEPhase} on top of the array of traces for saline taken from figures~\ref{fig:CPE_Magnitude} and~\ref{fig:CPE_Phase}.
+The measurements are presented in figures~\ref{fig:displacement_sheepCPEMagnitude} and~\ref{fig:displacement_sheepCPEPhase} on top of the array of traces for saline taken from figures~\ref{fig:CPE_Magnitude}
+and~\ref{fig:CPE_Phase}.
 Although it is clear that there are complications in vivo, a 0.25X PBS saline offers a good approximation to the resistive part of the trace.
@@
     \end{center}
-    \caption{Comparison between the magnitude of CPE in live sheep {\color{blue}(blue error bars)} against each of the PBS traces from figure~\ref{fig:CPE_Magnitude} (grey lines) and a simulated fit to the sheep data (red trace).}
+    \caption{Comparison between the magnitude of CPE in live sheep (blue circles) against each of the PBS traces from figure~\ref{fig:CPE_Magnitude} (grey lines) and a simulated fit to the sheep data (red trace).}
     \label{fig:displacement_sheepCPEMagnitude}
@@
     \end{center}
-    \caption{Comparison between the phase response of the CPE in live sheep {\color{blue}(blue error bars)} against each of the PBS traces taken from figure~\ref{fig:CPE_Phase} (grey lines) and a simulated fit to the sheep data (red trace).}
+    \caption{Comparison between the phase response of the CPE in live sheep (blues circles) against each of the PBS traces taken from figure~\ref{fig:CPE_Phase} (grey lines) and a simulated fit to the sheep data (red trace).}
     \label{fig:displacement_sheepCPEPhase}
@@
     We have encouraged the reader to review ScottSingle2013 in order to understand the interpretation of the given parameters.
+{\color{red} Should I just say they are resistances of elements in a resistor mesh?}
 }\\
@@
     Item 12\\
-    Have reworded this slightly to convey that the shift in the CPE response is small relative to the shift in the resistance in the solution bulk.
-We are referring to a relative difference, a gain in conductivity as a factor of the current conductivity.
-    {\color{red} Help! I don't know how better to explain this, The difference between 9 000 000 and 1 000 000 000 is small compared to the difference between 20 and 2000}
+    This has been reworded to improve clarity, see end of section III. We are referring to relative shifts as opposed to absolute impedances.
 }\\
@@
     Item 16\\ 
-    Graph of sheep response to displacement stimulus has been updated to include four separate measurements taken on the second day of sheep measurement.
-The first day gave results typical of these but we ran into connection problems leading to intermittent data hence they have been omitted.
+    {\color{Red} Leave sheep in but perhaps show the second measurement (day 1) if possible (4th reviewer found sheep correlation to PBS result interesting).
+Would a separate sheep measurement graph be of use showing all sheep results?
+Jonathans response: Put more sheep data in, put some error bars on.}
+    No response yet.
 }\\
@@
     Item 28\\
-    The mention of the use of electrodes 2 and 6 was a mistake. We actually used electrodes 3 and 7 due to damage to the electrode array we were using. See updated explination on page 4.
+    {\color{Red} Took resistance measurements of lead and electrode 2 is open circuit inside the electrode. Must have meant 3 and 7, due to damaged electrode 2}
+    No response yet.
 }\\
@@
     Item 36\\
-    {\color{Red} Perhaps Troyk could be added. References have been extended to include a Masters Theses and Neuroprosthetics: Theory and practise book}
-}
+    {\color{Red} Perhaps Troyk could be added. A search for textbook knowledge and more published state of the art should uncover more references}
+    No response yet.
+}\\
 

### 2014-02-11 paper.tex
Finished addressing reviewers comments. Edited faradaic response discussion

--- 2014-02-11 paper.tex
@@
 \author{Mark~H.~Jones and Jonathan~Scott,~\IEEEmembership{Senior Member,~IEEE}
-
 \thanks{Mark~H.~Jones is with the School of Electronic Engineering, University of Waikato, New Zealand, e-mail: markjones112358@gmail.com.}%
-
 \thanks{Jonathan Scott is with the School of Electronic Engineering, University of Waikato, New Zealand.}
-
 }
@@
 \begin{abstract}
+
     We report how the impedance presented by a platinum electrode scales with the concentration of phosphate buffered saline (PBS).
@@
 \section{Introduction}
+
 \IEEEPARstart{T}{here} is considerable interest in the electrical modelling of electrodes. \cite{Cogan2008,Troy2006}
@@
 Electrodes in the laboratory are typically tested in a saline solution selected to mimic the circumstances in which they will operate when implanted.
-{
-    \color{blue}
-    % Item 20
-A solution of Phosphate Buffered Saline (PBS) diluted to one-tenth concentration (0.1X) is common in the case of Spinal Cord Stimulators (SCS), while full concentration (1.0X) PBS is considered more representative of the situation in blood.
-}
+{\color{red} In an implanted setting there is no reference electrode and many of the well established electrochemical measurement regiemes do not apply.
+In this manuscript we measure the behaviour an electrode/electrolyte situation as it would be seen from an implant device.}
+
+{\color{blue} A solution of Phosphate Buffered Saline (PBS) diluted to one-tenth concentration (0.1X) is common in the case of Spinal Cord Stimulators (SCS), while full concentration (1.0X) PBS is considered more representative of the situation in blood.}
+
 In this manuscript we report how the parameters of a non-linear model change as the concentration of saline is varied.
@@
 
-{
-    \color{blue}
-It has been suggested that the primary coupling mechanism between platinum electrodes and physiological saline is the reversible evolution of gas, probably oxygen, at the platinum surface, which dissolves without bubble formation.\cite{Greatbatch1969} Understanding the exact mechanism of displacement or Faradaic charge transfer at the electrode surface is beyond the scope of this work.
-Rather we wish to characterise the electrode/electrolyte system in terms of parameters that may be fed into an electrical model.
-}
+{\color{blue} It has been suggested that the primary coupling mechanism between platinum electrodes and physiological saline is the reversible evolution of gas, probably oxygen, at the platinum surface, which dissolves without bubble formation.\cite{Greatbatch1969} Understanding the exact mechanism of displacement or Faradaic charge transfer at the electrode surface is beyond the scope of this work.
+Rather we wish to characterise the electrode/electrolyte system in terms of parameters that may be fed into an electrical model.}
 
@@
 
-%\pagebreak
 \section{Displacement Parameters}
-{
-    % Identifying reactions
-    \color{blue}
-Displacement currents are responsible for capacitive behaviour at interfacial boundaries.
+
+{\color{blue} Displacement currents are responsible for capacitive behaviour at interfacial boundaries.
     They are brought about by the redistribution of charge in response to applied fields, i.e.
-a charged electrode will attract or repel $Cl^{-}$ from its surface and reorientate polar molecules in the surrounding solution.
-This capacitive behaviour may also be a result of electrode polarisation in the form of reversible Faradaic reactions at the surface of the electrode.
-Such reactions involving water and platinum, as identified in \cite{Horch2004,Mohtashami2011}, include:
+a charged electrode will attract or repel $Cl^{-}$ from its surface and reorientate polar molecules in the surrounding solution.\cite{Merrill05} This capacitive behaviour may also be a result of electrode polarisation in the form of reversible Faradaic reactions at the surface of the electrode.
+Such reactions involving water and platinum, as identified in \cite{Horch2004,Mohtashami2011,Merrill05}, include:
 \begin{eqnarray}
@@
 \end{eqnarray}
-
-This displacement mechanism is capable of transferring charge between electrical and biological systems without damaging electrodes or tissue. \cite{Horch2004}
-This behaviour is modelled by way of a Constant Phase Element (CPE); also known as a fractional capacitor.
-}
-{
-    \color{blue}
-For simulation purposes this element is realised as an array of R-C branches.~\cite{ScottSingle2013,Morrison59,Elwakil10} where the value of each R-C pair is chosen to set the slope of impedance relative to frequency.
-The placement of R-C pairs within the CPE is determined by Morrison's parameters $m$ and $k$, where $k$ determines the spacing, or density, of R-C branches and $m$ determines the resulting slope.
-}
+This displacement mechanism is capable of transferring charge between electrical and biological systems without damaging electrodes or tissue.\cite{Horch2004}
+This behaviour is modelled by way of a Constant Phase Element (CPE); also known as a fractional capacitor.}
+{\color{blue} For simulation purposes this element is realised as an array of R-C branches.~\cite{ScottSingle2013,Morrison59,Elwakil10} where the value of each R-C pair is chosen to set the slope of impedance relative to frequency.
+The placement of R-C pairs within the CPE is determined by Morrison's parameters $m$ and $k$, where $k$ determines the spacing, or density, of R-C branches and $m$ determines the resulting slope.}
 We measure displacement currents by sweeping the frequency of a sinusoidal stimulus across electrodes 2 and 7 of the Octrode while measuring the voltage between electrodes 2 and 3 (numbering shown in Fig.~\ref{fig:octrode}).
@@
     \color{blue}
-    The geometric current density during measurements peaked at 22.59\thinspace mA/cm$^{2}$ at 5300\thinspace kHz in 1.0X PBS and fell as low as 27.66\thinspace $\mu$A/cm$^{2}$ at 50\thinspace mHz in 0.025X PBS.
+    The geometric current density during measurements peaked at 22.59\thinspace mA/cm$^{2}$ at 10000\thinspace kHz in 1.0X PBS and fell as low as 27.66\thinspace $\mu$A/cm$^{2}$ at 50\thinspace mHz in 0.025X PBS.
 Charge injection per phase is shown in figure~\ref{fig:chargeInjectionVsFrequency} for each solution.
@@
 This uses the same data as the previous figure but has been processed so that each point represents the average of the final 24 current measurements at each step.
-Below 0.9\thinspace V it appears that the concentration of the solution had no identifiable effect on Faradaic conduction as the traces are not monotonic with concentration in this region.
-Between 0.9\thinspace V and 1.05\thinspace V (concentration dependent) a transition occurs which results in current conduction becoming dependent on solution concentration.
+Below 0.9\thinspace V it appears that the concentration of the solution had no identifiable effect on Faradaic conduction {\color{blue}as there is overlap between each trace and the mean values are not monotonic with concentration in this region}.
+Between 0.9\thinspace V and 1.05\thinspace V a transition occurs which results in current conduction becoming dependent on solution concentration.
 Above 1.05\thinspace V the traces diverge showing clear dependence upon concentration.
+{\color{blue} The point at which this transition occurs is determined by the concentration of saline, with lower concentrations transitioning earlier.
+A concentration of 0.0625X PBS causes a transition at around 0.95\thinspace V whereas electrodes in the 1.0X PBS solution transition somewhere between 1.0\thinspace and 1.05\thinspace V.
+The effect of transition can be seen in the green trace at 1.0\thinspace V where the error bar is wide due to the current shift being captured in the measurement at that voltage.
+Part of a transition with respect to time is visible in figure~\ref{fig:StepResponse_Faradaic} where the red trace drops uncharacteristically after the increment at around 600 seconds.}
 
@@
 {\color{OliveGreen}
-    This has been reworded to convey that the shift in the CPE response is small relative to the shift in the resistance in the solution bulk.
-We are referring to a relative difference, a gain in conductivity as a factor of the current conductivity.
+    This has been reworded to improve clarity, see end of section III. We are referring to relative shifts as opposed to absolute impedances.
 }\\
@@
 {\color{OliveGreen}
-    {\color{Red} Should be easy to do, perhaps I make a second graph that shows more of the time data}
-    No response yet.
+    See revised discussion on page 5.
 }\\
@@
 
-{\color{blue}
-Authors
-The aim of this paper, to find a SPICE model of implanted electrodes, is important and the results presented in the paper are interesting.
+{\color{blue} The aim of this paper, to find a SPICE model of implanted electrodes, is important and the results presented in the paper are interesting.
 However, as it stands the paper is not well written and must be revised.
 The weaknesses of the paper are an unclear structure, with results and discussion mixed, poor attention to detail and inaccurate use of words.\\
-{\color{OliveGreen}
-    With respect to the comment on poor attention to detail and innaccurate use of words, we have revised the manuscript to include more detail both in regards to experimental setup, the electrochemistry and model elements.
-We have chosen to mix the discussion with results as the model parameters are derived along with the measurments, which are required before moving to each subsiquent step.
-}\\
+{\color{OliveGreen}With respect to the comment on poor attention to detail and innaccurate use of words, we have revised the manuscript to include more detail both in regards to experimental setup, the electrochemistry and model elements.
+We have chosen to mix the discussion with results as the model parameters are derived along with the measurments, which are required before moving to each subsiquent step.}\\
 
@@
 0.05 Hz): what potential excursion occurred was it really a ``small signal''?\\
-{\color{OliveGreen}
-    We have added maximum and minimum current density calculations, peak stimulus voltage information and added a plot showing the amount of charge injected during measurment of displacement currents.
-}\\
+{\color{OliveGreen}We have added maximum and minimum current density calculations, peak stimulus voltage information and added a plot showing the amount of charge injected during measurment of displacement currents.}\\
 
@@
 The stirring arrangements ought to be exactly described too because liquid flow may be critical.\\
-{\color{OliveGreen}
-    Item 19\\
-    This manuscript is primarily concerned with modelling the behaviour of electrodes in a bath of saline.
+{\color{OliveGreen}This manuscript is primarily concerned with modelling the behaviour of electrodes in a bath of saline.
 Phisiological solutions of saline are routinely used to mimic the impedances seen by an implant by designers in order to verify their designs and test any control logic.
@@
 This paper seeks to answer that question in a way that allows implant designers to broadly compare the behavior of their in-vitro experiments with in-vivo behavior.
-While controlling the partial pressure of oxygen in the PBS bath definitely appears to be of importance to the general field of in-vivo electrode modelling, we feel the results within this manuscript are of importance to those using solutions of PBS to verify electrical designs and models.
-}
+While controlling the partial pressure of oxygen in the PBS bath definitely appears to be of importance to the general field of in-vivo electrode modelling, we feel the results within this manuscript are of importance to those using solutions of PBS to verify electrical designs and models.}
 
@@
 1. P1, top RH col. ``0.1X'' ought to be explained when you first use this form.\\
-{\color{OliveGreen}
-    Fixed.
-}\\
+{\color{OliveGreen}Fixed.}\\
 
@@
 If you are not going to do so, you might help them by saying something like ``Readers are advised to see [4] to understand the meaning of the parameters in Table II''.\\
-{\color{OliveGreen}
-    Item 21\\
-    {\color{Red} Leave until the end, if we have the space then we put it in, otherwise put a better reference to ScottSingle2013}
-    We have advised the reader to read ScottSingle2013 to understand the interpretation of the mesh generation parameters, where they would find the radial volume model.
-}\\
+{\color{OliveGreen}Unfortunately there is little room in the manuscript as it stands for extra figures.
+We have advised the reader to read ScottSingle2013 to understand the interpretation of the mesh generation parameters, where they would find the radial volume model.}\\
 
 3. You say (p2 line 43) that there are 2 independent scaling factors. Is Rli independent or not? If not, why input it in Table II?\\
-{\color{OliveGreen}
-    Footnote added to sentence in question that describes our defining of $R_{sri}$ in terms of $R_{eri}$. 
-}\\
+{\color{OliveGreen}Footnote added to sentence in question that describes our defining of $R_{sri}$ in terms of $R_{eri}$.}\\
 
@@
 Is it the total series resistance or have you already subtracted the volume resistance (found in section II)?\\
-{\color{OliveGreen}
-    The caption in Figure 4 has been reworded to more accurately describe the situation. Yes this graph is showing the CPE in series with both the inter-electrode resistance and $R_{S}$.
-}\\
+{\color{OliveGreen}The caption in Figure 4 has been reworded to more accurately describe the situation.
+Yes this graph is showing the CPE in series with both the inter-electrode resistance and $R_{S}$.}\\
 
@@
 If so, this would be very interesting and I would like you to bring this out.\\
-{\color{OliveGreen} 
-    The requirement of $R_{S}$ has been clarified at the end of Section II. This was not made very clear in our original submission, thank you for pointing this out.
-}\\
+{\color{OliveGreen}The requirement of $R_{S}$ has been clarified at the end of Section II. This was not made very clear in our original submission, thank you for pointing this out.}\\
 
 6. P2, col 2, line 24: why 2 \& 7?\\
-{\color{OliveGreen}
-    The choice of electrodes was arbitrary.
+{\color{OliveGreen}The choice of electrodes was arbitrary.
 We felt that electrodes 2 and 7 were a good compromise between good separation and avoiding any end effects.
-This was the same pair as used by Scott \& Single 2013 from which we have based our measurements.
-}\\
+This was the same pair as used by Scott \& Single 2013 from which we have based our measurements.}\\
 
@@
 Please make clearer.\\
-{\color{OliveGreen}
-    We have cleaned this statement up. See end of section III.
-}\\
+{\color{OliveGreen} We have cleaned this statement up. See end of section III.}\\
 
 8. You do not explain why, in eq 1, you want to use this form. Why nVt? I suppose it isso you can use a standard SPICE form rather than this suits the data. Is that right?\\
-{\color{OliveGreen} 
-    That is correct. This equation is the standard diode equation found in any electronic engineering textbook.
-}\\
+{\color{OliveGreen} That is correct. This equation is the standard diode equation found in any electronic engineering textbook.}\\
 
 9. P3, col 2, line 31: why 2 and 6?\\
-{\color{OliveGreen}
-    Again a totally arbitrary choice, we fit the model to whichever pair we use.
+{\color{OliveGreen} Again a totally arbitrary choice, we fit the model to whichever pair we use.
 We actually used electrodes 7 and 3, the mention of electrodes 2 and 6 was a mistake.
-Thank you for bringing that to our attention.
-}\\
+Thank you for bringing that to our attention.}\\
 
 10. P3, col 2, line 36. I guess you mean what is usually called a Magnetic Stirrer. Not ``inductive'' surely?\\
-{\color{OliveGreen} 
-    Changed mention of inductive stirrer to magnetic stirrer.
-}\\
+{\color{OliveGreen} Changed mention of inductive stirrer to magnetic stirrer.}\\
 
 11. P3 footnote. ``The response of the CPE'': this is confusing! Surely this is the response of a pair of electrodes? The CPE is an element of your model.\\
-{\color{OliveGreen} 
-    Removed reference to the CPE element and have better quantified the settling period in that footnote.
-}\\
+{\color{OliveGreen}Removed reference to the CPE element and have better quantified the settling period in that footnote.}\\
 
 12. Fig 11 legend ``Simulated and measured response of the interface model''. Surely you mean ``Simulated response of the interface model compared to measurement from the electrodes''?\\
-{\color{OliveGreen}
-    Yes, that is better - thank you.
-}\\
+{\color{OliveGreen} Yes, that is better - thank you.}\\
 
 13. P5, col 2, line 46 ``the CPE is setting''. Again, you are confusing an element of your model with reality.\\
-{\color{OliveGreen}
-    Changed references to the CPE model element in the conclusion to the electrical double layer.
-}\\
+{\color{OliveGreen}Changed references to the CPE model element in the conclusion to the electrical double layer.}\\
 
@@
 Troyk published an interesting paper with measurement from electrodes in brain of zebra finches which showed that anomalous characteristics in vivo vanished as soon as the electrodes were returned to PBS, implying that the phenomenon was not due to some biofilm deposited on the electrodes.\\
-{\color{OliveGreen}
-    Item 33\\
-% We can dial up shift in cpe and bulk resistance to create a better match using available chemical reagenre.
-we hope to synth a superior phantom through combos of saline solvets and hydrolysed cellulose.
-we anticipate crateing a superios phantom using.
-one of the goals of one of our industrial partners.
-
-    No response yet.
-}\\
+{\color{OliveGreen} The extrapolation of CPE data from the in-vivo measurements has been removed.
+We have a couple of ideas as to why the resistive and displacement components of the in-vivo measurements do not match the saline solution, however we aren't willing to add those here until we have investigated the behaviour further.
+We hope to answer this questoin in part by mixing saline solutions with varous solvents and hydrolised cellulose in an attempt to create a closer and more broadband match to the in-vivo measurements.
+In effect we are hoping to create a recipe that allows our industrial partners to dial-up a given impedance response for implant testing purposes.
+We had not thought to measure the electrodes again in PBS after the in-vivo measurements but this is certainly something we will aim for if we have the chance in future, thank you.
+The electrodes we used were steralised immediately after the measurements made here.}\\
 }
@@
 \subsection*{Reviewer 4}
-{\color{blue}
-In this manuscript, the authors studied the impedance of a commercial electrode array as a function of concentration of phosphate buffered saline (PBS), both through simulation and empirical measurements, and compared those results to the impedance measured when the electrode array was implanted into a sheep's spinal cavity.
+
+{\color{blue} In this manuscript, the authors studied the impedance of a commercial electrode array as a function of concentration of phosphate buffered saline (PBS), both through simulation and empirical measurements, and compared those results to the impedance measured when the electrode array was implanted into a sheep's spinal cavity.
 From this comparison, they concluded that the current practice of testing spinal cord stimulator in 0.1x of physiologically normal saline is adequate but suggest that no single concentration of PBS captures the frequency dependence of the in vivo measured impedance.\\
@@
 Much of the underlying theory and development of parameters appear without informing the reader of their purpose or how they were calculated and/or measured.
-For example, the parameters in Table 2 (and reported to be in Figure 3) are not explained and what their relationship to the remainder of the manuscript is not provided.
+For example, the parameters in Table 2 (and reported to be in Figure 3) are not explained and what their relationship to the remainder of the manuscript is not provided.\\
+{\color{OliveGreen} We have expanded the explanation in the manuscript, and referred interested readers to the source.}\\
 
-{\color{OliveGreen}
-    Item 34\\
-    {\color{Red} Explain parameters in table two better or refer readers to ScottSingle2013}
-    We have expanded the explanation in the manuscript, and referred interested readers to the source.
-}
 To make this manuscript more approachable to a wider audience, I recommend the authors more fully develop Sections II, III, and IV.
-Further, they should explain their testing in terms of standard electrochemical characterization, detailing their counter, working, and reference electrodes used in measuring impedance.
-{\color{OliveGreen}
-    Item 35\\
-% No reference elect possible in an implated scenario.
-Much of problem stems fro trad.
-electchem are inepplicable or impodssible.
-much or ou rreviewers arises fro fact that we are operating ni  an scenario far fro trad electrochem labs.
-    {\color{Red} Try to include any relevant electrochemical information, find out what that is first}
-    No response yet.
-}
+Further, they should explain their testing in terms of standard electrochemical characterization, detailing their counter, working, and reference electrodes used in measuring impedance.\\
+{\color{OliveGreen} Our approach arises from the fact that reference electrodes are not possible in an implanted scenario and that implant electrode arrays such as is used in this work do not have specifically designed counter or working electrodes.
+We have added a statement to this effect in the introduction.
+We feel that many of the questions or concerns arrising from the reviewers stems from the fact that we are operating in a scenario far from traditional electrochemistry labs.}\\
+
 As part of this expansion, the references should be increased beyond the present ten references.
@@
 al), the information contained in these references are not effectively used to support the authors’ work.\\
-{\color{OliveGreen}
-    Item 36\\
-% In response to numersios reviewese commnets we have added citations we hope we have more thoroughly put more thoro pointers to the literature in  nour manuscript...
-After extensice ...
-we have added citations
-    {\color{Red} Perhaps Troyk could be added. References have been extended to include a Masters Theses and Neuroprosthetics: Theory and practise book}
-}
+{\color{red} Find places for Merrill and Kane. Jonathan: Cogan, where can we use it? I don't have access  to this paper.}
+{\color{OliveGreen} In response the numerous reviewee comments we have added more citations. We hope we have more thorough pointers to the literature where appropriate in our literature.}\\
 
@@
 Presumably, the second version of the labels should be 0.65, 0.75, ..., 1.05.\\
-{\color{OliveGreen}
-    Item 37\\
-    Thank you very much. See updated figure (now figure~\ref{fig:faradaic_currentVsVoltage}).
-}\\
+{\color{OliveGreen}Thank you very much. See updated figure (now figure~\ref{fig:faradaic_currentVsVoltage}).}\\
+
 }

### 2014-02-11 paper.tex
Edits with Jonathan

@@
 
-Electrodes in the laboratory are typically tested in a saline solution selected to mimic the circumstances in which they will operate when implanted.
-{\color{red} In an implanted setting there is no reference electrode and many of the well established electrochemical measurement regiemes do not apply.
-In this manuscript we measure the behaviour an electrode/electrolyte situation as it would be seen from an implant device.}
+{\color{blue} Electrodes in the laboratory are typically tested in a saline solution selected to mimic the circumstances in which they will operate when implanted.
+In an implanted setting there is no reference electrode and many of the well established electrochemical measurement regimes do not apply.
+In this manuscript we measure the behaviour an electrode/electrolyte situation as it would be seen from an implant device.
 
-{\color{blue} A solution of Phosphate Buffered Saline (PBS) diluted to one-tenth concentration (0.1X) is common in the case of Spinal Cord Stimulators (SCS), while full concentration (1.0X) PBS is considered more representative of the situation in blood.}
+A solution of Phosphate Buffered Saline (PBS) diluted to one-tenth concentration (0.1X) is common in the case of Spinal Cord Stimulators (SCS), while full concentration (1.0X) PBS is considered more representative of the situation in blood.}
 
@@
     \color{blue}
-    The geometric current density during measurements peaked at 22.59\thinspace mA/cm$^{2}$ at 10000\thinspace kHz in 1.0X PBS and fell as low as 27.66\thinspace $\mu$A/cm$^{2}$ at 50\thinspace mHz in 0.025X PBS.
+    The geometric current density during measurements peaked at 22.6\thinspace mA/cm$^{2}$ at 10000\thinspace kHz in 1.0X PBS and fell as low as 27.6\thinspace $\mu$A/cm$^{2}$ at 50\thinspace mHz in 0.025X PBS.
 Charge injection per phase is shown in figure~\ref{fig:chargeInjectionVsFrequency} for each solution.
@@
 It is apparent from this trace that the temporal response of the CPE does not match the transient decay curves seen in the Faradaic measurements, something the CPE should predict.
-These transient decay curves appear to have time-constant that decreases with each subsequent measurement.
+These transient decay curves appear to have a time-constant\footnote{We use the term ``time-constant'' although a CPE does not have a simple exponential time-domain response.} that decreases with each subsequent measurement.
 This variable time-constant phenomena is especially clear when looking back at figure~\ref{fig:CPE_currentVsTime}.
 Although the Faradaic response transients appear to approach the time-constant predicted by the CPE, there is still behaviour not completely described by the CPE.
+
 The match between fitted diode parameters ($n$ and $i_{0}$) and the measurement data 64 seconds after each voltage increment has been plotted in figure~\ref{fig:faradaic_currentVsVoltage}.
@@
 {\color{OliveGreen}
-    This response has concerned us and we have subsequently invested considerable effort in broadening our search of published state-of-the-art.
-Where possible we have included references to electrochemistry literature from any areas we are dealing with in this revision.
-During this expansion we were unable to find anything that subtracts from the novelty of this work.
-That said, our work is concerned primarily with the electrical side of an interface impedance and more specifically with that of an implanted electrode.
+    This response has concerned us and we subsequently invested considerable effort in broadening our search of the literature.
+We have included some new references to the electrochemistry literature.
+This work is concerned primarily with the electrical side of an interface and more specifically with that of an implanted electrode.
 Our intention is to be able to encapsulate the electrical aspect of the interface and surrounding electrolyte in an equivalent electrical circuit, regardless of the chemistry at play.
+Nevertheless, we were unable to find anything that subtracts from the novelty of this work that lies in the relationship between impedance and electrolytes. 
 }\\
@@
 {\color{OliveGreen}
-    Correct, there are many published interfacial models.
-This model differentiates itself from those by being compact.
-Compact in the sense that it can be entered into any common electronic circuit simulator and used to make predictions about impedance.
-This is especially important for elecronic engineers designing medical impalant devices.
+    There are many published interfacial models.
+This model differentiates itself from all previous models by being compact, in the mathematical-modeling meaning of that word, implying that it can be entered into any common electronic circuit simulator and used to make predictions about impedance.
+This is especially important for elecronic engineers designing medical implant devices.
 }\\
@@
 {\color{OliveGreen}
-    Relevant Faradaic reactions, both reversible and irreversible, have been added both to the displacement/polarisation and Faradaic sections.
+    As a matter of interest, relevant Faradaic reactions, both reversible and irreversible, have been added both to the displacement/polarisation and Faradaic sections.
+Nevertheless, we do not need to understand any specific reactions that occur, as we confine our attention to the electrical impedance properties.
+We have added, as the second paragraph of the introduction, a clarification of the goals of the work.
 }\\
@@
 {\color{OliveGreen}
-    The measurements involving the back-to-back diodes are those measuring the contribution from irreversible Faradaic reactions.
-These measurements involve two active electrodes while the remaining electrodes and the electrolyte have a floating potentials.
+Measurements were made up to 1.2V, refer to figure 10 for example. The results are naturally symmetrical.
+%The measurements involving the back-to-back diodes are those measuring the contribution from irreversible Faradaic reactions.
+These measurements involve two active electrodes while the remaining electrodes and the electrolyte have a floating potential.
 Sweeping the voltage from -1.2V to +1.2V in this case would be the equivalent of swapping the terminals halfway through the sweep.
@@
     Graph of sheep response to displacement stimulus has been updated to include four separate measurements taken on the second day of sheep measurement. 
-The first day gave results typical of these but we ran into connection problems leading to intermittent data hence they have been omitted.
 }\\
@@
 {\color{OliveGreen}With respect to the comment on poor attention to detail and innaccurate use of words, we have revised the manuscript to include more detail both in regards to experimental setup, the electrochemistry and model elements.
-We have chosen to mix the discussion with results as the model parameters are derived along with the measurments, which are required before moving to each subsiquent step.}\\
+We have chosen to mix the discussion with results as the model parameters are derived along with the measurments, which are required before moving to each subsequent step.
+This arrangement is common in modeling papers in EE.}\\
 
@@
 0.05 Hz): what potential excursion occurred was it really a ``small signal''?\\
-{\color{OliveGreen}We have added maximum and minimum current density calculations, peak stimulus voltage information and added a plot showing the amount of charge injected during measurment of displacement currents.}\\
+{\color{OliveGreen}We have fully addressed this issue.
+We have added maximum and minimum current density calculations, peak stimulus voltage information and added a plot showing the amount of charge injected during measurment of displacement currents.}\\
 
@@
 If you are not going to do so, you might help them by saying something like ``Readers are advised to see [4] to understand the meaning of the parameters in Table II''.\\
-{\color{OliveGreen}Unfortunately there is little room in the manuscript as it stands for extra figures.
+{\color{OliveGreen}We agree absolutely.
+Unfortunately there is little room in the manuscript as it stands for extra figures.
 We have advised the reader to read ScottSingle2013 to understand the interpretation of the mesh generation parameters, where they would find the radial volume model.}\\
@@
 For example, the parameters in Table 2 (and reported to be in Figure 3) are not explained and what their relationship to the remainder of the manuscript is not provided.\\
-{\color{OliveGreen} We have expanded the explanation in the manuscript, and referred interested readers to the source.}\\
+{\color{OliveGreen} We have greatly expanded the explanation in the manuscript, and referred interested readers to the source.}\\
 
@@
 Further, they should explain their testing in terms of standard electrochemical characterization, detailing their counter, working, and reference electrodes used in measuring impedance.\\
-{\color{OliveGreen} Our approach arises from the fact that reference electrodes are not possible in an implanted scenario and that implant electrode arrays such as is used in this work do not have specifically designed counter or working electrodes.
+{\color{OliveGreen} Our approach arises from the fact that reference electrodes are not possible in an implanted scenario and that implant electrode arrays such as is used in this work do not have specifically designed counter and working electrodes.
 We have added a statement to this effect in the introduction.
@@
 al), the information contained in these references are not effectively used to support the authors’ work.\\
-{\color{red} Find places for Merrill and Kane. Jonathan: Cogan, where can we use it? I don't have access  to this paper.}
+%{\color{red} Find places for Merrill and Kane. Jonathan: Cogan, where can we use it? I don't have access  to this paper.}
 {\color{OliveGreen} In response the numerous reviewee comments we have added more citations. We hope we have more thorough pointers to the literature where appropriate in our literature.}\\

### 2014-02-18 paper_marsden.tex
Created Marsden version with no reviewer comments and no colourisation of revision edits

--- 2014-02-11 paper.tex
@@
 
-{\color{blue} Electrodes in the laboratory are typically tested in a saline solution selected to mimic the circumstances in which they will operate when implanted.
+Electrodes in the laboratory are typically tested in a saline solution selected to mimic the circumstances in which they will operate when implanted.
 In an implanted setting there is no reference electrode and many of the well established electrochemical measurement regimes do not apply.
@@
 
-A solution of Phosphate Buffered Saline (PBS) diluted to one-tenth concentration (0.1X) is common in the case of Spinal Cord Stimulators (SCS), while full concentration (1.0X) PBS is considered more representative of the situation in blood.}
+A solution of Phosphate Buffered Saline (PBS) diluted to one-tenth concentration (0.1X) is common in the case of Spinal Cord Stimulators (SCS), while full concentration (1.0X) PBS is considered more representative of the situation in blood.
 
 In this manuscript we report how the parameters of a non-linear model change as the concentration of saline is varied.
-{\color{blue} We refine a series of measurements compatible with commercially available medical electrodes in physiological saline that allow us to describe the impedance with minimal parameters.} We place these parameters in context with a biological measurement made in the spinal cavity of a live sheep.
+We refine a series of measurements compatible with commercially available medical electrodes in physiological saline that allow us to describe the impedance with minimal parameters.
+We place these parameters in context with a biological measurement made in the spinal cavity of a live sheep.
 
@@
 The electrical interface model of \cite{Franks2005} and \cite{ScottSingle2013} has two parts, a displacement branch and a Faradaic branch.
-{\color{blue} While Scott and Single \cite{ScottSingle2013} incorporate a memristor into their model, it has been omitted here for simplicity.
-Its contribution is limited to situations where diffusion limited Faradaic reactions come into play, a situation that stimulator implants are designed to avoid.}
+While Scott and Single \cite{ScottSingle2013} incorporate a memristor into their model, it has been omitted here for simplicity.
+Its contribution is limited to situations where diffusion limited Faradaic reactions come into play, a situation that stimulator implants are designed to avoid.
 
-{\color{blue} It has been suggested that the primary coupling mechanism between platinum electrodes and physiological saline is the reversible evolution of gas, probably oxygen, at the platinum surface, which dissolves without bubble formation.\cite{Greatbatch1969} Understanding the exact mechanism of displacement or Faradaic charge transfer at the electrode surface is beyond the scope of this work.
-Rather we wish to characterise the electrode/electrolyte system in terms of parameters that may be fed into an electrical model.}
+It has been suggested that the primary coupling mechanism between platinum electrodes and physiological saline is the reversible evolution of gas, probably oxygen, at the platinum surface, which dissolves without bubble formation.\cite{Greatbatch1969} Understanding the exact mechanism of displacement or Faradaic charge transfer at the electrode surface is beyond the scope of this work.
+Rather we wish to characterise the electrode/electrolyte system in terms of parameters that may be fed into an electrical model.
 
@@
 The ingredients of that stock solution are given in table~\ref{tab:PBSrecipe}.
-{
-    \color{blue}
-    % Item 11
 The pH level of the stock was measured, using a calibrated EDT Instruments BA-350 pH meter, to have a pH of 7.4. No pH adjustments were made to the derived solutions.
-}
+
 \begin{table}
@@
 Repeating that work, a resistor network that connects each of the eight electrodes is constructed, mimicking the resistances due to the solution bulk.
-{
-    \color{blue}
 The mesh depth and padding values of five columns and three rows, respectively, has been taken directly from \cite{ScottSingle2013}.
@@
 Hence, we define $R_{sri}$ to be 3/4 that of $R_{eri}$ making it a dependant parameter.}.
-}
 The resulting fit and parameter values are presented in figure~\ref{fig:transresistance} and table~\ref{tab:RESparams} respectively.
-{
-    \color{blue}
-    % Item 11
 Measurements of the inter-electrode impedance were made using a Tektronix TPS2014 DSO with four fully isolated and floating channels; an Agilent 33220A Function Generator; and a desktop PC controlling the instruments via Python 2.7.
 
-It should be noted that the resistive mesh created in this step models only the restitivity of the solution bulk.
+It should be noted that the resistive mesh created in this step models only the resistivity of the solution bulk.
 This means that no resistive contribution from the electrode/electrolyte interface is included in these measurements as voltage measurements are always across pairs of non-driven electrodes.
-We determine the fixed resistance of a single inteface, $R_{S}$, when fitting parameters to the displacement component.
-}
+We determine the fixed resistance of a single interface, $R_{S}$, when fitting parameters to the displacement component.
 
@@
 
-{\color{blue} Displacement currents are responsible for capacitive behaviour at interfacial boundaries.
+Displacement currents are responsible for capacitive behaviour at interfacial boundaries.
 They are brought about by the redistribution of charge in response to applied fields, i.e.
@@
 This displacement mechanism is capable of transferring charge between electrical and biological systems without damaging electrodes or tissue.\cite{Horch2004}
-This behaviour is modelled by way of a Constant Phase Element (CPE); also known as a fractional capacitor.}
-{\color{blue} For simulation purposes this element is realised as an array of R-C branches.~\cite{ScottSingle2013,Morrison59,Elwakil10} where the value of each R-C pair is chosen to set the slope of impedance relative to frequency.
-The placement of R-C pairs within the CPE is determined by Morrison's parameters $m$ and $k$, where $k$ determines the spacing, or density, of R-C branches and $m$ determines the resulting slope.}
+This behaviour is modelled by way of a Constant Phase Element (CPE); also known as a fractional capacitor.
+For simulation purposes this element is realised as an array of R-C branches.~\cite{ScottSingle2013,Morrison59,Elwakil10} where the value of each R-C pair is chosen to set the slope of impedance relative to frequency.
+The placement of R-C pairs within the CPE is determined by Morrison's parameters $m$ and $k$, where $k$ determines the spacing, or density, of R-C branches and $m$ determines the resulting slope.
 We measure displacement currents by sweeping the frequency of a sinusoidal stimulus across electrodes 2 and 7 of the Octrode while measuring the voltage between electrodes 2 and 3 (numbering shown in Fig.~\ref{fig:octrode}).
@@
     \end{center}
-    \caption{\color{blue} Charge injected per phase during CPE measurement for each of the six concentrations of PBS. Calculated using a geometric surface area of 10\thinspace mm$^{2}$}
+    \caption{Charge injected per phase during CPE measurement for each of the six concentrations of PBS. Calculated using a geometric surface area of 10\thinspace mm$^{2}$}
     \label{fig:chargeInjectionVsFrequency}
 \end{figure}
-{
-    \color{blue}
 The geometric current density during measurements peaked at 22.6\thinspace mA/cm$^{2}$ at 10000\thinspace kHz in 1.0X PBS and fell as low as 27.6\thinspace $\mu$A/cm$^{2}$ at 50\thinspace mHz in 0.025X PBS.
@@
 The stimulus waveform was set at 300\thinspace mV (peak) at each measurement point. The measurement instruments used are the same as those used to measure the inter-electrode resistance.
-}
-{
-    \color{blue}
+
 Figure~\ref{fig:CPE_Magnitude} shows the magnitude of the measured response of each of the six PBS concentrations accompanied by simulation results.
@@
 Those values were chosen as they give the closest match to the measured data.
-}
+
 As shown in the interface model schematic (figure~\ref{fig:schematic}), the interface contains its own internal series resistance ($R_{S}$).
@@
 Here we express the CPE offset parameter as $|Z|\thinspace @ \thinspace 1Hz$, but the fits used $|Z|\thinspace @ \thinspace 0.05Hz$, as data points at this frequency are outside the transitional zone where the impedance of the CPE and that of $R_{S+bulk}$ overlap.
-{
-    \color{blue} The data presented in Fig.~\ref{fig:CPE_Magnitude} show a large, linear, relative shift of $|Z|$ with salinity at higher frequencies, where the resistive component of the solution dominates.
+
+The data presented in Fig.~\ref{fig:CPE_Magnitude} show a large, linear, relative shift of $|Z|$ with salinity at higher frequencies, where the resistive component of the solution dominates.
 Conversely, at lower frequencies where the $|Z|$ changes with frequency, the relative change is closer to logarithmic. This region is modeled by the CPE.
 This suggests that the CPE does not chiefly rely on the added salt ions, but they do have some effect.
-Instead, the constant-phase charge effect must arise from phenonema not associated with the salt ions.
-}
+Instead, the constant-phase charge effect must arise from phenomena not associated with the salt ions.
 
@@
 With parameters fitted for the scaling of both the CPE and $R_{S}$ with PBS concentration, we turn to Faradaic conduction.
-{
-    \color{blue}
 Our model uses two reverse connected diodes to represent Faradaic current conduction between electrode and electrolyte.
@@
     \end{eqnarray}
-}
+
 The interface model uses the diodes to reproduce the exponential behaviour of Faradaic current conduction implied by the Butler-Volmer equation.
@@
 The CPE will draw negligible current once it has settled and in the case of our model we assume the remaining current conduction to be the result of Faradaic processes.
-{\color{blue} In \cite{Greatbatch1969} it is shown that the stirring of an air-saturated solution of physiological saline reduces the settling time of platinum electrodes to stimulus transients; with both situations eventually settling to the same impedance.}
+In \cite{Greatbatch1969} it is shown that the stirring of an air-saturated solution of physiological saline reduces the settling time of platinum electrodes to stimulus transients; with both situations eventually settling to the same impedance.
 The equation governing current conduction in a diode where the forward voltage across the diode, $V_{D}$, is small is
@@
 Faradaic measurements were made using an Agilent E5270B Precision Measurement Mainframe producing a stepped DC voltage stimulus whilst continuously measuring the output current.
-%{
-%    \color{blue}
-%    The use of electrodes 3 and 7 was made because the connection to electrode 2 in our Octrode had been damaged.
-This alteration has no impact on the validity of results as all other electrodes are left to float.
-%}
 
@@
 Those measurements show a trend of decreasing current stabilisation time as the overpotential steps increase.
-Sixty four seconds after stepping from 0.64\thinspace V to 0.72\thinspace V, the current has stabalised to $95\%$ of its value at 10\,000 seconds.
+Sixty four seconds after stepping from 0.64\thinspace V to 0.72\thinspace V, the current has stabilised to $95\%$ of its value at 10\,000 seconds.
 At overpotential steps for higher voltages, the settling time is further reduced.
@@
 This uses the same data as the previous figure but has been processed so that each point represents the average of the final 24 current measurements at each step.
-Below 0.9\thinspace V it appears that the concentration of the solution had no identifiable effect on Faradaic conduction {\color{blue}as there is overlap between each trace and the mean values are not monotonic with concentration in this region}.
+Below 0.9\thinspace V it appears that the concentration of the solution had no identifiable effect on Faradaic conduction as there is overlap between each trace and the mean values are not monotonic with concentration in this region.
 Between 0.9\thinspace V and 1.05\thinspace V a transition occurs which results in current conduction becoming dependent on solution concentration.
 Above 1.05\thinspace V the traces diverge showing clear dependence upon concentration.
-{\color{blue} The point at which this transition occurs is determined by the concentration of saline, with lower concentrations transitioning earlier.
+ The point at which this transition occurs is determined by the concentration of saline, with lower concentrations transitioning earlier.
 A concentration of 0.0625X PBS causes a transition at around 0.95\thinspace V whereas electrodes in the 1.0X PBS solution transition somewhere between 1.0\thinspace and 1.05\thinspace V.
 The effect of transition can be seen in the green trace at 1.0\thinspace V where the error bar is wide due to the current shift being captured in the measurement at that voltage.
-Part of a transition with respect to time is visible in figure~\ref{fig:StepResponse_Faradaic} where the red trace drops uncharacteristically after the increment at around 600 seconds.}
+Part of a transition with respect to time is visible in figure~\ref{fig:StepResponse_Faradaic} where the red trace drops uncharacteristically after the increment at around 600 seconds.
 
@@
 
-{
-    \color{blue}
 Figure~\ref{fig:faradaic_currentVsTime} shows a subset of the data used in Fig.~\ref{fig:StepResponse_Faradaic} (the 1.0X PBS trace) to show the fit between simulated and measured data in the time domain.
@@
 In future we hope to extend this model into a diffusion controlled conduction scenario and extend the CPE element to better reproduce the time domain response.
-}
+
 \section{In-vivo measurements of sheep}
@@
 \end{figure}
+Cogan states the main differences between in-vivo and in-vitro responses come down to temperature, the presence of organic species, tortuous diffusion path for charge carriers, physiological responses of the host to a foreign body, and uncertain concentrations of electrolytes and buffers near the electrode surface.\cite{Cogan2008}
+    Nevertheless, electrical engineers use baths of saline as a substitute for in-vivo testing (a ``phantom'') due to its convienience.
+We now test the claim that 0.1X PBS is a reasonable representation of the spine of a living sheep.
 
-We now test the claim that 0.1X PBS is a reasonable representation of the spine of a living sheep.
 The displacement measurements were repeated inside the spinal canal of a live sheep, just outside the dura as shown in figure~\ref{fig:sheepSpine}.
@@
 The study complied with the Australian Code of Practice for the Care and Use of Animals for Scientific Purposes.
-{\color{blue} Four measurements taken at regular invervals over a period of 30 minutes} are presented in figures~\ref{fig:displacement_sheepCPEMagnitude} and~\ref{fig:displacement_sheepCPEPhase} on top of the array of traces for saline taken from figures~\ref{fig:CPE_Magnitude} and~\ref{fig:CPE_Phase}.
+Four measurements taken at regular intervals over a period of 30 minutes are presented in figures~\ref{fig:displacement_sheepCPEMagnitude} and~\ref{fig:displacement_sheepCPEPhase} on top of the array of traces for saline taken from figures~\ref{fig:CPE_Magnitude} and~\ref{fig:CPE_Phase}.
 Although it is clear that there are complications in vivo, a 0.25X PBS saline offers a good approximation to the resistive part of the trace.
@@
     \end{center}
-    \caption{Comparison between the magnitude of CPE in live sheep {\color{blue}(blue error bars)} against each of the PBS traces from figure~\ref{fig:CPE_Magnitude} (grey lines) and a simulated fit to the sheep data (red trace).}
+    \caption{Comparison between the magnitude of CPE in live sheep (blue error bars) against each of the PBS traces from figure~\ref{fig:CPE_Magnitude} (grey lines) and a simulated fit to the sheep data (red trace).}
     \label{fig:displacement_sheepCPEMagnitude}
@@
     \end{center}
-    \caption{Comparison between the phase response of the CPE in live sheep {\color{blue}(blue error bars)} against each of the PBS traces taken from figure~\ref{fig:CPE_Phase} (grey lines) and a simulated fit to the sheep data (red trace).}
+    \caption{Comparison between the phase response of the CPE in live sheep (blue error bars) against each of the PBS traces taken from figure~\ref{fig:CPE_Phase} (grey lines) and a simulated fit to the sheep data (red trace).}
     \label{fig:displacement_sheepCPEPhase}
@@
 
-    \bibitem{Mohtashami2011}
-    Saba~Mohtashami,
-    ``Electrochemical Properties of Flexible Electrodes for Implanted Neuromuscular Excitation Applications'',
-    Open Acess Dissertations and Theses (2011), Paper 6152
-
-    \bibitem{Horch2004}
-    K.~W.~Horsch and G.~S.~Gurpreet,
-    ``Neuroprosthetics: theory and practice'',
-    World Scientific, 2004.
-
 \bibitem{Cogan2008}
@@
 vol.~52 no.~7, July 2005, pp1295--1302.
+
+\bibitem{Mohtashami2011}
+    Saba~Mohtashami,
+    ``Electrochemical Properties of Flexible Electrodes for Implanted Neuromuscular Excitation Applications'',
+    Open Acess Dissertations and Theses (2011), Paper 6152
+
+\bibitem{Horch2004}
+    K.~W.~Horsch and G.~S.~Gurpreet,
+    ``Neuroprosthetics: theory and practice'',
+    World Scientific, 2004.
 
@@
 
-\section*{Reviewer Comments}
-
-\subsection*{Reviewer 1}
-
-{\color{blue}
-I am not very enthusiastic about his paper as it does not contain many novel or original ideas and finding.
-On the electrochemistry side it is superficial and falls back behind published state of the art and textbook knowledge.\\
-{\color{OliveGreen}
-    This response has concerned us and we subsequently invested considerable effort in broadening our search of the literature.
-We have included some new references to the electrochemistry literature.
-This work is concerned primarily with the electrical side of an interface and more specifically with that of an implanted electrode.
-Our intention is to be able to encapsulate the electrical aspect of the interface and surrounding electrolyte in an equivalent electrical circuit, regardless of the chemistry at play.
-Nevertheless, we were unable to find anything that subtracts from the novelty of this work that lies in the relationship between impedance and electrolytes. 
-}\\
-
-1. The interface model as such is not new and has been published extensively.\\
-{\color{OliveGreen}
-    There are many published interfacial models.
-This model differentiates itself from all previous models by being compact, in the mathematical-modeling meaning of that word, implying that it can be entered into any common electronic circuit simulator and used to make predictions about impedance.
-This is especially important for elecronic engineers designing medical implant devices.
-}\\
-
-2.
-The authors do not at all comment on interface polarization, which is particularly important under DC conditions.
-As soon as an electrode carries current, such phenomena become important and relevant.\\
-{\color{OliveGreen}
-    We have lumped the effects of polarisation into the response of the displacement element in the model (CPE).
-The introduction to the Displacement Parameters section has been updated to include mention of polarisation.
-Our technique for measuring Faradaic reactions, namely to apply a DC voltage and wait until current transients settle before making a measurement, has been choosen to minimise any contribution from polarisation effects.
-}\\
-
-3.
-To assess the resistivity or impedance of a material between two electrodes, one normally uses a 4-electrode setup with injection of current through the two outer electrodes, while measuring a voltage between the inner ones.
-This is particularly relevant for the measurements in Fig.
-3 and the related and subsequent text.\\
-{\color{OliveGreen}
-    We are not so much interested in knowing the resistivity of the solution as we are in knowing the resistance between any pair of electrodes for the specific electrode array.
-The difference being that we expect the geometry of the electrode array, being comprised of 8 cylindrical coaxially placed electrodes as shown in Fig.~1, to determine the resistance in a non-trivial way.
-Using the transimedance measurements we can construct a mesh that represents the geometry of the electrodes and the resistivity of the solution.
-Another benefit in the method chosen is that it does not rely on knowing the electrode geometry and is therefore more versatile.
-}\\
-
-4.
-The authors never mention the origin of any Faradaic contribution at the electrodes.
-What is the electro- or redox-chemistry that the authors assume to happen??
-Gas formation at the electrodes, electrolysis of the saline, i.e., hydrogen and oxygen formation??\\
-{\color{OliveGreen}
-    As a matter of interest, relevant Faradaic reactions, both reversible and irreversible, have been added both to the displacement/polarisation and Faradaic sections.
-Nevertheless, we do not need to understand any specific reactions that occur, as we confine our attention to the electrical impedance properties.
-We have added, as the second paragraph of the introduction, a clarification of the goals of the work.
-}\\
-
-5. Figure 5 is not referenced anywhere in the text. Also the blue variations in the curves are hardly visible.\\
-{\color{OliveGreen}
-    Graphs redrawn with a wider range of shading to help identify traces and referenced on page 3 (now figure \ref{fig:CPE_Phase}).
-}\\
-
-6. Since the electrode model includes two back-to-back diodes, I think it would be valuable to sweep the voltage from -1.2V to +1.2V.\\
-{\color{OliveGreen}
-Measurements were made up to 1.2V, refer to figure 10 for example. The results are naturally symmetrical.
-%The measurements involving the back-to-back diodes are those measuring the contribution from irreversible Faradaic reactions.
-These measurements involve two active electrodes while the remaining electrodes and the electrolyte have a floating potential.
-Sweeping the voltage from -1.2V to +1.2V in this case would be the equivalent of swapping the terminals halfway through the sweep.
-Physically this would not be the same as polarisation effects would linger, however we are only interested in the steady state Faradaic conduction where we assume polarisation and displacement effects are negligible.
-}\\
-
-7.
-There is a big difference between blue dots and red curve in Fig.
-10, except for the "voltage increment time" and "64 seconds after increment".
-This indicates to me that the CPE model is NOT that accurate, as the settling curve is highly correlated to the CPE parameters.\\
-{\color{OliveGreen}
-    We have addressed this discrepancy on page 5.
-The frequency response of the CPE is still valid, which is what we had fitted the parameters.
-We agree that the time-domain response of the CPE may need further work.
-Thank you for your time and critique.
-}\\
-}
-
-\subsection*{Reviewer 2}
-
-{\color{blue}
-In this manuscript, the authors report how the non-linear electrode-electrolyte interface model parameters change as a function of saline solution concentration.
-This is a very interesting and important subject that could be potentially of great importance for readers of IEEE Transactions on Biomedical Circuits ans Systems.
-The manuscript is well written and adequately referenced.
-However, the reviewer would like to pose a few questions to the authors to clarify some  issues in the manuscript, which should be addressed.\\
-
-page 2, in text/ table II. The scaling parameters and their meanings should be described more comprehensively. They remain somewhat unclear and meaningless to reader.\\
-{\color{OliveGreen}
-    We have encouraged the reader to review ScottSingle2013 in order to understand the interpretation of the given parameters.
-}\\
-
-page 2 Measurement of the CPE. What was the current density used in EIS measurements?
-What is the effect of chosen current density on CPE impedance (Fig. 5)?
-{\color{OliveGreen}
-    Added a new figure to show the current density during CPE measurement.
-}
-
-In addition,  measurement apparatus information is fully lacking.\\
-{\color{OliveGreen}
-    Added missing details of instrumentation used to conduct inter-electrode resistance measurements and clarified their reuse for displacement measurements.
-}\\
-
-page 2, line 52. "the magnitude shifts relatively little". However, In Fig. 4, logaritmic scale is used, and the change from 1.0X to 0.025X is almost 50k at the lowest frequencies.
-please clarify this point.\\
-{\color{OliveGreen}
-    This has been reworded to improve clarity, see end of section III. We are referring to relative shifts as opposed to absolute impedances.
-}\\
-
-page 3, in text/ table III. The parameters (m, k..) and their meanings should be described more comprehensively, as well.\\
-{\color{OliveGreen}
-    Sure, we have added a quick interpretation for the parameters $m$ and $k$ in the text.
-}\\
-
-Figure 9 (page 4).
-There is a clear difference in behavior of faradic conduction between 0.25X (red curve) and 0.5X (green curve).
-Transient current occur at 0.95V (<0.25X PBS) changing to occur at 1.0 V (>0.5X PBS).
-This behavior has not discussed in manuscript at all.
-Please revise it.\\
-{\color{OliveGreen}
-    See revised discussion on page 5.
-}\\
-
-page 4. Referencing (in the text) to the Fig. 10 is lacking (?).\\
-{\color{OliveGreen}
-    Thank you, we have updated discussion of Faradaic Parameters to include the results from what is now figure~\ref{fig:faradaic_currentVsTime}.
-}\\
-
-Finally, and most importantly, the part of in vivo measurements are very limited since only one spinal channel measurement has been performed.
-My opinion is that this manuscript could be even better without this uncertain (n=1) result and thus I recommend to leave this part out.\\
-{\color{OliveGreen}
-    Graph of sheep response to displacement stimulus has been updated to include four separate measurements taken on the second day of sheep measurement. 
-}\\
-}
-
-\subsection*{Reviewer 3}
-
-{\color{blue} The aim of this paper, to find a SPICE model of implanted electrodes, is important and the results presented in the paper are interesting.
-However, as it stands the paper is not well written and must be revised.
-The weaknesses of the paper are an unclear structure, with results and discussion mixed, poor attention to detail and inaccurate use of words.\\
-{\color{OliveGreen}With respect to the comment on poor attention to detail and innaccurate use of words, we have revised the manuscript to include more detail both in regards to experimental setup, the electrochemistry and model elements.
-We have chosen to mix the discussion with results as the model parameters are derived along with the measurments, which are required before moving to each subsequent step.
-This arrangement is common in modeling papers in EE.}\\
-
-Concerning the experiments, I have two points to make.
-
-1.
-You do not explain how the impedance measurements have been made (Figs 4, 5 13 \& 14).
-I want to know how much charge was being applied to these electrodes at low frequencies (e.g.
-0.05 Hz): what potential excursion occurred was it really a ``small signal''?\\
-{\color{OliveGreen}We have fully addressed this issue.
-We have added maximum and minimum current density calculations, peak stimulus voltage information and added a plot showing the amount of charge injected during measurment of displacement currents.}\\
-
-2.
-I think that the classical view of the electrochemistry of Pt in saline (as, for example, expressed in your ref 1), is that the electrolysis reactions (oxygen and hydrogen evolution) start with a potential difference of about 1.4V.
-Below this p.d., the likeliest reaction is reduction of oxygen at the cathode which could accompany oxygen evolution from water at the anode.
-Your paper lacks any consideration of the chemistry but this is a important fault in the stepped-current experiment.
-Was the solution in equilibrium with air before the experiment?
-If this is a model for electrodes in vivo, should not the PBS have been in equilibrium with gas with the in vivo partial pressure of oxygen?
-I suggest that you repeat this experiment, at least (i) under air, (ii) under nitrogen, \& perhaps (iii) under in vivo partial pressure of oxygen.
-The stirring arrangements ought to be exactly described too because liquid flow may be critical.\\
-{\color{OliveGreen}This manuscript is primarily concerned with modelling the behaviour of electrodes in a bath of saline.
-Phisiological solutions of saline are routinely used to mimic the impedances seen by an implant by designers in order to verify their designs and test any control logic.
-In spinal cord stimulation 0.1X PBS is used but there is no way to tell how accurate a phantom such a solution is for the a real spinal column.
-This paper seeks to answer that question in a way that allows implant designers to broadly compare the behavior of their in-vitro experiments with in-vivo behavior.
-While controlling the partial pressure of oxygen in the PBS bath definitely appears to be of importance to the general field of in-vivo electrode modelling, we feel the results within this manuscript are of importance to those using solutions of PBS to verify electrical designs and models.}
-
-Other points
-
-1. P1, top RH col. ``0.1X'' ought to be explained when you first use this form.\\
-{\color{OliveGreen}Fixed.}\\
-
-2.
-Should the resistor model of the volume conductor from [4] be shown in this paper?
-It would make the paper easier to understand for your reader if you showed the model.
-If you are not going to do so, you might help them by saying something like ``Readers are advised to see [4] to understand the meaning of the parameters in Table II''.\\
-{\color{OliveGreen}We agree absolutely.
-Unfortunately there is little room in the manuscript as it stands for extra figures.
-We have advised the reader to read ScottSingle2013 to understand the interpretation of the mesh generation parameters, where they would find the radial volume model.}\\
-
-3. You say (p2 line 43) that there are 2 independent scaling factors. Is Rli independent or not? If not, why input it in Table II?\\
-{\color{OliveGreen}Footnote added to sentence in question that describes our defining of $R_{sri}$ in terms of $R_{eri}$.}\\
-
-4.
-In the legend of Fig 4 and in paragraph below, you say this is magnitude of the CPE.
-But surely it is not since the sloping lines become horizontal.
-It is the CPE in series with something.
-But what is this something?
-Is it the total series resistance or have you already subtracted the volume resistance (found in section II)?\\
-{\color{OliveGreen}The caption in Figure 4 has been reworded to more accurately describe the situation.
-Yes this graph is showing the CPE in series with both the inter-electrode resistance and $R_{S}$.}\\
-
-5.
-The previous point is complicated by your statement that Rs (Fig 2) is an addition to the volume resistance (p2 RH col).
-Why is Rs necessary?
-Is it because the resistance values at high frequencies in Fig 4 are not consistent with the values from the resistor network found in section II?
-If so, this would be very interesting and I would like you to bring this out.\\
-{\color{OliveGreen}The requirement of $R_{S}$ has been clarified at the end of Section II. This was not made very clear in our original submission, thank you for pointing this out.}\\
-
-6. P2, col 2, line 24: why 2 \& 7?\\
-{\color{OliveGreen}The choice of electrodes was arbitrary.
-We felt that electrodes 2 and 7 were a good compromise between good separation and avoiding any end effects.
-This was the same pair as used by Scott \& Single 2013 from which we have based our measurements.}\\
-
-7.
-P2, col 2, line 53: ``implying that its behaviour is a property of Pt and water''.
-Previous authors have thought this showed that the CPE depended on the geometry (surface roughness) of the electrode.
-Did you mean that, or were you thinking of the electrochemical properties of Pt.
-Please make clearer.\\
-{\color{OliveGreen} We have cleaned this statement up. See end of section III.}\\
-
-8. You do not explain why, in eq 1, you want to use this form. Why nVt? I suppose it isso you can use a standard SPICE form rather than this suits the data. Is that right?\\
-{\color{OliveGreen} That is correct. This equation is the standard diode equation found in any electronic engineering textbook.}\\
-
-9. P3, col 2, line 31: why 2 and 6?\\
-{\color{OliveGreen} Again a totally arbitrary choice, we fit the model to whichever pair we use.
-We actually used electrodes 7 and 3, the mention of electrodes 2 and 6 was a mistake.
-Thank you for bringing that to our attention.}\\
-
-10. P3, col 2, line 36. I guess you mean what is usually called a Magnetic Stirrer. Not ``inductive'' surely?\\
-{\color{OliveGreen} Changed mention of inductive stirrer to magnetic stirrer.}\\
-
-11. P3 footnote. ``The response of the CPE'': this is confusing! Surely this is the response of a pair of electrodes? The CPE is an element of your model.\\
-{\color{OliveGreen}Removed reference to the CPE element and have better quantified the settling period in that footnote.}\\
-
-12. Fig 11 legend ``Simulated and measured response of the interface model''. Surely you mean ``Simulated response of the interface model compared to measurement from the electrodes''?\\
-{\color{OliveGreen} Yes, that is better - thank you.}\\
-
-13. P5, col 2, line 46 ``the CPE is setting''. Again, you are confusing an element of your model with reality.\\
-{\color{OliveGreen}Changed references to the CPE model element in the conclusion to the electrical double layer.}\\
-
-14.
-P5, col 1, line 49 ``a 0.25X PBS is a good model''.
-This seems a very feeble comment on an interesting result.
-The series resistance part of the in vivo magnitude is a good fit to the 0.25X curve and the slope of the CPS is very similar (though you have exaggerated this by extrapolating nearly 2 decades in frequency below the lowest-frequency measurement).
-But the impedance at low frequencies is about three times too high.
-How do you explain that?
-It cannot be because of the bone and other high-resistivity structures around the electrodes (which would have an effect on the high frequency asymptote).
-So what is it?
-Did you measure the electrodes again in PBS after removing from the sheep?
-Troyk published an interesting paper with measurement from electrodes in brain of zebra finches which showed that anomalous characteristics in vivo vanished as soon as the electrodes were returned to PBS, implying that the phenomenon was not due to some biofilm deposited on the electrodes.\\
-{\color{OliveGreen} The extrapolation of CPE data from the in-vivo measurements has been removed.
-We have a couple of ideas as to why the resistive and displacement components of the in-vivo measurements do not match the saline solution, however we aren't willing to add those here until we have investigated the behaviour further.
-We hope to answer this questoin in part by mixing saline solutions with varous solvents and hydrolised cellulose in an attempt to create a closer and more broadband match to the in-vivo measurements.
-In effect we are hoping to create a recipe that allows our industrial partners to dial-up a given impedance response for implant testing purposes.
-We had not thought to measure the electrodes again in PBS after the in-vivo measurements but this is certainly something we will aim for if we have the chance in future, thank you.
-The electrodes we used were steralised immediately after the measurements made here.}\\
-}
-
-\subsection*{Reviewer 4}
-
-{\color{blue} In this manuscript, the authors studied the impedance of a commercial electrode array as a function of concentration of phosphate buffered saline (PBS), both through simulation and empirical measurements, and compared those results to the impedance measured when the electrode array was implanted into a sheep's spinal cavity.
-From this comparison, they concluded that the current practice of testing spinal cord stimulator in 0.1x of physiologically normal saline is adequate but suggest that no single concentration of PBS captures the frequency dependence of the in vivo measured impedance.\\
-
-Overall, the paper was brief and to the point, which in this case is actually a determent instead of a benefit.
-Much of the underlying theory and development of parameters appear without informing the reader of their purpose or how they were calculated and/or measured.
-For example, the parameters in Table 2 (and reported to be in Figure 3) are not explained and what their relationship to the remainder of the manuscript is not provided.\\
-{\color{OliveGreen} We have greatly expanded the explanation in the manuscript, and referred interested readers to the source.}\\
-
-To make this manuscript more approachable to a wider audience, I recommend the authors more fully develop Sections II, III, and IV.
-Further, they should explain their testing in terms of standard electrochemical characterization, detailing their counter, working, and reference electrodes used in measuring impedance.\\
-{\color{OliveGreen} Our approach arises from the fact that reference electrodes are not possible in an implanted scenario and that implant electrode arrays such as is used in this work do not have specifically designed counter and working electrodes.
-We have added a statement to this effect in the introduction.
-We feel that many of the questions or concerns arrising from the reviewers stems from the fact that we are operating in a scenario far from traditional electrochemistry labs.}\\
-
-As part of this expansion, the references should be increased beyond the present ten references.
-Although their current references include clearly important electrode characterization references (Cogan, Merrill et.
-al, \& Kane et.
-al), the information contained in these references are not effectively used to support the authors’ work.\\
-%{\color{red} Find places for Merrill and Kane. Jonathan: Cogan, where can we use it? I don't have access  to this paper.}
-{\color{OliveGreen} In response the numerous reviewee comments we have added more citations. We hope we have more thorough pointers to the literature where appropriate in our literature.}\\
-
-Technically, I found one issue with this paper.
-In Figure 11, the x-axis labels should have 2 digits after the decimal.
-As presently shown, each of the labels 0.6, 0.7, ..., 1.0 are repeated twice on the axis.
-Presumably, the second version of the labels should be 0.65, 0.75, ..., 1.05.\\
-{\color{OliveGreen}Thank you very much. See updated figure (now figure~\ref{fig:faradaic_currentVsVoltage}).}\\
-
-}
-
 \end{document}

### 2014-04-03 paper.tex
Removed reviewer comments and feedback (along with edit highlighting) from paper.

@@
 Repeating that work, a resistor network that connects each of the eight electrodes is constructed, mimicking the resistances due to the solution bulk.
-{
-    \color{blue}
+
 The mesh depth and padding values of five columns and three rows, respectively, has been taken directly from \cite{ScottSingle2013}.
@@
 Hence, we define $R_{sri}$ to be 3/4 that of $R_{eri}$ making it a dependant parameter.}.
-}
+
 The resulting fit and parameter values are presented in figure~\ref{fig:transresistance} and table~\ref{tab:RESparams} respectively.
-{
-    \color{blue}
-    % Item 11
+
 Measurements of the inter-electrode impedance were made using a Tektronix TPS2014 DSO with four fully isolated and floating channels; an Agilent 33220A Function Generator; and a desktop PC controlling the instruments via Python 2.7.
 
-It should be noted that the resistive mesh created in this step models only the restitivity of the solution bulk.
+It should be noted that the resistive mesh created in this step models only the resistivity of the solution bulk.
 This means that no resistive contribution from the electrode/electrolyte interface is included in these measurements as voltage measurements are always across pairs of non-driven electrodes.
-We determine the fixed resistance of a single inteface, $R_{S}$, when fitting parameters to the displacement component.
-}
+We determine the fixed resistance of a single interface, $R_{S}$, when fitting parameters to the displacement component.
 
@@
     \end{center}
-    \caption{\color{blue} Charge injected per phase during CPE measurement for each of the six concentrations of PBS. Calculated using a geometric surface area of 10\thinspace mm$^{2}$}
+    \caption{Charge injected per phase during CPE measurement for each of the six concentrations of PBS. Calculated using a geometric surface area of 10\thinspace mm$^{2}$}
     \label{fig:chargeInjectionVsFrequency}
 \end{figure}
-{
-    \color{blue}
+
 The geometric current density during measurements peaked at 22.6\thinspace mA/cm$^{2}$ at 10000\thinspace kHz in 1.0X PBS and fell as low as 27.6\thinspace $\mu$A/cm$^{2}$ at 50\thinspace mHz in 0.025X PBS.
@@
 The stimulus waveform was set at 300\thinspace mV (peak) at each measurement point. The measurement instruments used are the same as those used to measure the inter-electrode resistance.
-}
-{
-    \color{blue}
 Figure~\ref{fig:CPE_Magnitude} shows the magnitude of the measured response of each of the six PBS concentrations accompanied by simulation results.
@@
 With parameters fitted for the scaling of both the CPE and $R_{S}$ with PBS concentration, we turn to Faradaic conduction.
-{
-    \color{blue}
+
 Our model uses two reverse connected diodes to represent Faradaic current conduction between electrode and electrolyte.
@@
 \end{eqnarray}
-}
+
 The interface model uses the diodes to reproduce the exponential behaviour of Faradaic current conduction implied by the Butler-Volmer equation.
@@
 This uses the same data as the previous figure but has been processed so that each point represents the average of the final 24 current measurements at each step.
-Below 0.9\thinspace V it appears that the concentration of the solution had no identifiable effect on Faradaic conduction {\color{blue}as there is overlap between each trace and the mean values are not monotonic with concentration in this region}.
+Below 0.9\thinspace V it appears that the concentration of the solution had no identifiable effect on Faradaic conduction as there is overlap between each trace and the mean values are not monotonic with concentration in this region.
 Between 0.9\thinspace V and 1.05\thinspace V a transition occurs which results in current conduction becoming dependent on solution concentration.
 Above 1.05\thinspace V the traces diverge showing clear dependence upon concentration.
-{\color{blue} The point at which this transition occurs is determined by the concentration of saline, with lower concentrations transitioning earlier.
+The point at which this transition occurs is determined by the concentration of saline, with lower concentrations transitioning earlier.
 A concentration of 0.0625X PBS causes a transition at around 0.95\thinspace V whereas electrodes in the 1.0X PBS solution transition somewhere between 1.0\thinspace and 1.05\thinspace V.
 The effect of transition can be seen in the green trace at 1.0\thinspace V where the error bar is wide due to the current shift being captured in the measurement at that voltage.
-Part of a transition with respect to time is visible in figure~\ref{fig:StepResponse_Faradaic} where the red trace drops uncharacteristically after the increment at around 600 seconds.}
+Part of a transition with respect to time is visible in figure~\ref{fig:StepResponse_Faradaic} where the red trace drops uncharacteristically after the increment at around 600 seconds.
 
@@
 
-{
-    \color{blue}
     Figure~\ref{fig:faradaic_currentVsTime} shows a subset of the data used in Fig.~\ref{fig:StepResponse_Faradaic} (the 1.0X PBS trace) to show the fit between simulated and measured data in the time domain.
@@
 \end{figure}
+Cogan states the main differences between in-vivo and in-vitro responses come down to temperature, the presence of organic species, tortuous diffusion path for charge carriers, physiological responses of the host to a foreign body, and uncertain concentrations of electrolytes and buffers near the electrode surface.\cite{Cogan2008}
+Nevertheless, electrical engineers use baths of saline as a substitute for in-vivo testing (a ``phantom'') due to its convienience.
+We now test the claim that 0.1X PBS is a reasonable representation of the spine of a living sheep.
 
-We now test the claim that 0.1X PBS is a reasonable representation of the spine of a living sheep.
 The displacement measurements were repeated inside the spinal canal of a live sheep, just outside the dura as shown in figure~\ref{fig:sheepSpine}.

### 2014-04-03 paper.tex
Added reviewer comments from second round

@@
 
+\section*{Reviewers' Comments to the Authors:}
+
+\subsection*{Reviewer: 1}
+
+Comments to the Author
+
+{
+    \color{OliveGreen}
+    My comments have been sufficiently addressed.
+}
+
+{
+    \color{blue}
+    Thank you.
+}
+
+\subsection*{Reviewer: 2}
+
+Comments to the Author
+
+{
+    \color{OliveGreen}
+    Required modification done and manuscript now significantly improved.
+}
+
+{
+    \color{blue}
+    Thank you.
+}
+
+\subsection*{Reviewer: 3}
+
+Comments to the Author
+
+{
+    \color{OliveGreen}
+
+    I am sorry to say that the revised version of the paper is still quite unsatisfactory.
+You have added electrochemical reactions (5)-(9) but do not acknowledge that these all have different reaction potentials, will have different charge transfer coefficients ( alpha in the Butler Volmer equation http://en.wikipedia.org/wiki/Butler\%E2\%80\%93Volmer\_equation), and will by limited by mass transfer to different extents.
+Therefore the use of diodes in the model is not obviously appropriate.
+
+    My interpretation of your data in Fig 10 is this.
+Above 1.05V, the electrolysis reactions (6) and (7) are occurring and the current will partly depend on the conductivity (therefore concentration) of the electrolyte.
+Below about 1.05V, the direct current may indeed be due to oxygen reduction at the cathode and oxygen evolution at the anode, which you cite (page 1, col 2, line 53) from ref 10 (c.f.
+Clark Oxygen Electrode).
+In that case, dissolved oxygen will have to diffuse to the cathode because it is not charged, so this will be diffusion-limited, which explains why the current is independent of concentration.
+Maybe you disagree with me but it is unsatisfactory that this is speculative and no doubt you will say that you did not want to get involved in electrochemistry, you just wanted to construct a model.
+
+    Even as a model, however, your case is not very convincing.
+
+    1.
+You state in the Introduction that you aim for a model suitable for stimulation yet there are no results comparing the model with experiment when the electrodes are used in this way.
+All the results are with sinusoidal excitation (which are of low amplitude at high frequencies), or DC with steps.
+
+    2.
+Your model of the interface (Fig 2) has a series resistor Rs.
+I do not see why you need this and how you can measure it: how do you separate it from the volume resistance (``Resistive Network'')?
+(You mention this on p3 col 1, line 55 without casting any light.)
+
+    3.
+The maximum charge limit for Pt was given by Brummer \& Turner (IEEE Trans BME, 24, 436-9, 1977) as 320 microcoulombs per cm\^2, and later authors revised this downward.
+If you really applied the charge density that you show in Fig 4, you exceeded this limit at frequencies below ~50Hz and I would expect that your electrodes would have been gassing.
+In that case it is surprising that the impedance curves in Figs 5 \& 6 do not show a deviation from pure CPE behaviour.
+This is an important anomaly.
+
+    4.
+The time constants seen in Figs 8, 9 \& 11 are interesting.
+Fig 11 shows that the model does not fit well because its time constant is too short.
+But is this surprising?
+Your impedance spectra go down to 0.05Hz (Figs 4-6) and I suppose that you chose RC pairs for your CPE model that go down to that frequency.
+But that is only to a time constant of ~3s (1/2*pi*f) which is much less that the 250s in Fig 8.
+It would be interesting to know whether, if you extended the spectrum far enough down, the time constants from step changes to the RC network that approximates the CPE would be similar to those seen in Fig 8.
+
+    5. p 6, col 1, line 11. ``rate dependent on the log'' should be ``rate varies exponentially''. i.e. Tafel equation.
+
+    6.
+Figs 14 \& 15 are intriguing.
+For reason given in 3 above, I discount the results below 50Hz, yet it does look as if the slope of the CPE is the same in vivo but with an offset that would correspond to a very weak solution of PBS.
+As far as I know, there is no satisfactory explanation yet for the CPE so perhaps this is a significant clue.
+}
+
+\subsection*{Reviewer: 4}
+
+Comments to the Author
+
+{
+    \color{OliveGreen}
+    In this manuscript, the authors studied the impedance of a commercial electrode array as a function of concentration of phosphate buffered saline (PBS), both through simulation and empirical measurements, and compared those results to the impedance measured when the electrode array was implanted into a sheep's spinal cavity.
+From this comparison, they concluded that the current practice of testing spinal cord stimulator in 0.1x of physiologically normal saline is adequate but suggest that no single concentration of PBS captures the frequency dependence of the in vivo measured impedance.
+Although not a very compelling conclusion, this manuscript does provide value to the field as a single source for creation of a compact, SPICE model of an electrode.
+Hence, my review is cast in the light of using this paper as a guide in developing a model of a different electrode.
+
+    1. As much of the paper involves development of the model, I recommend that the authors add some reference to modeling in the abstract.
+
+    2.
+Sections 2, 3, and 4 detail the measurement and simulation of measurements of parameters associated with the bulk solution, CPE and Rs, and the diodes of the model in Figure 2.
+I recommend that the authors expand the introduction to explain this organization to help the reader's understanding.
+Additionally, I propose that the authors expand the section headings to include this information.
+
+    3.
+The parameters provided in Table II include reference to an unexplained term sigma (σ).
+I presume this is the conductivity of saline (correct symbol and units for conductivity).
+For completeness, I recommend the authors explain this term, provide the numeric value (or values) that they used, provide how they adjusted this with concentration, and reference the source of their numeric data.
+
+    4.
+From the parameters provided in Table II, I can guess how many elements are in the SPICE model arising from these parameters but it would be much more valuable to the reader to have a clear statement of the true size of the associated SPICE model.
+I recommend the authors provide a clear statement at the end of this section of how many resistors are in their SPICE model as a result of this parameterization.
+
+    5.
+In Section 3, the authors state that the CPE is modeled as an array of R-C branches but at no time do they state the actual number of branches used in their model.
+I recommend the authors provide a clear statement at the end of this section of how many capacitors and resistors are in their SPICE model because of this parameterization.
+
+    6.
+The parameters provided in Table II include reference to `concentration'.
+As different readers will have different interpretations (mass concentration=0.9\%, molar concentration = 0.154M), I recommend the authors clearly explain the meaning of this term.
+
+    7.
+Given the authors details 3 different parts of their model in Sections 2, 3, and 4, I found it surprising that they only chose to characterize CPE in their in vivo experiment.
+In other words, if the complete model is important to performing simulation studies of a stimulation system, why did they not do such in their in vivo model and how valuable is their conclusion regarding the applicability of using 0.1xPBS as an in vitro of an animal.
+At minimum, I recommend the authors explain why they only characterized CPE in vivo.
+
+    8.
+In the conclusions, I recommend the authors provide details on the overall size of their SPICE model.
+Knowing this information, a reader can compare the compactness of the complete model to that of using a finite element model.
+
+    9.
+In their conclusions, I recommend the authors restate any limitations in their model that they mentioned earlier in the text (e.g., 0.9v limitation) and provide an honest discussion regarding the limits of their model.
+}
+
 \end{document}

### 2014-04-03 paper.tex
Added preliminary responses to reviewer comments

@@
 \end{eqnarray}
+
 This displacement mechanism is capable of transferring charge between electrical and biological systems without damaging electrodes or tissue.\cite{Horch2004}
@@
 Possible irreversible Faradaic reactions for platinum electrodes in saline are:
-\begin{eqnarray}
-    Pt + 4Cl^{-} &\Rightarrow& [PtCl_{4}]^{2-} + 2 e^{-}\\
-    2H_{2}O + 2 e^{-} &\Rightarrow& H_{2}\uparrow + 2OH^{-}\\
-    2H_{2}O &\Rightarrow& O_{2}\uparrow + 4H^{+} + 4e^{-}\\
-    2Cl^{-} &\Rightarrow& Cl_{2}\uparrow + 2e^{-}\\
-    Cl^{-} + H_{2}O &\Rightarrow& ClO^{-} + 2H^{+} + 2e^{-}
-\end{eqnarray}
+
+\begin{align}
+    Pt + 4Cl^{-} &\Rightarrow& [PtCl_{4}]^{2-} + 2 e^{-} \label{eqn:ptCl}\\
+    2H_{2}O + 2 e^{-} &\Rightarrow& H_{2}\uparrow + 2OH^{-} \label{eqn:H20}\\
+    2H_{2}O &\Rightarrow& O_{2}\uparrow + 4H^{+} + 4e^{-} \label{eqn:2H20}\\
+    2Cl^{-} &\Rightarrow& Cl_{2}\uparrow + 2e^{-} \label{eqn:Cl} \\
+    Cl^{-} + H_{2}O &\Rightarrow& ClO^{-} + 2H^{+} + 2e^{-} \label{eqn:ClH20}
+\end{align}
+
+{
+    \color{blue}
+    It should be noted that each of these reactions (\ref{eqn:ptCl}, \ref{eqn:H20}, \ref{eqn:2H20}, \ref{eqn:Cl} and \ref{eqn:ClH20}) have different reaction potentials.
+It is expected that the situation in-vivo will be much more complex.
+}
 
@@
 
+    {
+        \color{Blue}
+        The diodes are there to model the change in current attributed to the first biologically damaging reaction that occurs at the electrode/electrolyte interface.
+Whatever reaction occurs first in the relevant electrolyte is the reaction that diode aims to mimic.
+We observe that the current increases near exponentially around this point so we use a diode to mimic that.
+We expect this reaction may not be the same in-vivo as it is in-vivo but the properties of a diode can be altered to match where this occurs.
+
+        If there are secondary reactions occurring at higher potentials then we could add a second pair of diodes with the properties of that specific reaction.
+The problem here is that we would then need to include memristors (as used in ScottSingle2013) to account for reactant depletion.
+We don't account for reactant depletion for the same reason we don't account for reactions other than the very first Faradaic reaction to occur.
+The reason is that we never want biologically damaging reactions to occur due to an implant, so if they happen then something has gone wrong.
+
+        Think of our attempt to model Faradaic reactions as a ``you've pushed this too far'' indicator for an electrical engineer.
+
+        I think you're essentially right with you're argument, we're not up-front about this and we probably portray more capability in the Faradaic modelling aspect than we are able or aim to achieve.
+    }
+
     My interpretation of your data in Fig 10 is this.
@@
 
+    {
+        \color{Blue}
+        Correct, we do not wish to determine exactly what is happening at the electrode surface - we want to create a flexible model that can be used to simulate impedance.
+
+    }
+
     Even as a model, however, your case is not very convincing.
@@
 
+    {
+        \color{Blue}
+        This is a good point.
+ScottSingle2013 compare the model prediction to stimulus waveforms.
+Our aim is to see what changes in that model as the concentration of PBS is varied and to compare those measurements to in-vivo measurements using a live sheep.
+Were doing this because 0.1X PBS is commonly used as a phantom for real spine.
+There hasn't been an objective way of determining how accurate that assumption was until we used this model to make that comparison.
+    }
+
     2.
@@
 (You mention this on p3 col 1, line 55 without casting any light.)
+
+    {
+        \color{Blue}
+        We need this because it represents the resistance of the interface itself, separate from that of the fluid.
+        We measure the impedance magnitude of the displacement currents at high frequency (flattened part of Fig.
+5).
+For each concentration the impedance magnitude at 10kHz is higher than is predicted by the transimpedance measurements made in Fig.
+3.
+The transimpedance measurments do not measure impedance across an interface that is passing current and therefore any voltage drop across an interface due to $R_{S}$ would vanish.
+The displacement measurements take the voltage across interfaces that are passing stimulus currents.
+These measurements see the potential drop across the interface due to the current flow via Ohms law.
+
+        The transimpedance measurements give us an interelectrode resistance.
+The displacement measurements at high frequency give us an interelectrode impedance plus an interface impedance.
+Subtracting one from the other gives us a value of resistance that only appears as we pass current through an interface, which we include as $R_{S}$.
+    }
 

### 2014-04-03 paper.tex
Address reviewer comment

@@
 We hypothesise that the charging of the CPE draws available ions to the electrode, creating a layer of high ionic concentration at the surface irrespective of that of the solution bulk.
-It is this layer that is subsequently consumed by the Faradaic reactions at a rate dependent on the log of the electrode overpotential.
+It is this layer that is subsequently consumed by the Faradaic reactions at a {\color{blue} rate that increases exponentially with} electrode overpotential.
 The effect of bulk solution concentration while this layer has formed is negligible until the point at which the layer is consumed faster than it can be replenished.
@@
 
-{
-    \color{OliveGreen}
-
+{\color{OliveGreen}
     I am sorry to say that the revised version of the paper is still quite unsatisfactory.
@@
 
-    {
-        \color{Blue}
+    {\color{blue}
         The diodes are there to model the change in current attributed to the first biologically damaging reaction that occurs at the electrode/electrolyte interface.
@@
     {
-        \color{Blue}
+        \color{blue}
         Correct, we do not wish to determine exactly what is happening at the electrode surface - we want to create a flexible model that can be used to simulate impedance.
@@
     {
-        \color{Blue}
+        \color{blue}
         This is a good point.
@@
     5. p 6, col 1, line 11. ``rate dependent on the log'' should be ``rate varies exponentially''. i.e. Tafel equation.
+    {
+        \color{blue}
+        Correct, change made.
+    }
 

### 2014-04-07 paper.tex
Minor edit
Began adding responses to Reviewer 3's comments.

@@
 \begin{abstract}
-
 We report how the impedance presented by a platinum electrode scales with the concentration of phosphate buffered saline (PBS).
+{
+    \color{blue}
+    We measure this response in various solutions with an electrode array as is commonly used with spinal cord stimulation (SCS) implants.
+We match the parameters of a compact non-linear interface model to the measured response at each concentration.
+}
 We find that the constant phase element of the model scales with approximately the log of concentration, whereas the resistivity is inversely proportional.
@@
 The design of successful circuits depends upon a good understanding of external load impedance, while maximisation of battery life is linked to the use of electrodes whose impedance is well understood.
+
 Having a compact model of an electrode in the appropriate electrolyte allows circuit designers to simulate their designs with valid loads.
@@
 Electrodes in the laboratory are typically tested in a saline solution selected to mimic the circumstances in which they will operate when implanted.
+
 In an implanted setting there is no reference electrode and many of the well established electrochemical measurement regimes do not apply.
@@
 The electrode used in this work is a commercial linear array of eight platinum electrodes intended for SCS implantation called an ``Octrode''.~\cite{StJudeOctrode} A picture of an Octrode is presented in figure~\ref{fig:octrode}.
+
 The electrical interface model of \cite{Franks2005} and \cite{ScottSingle2013} has two parts, a displacement branch and a Faradaic branch.
@@
 Its contribution is limited to situations where diffusion limited Faradaic reactions come into play, a situation that stimulator implants are designed to avoid.
+{\color{blue} Modelling Faradaic current onset allows engineers to predict and avoid such situations in-vivo.
+For this reason the measurements and model fitting are mostly concerned with capturing only the onset of Faradaic conduction.
+The model is not intended to model the behaviour of an electrode array operating in a Faradaic conduction mode.}
 
@@
 Rather we wish to characterise the electrode/electrolyte system in terms of parameters that may be fed into an electrical model.
+
+{
+    \color{blue}
+    The remainder of this manuscript is broken into five sections.
+Section \ref{sect:resistorMesh} details the measurement of the inter-electrode resistances and the generation of a resistor network to replicate these resistances.
+    Sections \ref{sect:cpe} and \ref{sect:faradaic} are concerned with the measurement and parameter fitting of displacement currents and Faradaic currents, respectively, across the electrolyte interface.
+}
 
@@
 
-\section{Resistive Network}
+\section{{\color{blue}Bulk Resistivity / Resistor} Network }
+\label{sect:resistorMesh}
 Six solutions ranging from 1.0X to 0.025X the concentration of a stock PBS solution have been examined.
@@
 
-\section{Displacement Parameters}
+\section{Displacement Parameters {\color{blue}/ CPE}}
+\label{sect:cpe}
 
@@
 
-\section{Faradaic Parameters}
+\section{Faradaic Parameters {\color{blue}/ Diodes}}
+\label{sect:faradaic}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Check that these are in the right order!!!
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \bibitem{Weiland2000}
@@
     {
-        \color{Blue}
+        \color{blue}
         We need this because it represents the resistance of the interface itself, separate from that of the fluid.
@@
 3.
-The transimpedance measurments do not measure impedance across an interface that is passing current and therefore any voltage drop across an interface due to $R_{S}$ would vanish.
+The transimpedance measurements do not measure impedance across an interface that is passing current and therefore any voltage drop across an interface due to $R_{S}$ would vanish.
 The displacement measurements take the voltage across interfaces that are passing stimulus currents.
@@
 
+    {
+        \color{blue}
+
+    }
+
     4.
@@
 
+    {
+        \color{blue}
+        The RC pairs are generated via a Python script for a given frequency range.
+Simulations in this manuscript used RC pairs spanning 1.0 nHz to 1.0 GHz spaced 3 per decade.
+Adding more RC pairs than necessary came at negligible computation cost and having the circuited constructed in an automated fashion to satisfy the given frequency range adds no extra work.
+    }
+
     5. p 6, col 1, line 11. ``rate dependent on the log'' should be ``rate varies exponentially''. i.e. Tafel equation.
+
     {
@@
 
+    {
+        \color{blue}
+        Of course, thank you.
+    }
+
     2.
@@
 Additionally, I propose that the authors expand the section headings to include this information.
+
+    {
+        \color{blue}
+        Heading expanded slightly to include model elements.
+    }
 

### 2014-04-07 paper.tex
Added new section and explained memristors

@@
     We measure this response in various solutions with an electrode array as is commonly used with spinal cord stimulation (SCS) implants.
-We match the parameters of a compact non-linear interface model to the measured response at each concentration.
+We match the parameters of a compact non-linear electrode/electrolyte interface model to measured responses at various concentrations of PBS.
 }
@@
 
-In an implanted setting there is no reference electrode and many of the well established electrochemical measurement regimes do not apply.
-In this manuscript we measure the behaviour an electrode/electrolyte situation as it would be seen from an implant device.
-
-A solution of Phosphate Buffered Saline (PBS) diluted to one-tenth concentration (0.1X) is common in the case of Spinal Cord Stimulators (SCS), while full concentration (1.0X) PBS is considered more representative of the situation in blood.
-
-In this manuscript we report how the parameters of a non-linear model change as the concentration of saline is varied.
-We refine a series of measurements compatible with commercially available medical electrodes in physiological saline that allow us to describe the impedance with minimal parameters.
-We place these parameters in context with a biological measurement made in the spinal cavity of a live sheep.
-
-The electrode used in this work is a commercial linear array of eight platinum electrodes intended for SCS implantation called an ``Octrode''.~\cite{StJudeOctrode} A picture of an Octrode is presented in figure~\ref{fig:octrode}.
-
-The electrical interface model of \cite{Franks2005} and \cite{ScottSingle2013} has two parts, a displacement branch and a Faradaic branch.
-While Scott and Single \cite{ScottSingle2013} incorporate a memristor into their model, it has been omitted here for simplicity.
-Its contribution is limited to situations where diffusion limited Faradaic reactions come into play, a situation that stimulator implants are designed to avoid.
-{\color{blue} Modelling Faradaic current onset allows engineers to predict and avoid such situations in-vivo.
-For this reason the measurements and model fitting are mostly concerned with capturing only the onset of Faradaic conduction.
-The model is not intended to model the behaviour of an electrode array operating in a Faradaic conduction mode.}
-
-It has been suggested that the primary coupling mechanism between platinum electrodes and physiological saline is the reversible evolution of gas, probably oxygen, at the platinum surface, which dissolves without bubble formation.\cite{Greatbatch1969} Understanding the exact mechanism of displacement or Faradaic charge transfer at the electrode surface is beyond the scope of this work.
-Rather we wish to characterise the electrode/electrolyte system in terms of parameters that may be fed into an electrical model.
-
-{
-    \color{blue}
-    The remainder of this manuscript is broken into five sections.
-Section \ref{sect:resistorMesh} details the measurement of the inter-electrode resistances and the generation of a resistor network to replicate these resistances.
-    Sections \ref{sect:cpe} and \ref{sect:faradaic} are concerned with the measurement and parameter fitting of displacement currents and Faradaic currents, respectively, across the electrolyte interface.
-}
-
 \begin{figure}
@@
 \end{figure}
+
+In an implanted setting there is no reference electrode and many of the well established electrochemical measurement regimes do not apply.
+In this manuscript we measure the behaviour an electrode/electrolyte situation as it would be seen from an implant device.
+
+The electrode used in this work is a commercial linear array of eight platinum electrodes intended for SCS implantation called an ``Octrode''.~\cite{StJudeOctrode} A picture of an Octrode is presented in figure~\ref{fig:octrode}.
+A solution of Phosphate Buffered Saline (PBS) diluted to one-tenth concentration (0.1X) is common in the case of Spinal Cord Stimulators (SCS), while full concentration (1.0X) PBS is considered more representative of the situation in blood.
+
+% {
+%     \color{red}
+% In this manuscript we report how the parameters of a non-linear model change as the concentration of saline is varied.
+We refine a series of measurements compatible with commercially available medical electrodes in physiological saline that allow us to describe the impedance with minimal parameters.
+We place these parameters in context with a biological measurement made in the spinal cavity of a live sheep.
+
+%     THIS IS IN THE ABSTRACT
+% }
+
+Six solutions ranging from 1.0X to 0.025X the concentration of a stock PBS solution have been examined.
+The ingredients of that stock solution are given in table~\ref{tab:PBSrecipe}.
+
+{
+    \color{blue}
+\section{Compact Non-Linear Electrical Model}
 
@@
 
+This manuscript uses an adapted version of the compact non-linear model presented by Scott and Single \cite{ScottSingle2013}.
+The model is compact in that it is suitable for entering into SPICE, i.e., freely available electrical circuit simulation software.
+The schematic for the model used here is presented be seen in Figure \ref{fig:schematic}.
+}
+The electrical interface model of \cite{Franks2005} {\color{red} (is this true, I can't see a faradaic part in Franks)} and \cite{ScottSingle2013} has two parts, a displacement branch and a Faradaic branch.
+While Scott and Single \cite{ScottSingle2013} incorporate memristors into their model, they has been omitted here for simplicity.
+{
+    \color{blue}
+    The memristors in \cite{ScottSingle2013} are used to mimic a diffusion limited current conduction mode, i.e., their purpose is to throttle electrical current associated with Faradaic reactions.
+In an implanted setting an electrode should never be operated in a Faradaic counduction mode, and certainly never to the point of becoming diffusion limited.
+It is for this reason the memristors have been removed.
+}
+
+% Contribution from memristive elements is limited to situations where diffusion limited Faradaic reactions come into play, a situation that stimulator implants are designed to avoid.{
+%     \color{blue}
+%     Modelling Faradaic current onset allows engineers to predict and avoid such situations in-vivo.
+For this reason the measurements and model fitting are primarily concerned with capturing the onset of Faradaic conduction, as is modelled by diodes.
+The model used here is not intended to model the behaviour of an electrodes operating in a Faradaic conduction mode.
+It is for this reason we have removed the memristors and limit the model to a single pair of diodes, thus capturing only the beginning of the primary Faradaic component.
+% }
+
+It has been suggested that the primary coupling mechanism between platinum electrodes and physiological saline is the reversible evolution of gas, probably oxygen, at the platinum surface, which dissolves without bubble formation.\cite{Greatbatch1969} Understanding the exact mechanism of displacement or Faradaic charge transfer at the electrode surface is beyond the scope of this work.
+Rather we wish to characterise the electrode/electrolyte system in terms of a {\color{blue} small number of} parameters that may be fed into an electrical model.
+
+{
+    \color{blue}
+    The remainder of this manuscript is broken into five sections.
+Section \ref{sect:resistorMesh} details the measurement of the inter-electrode resistances and the generation of a resistor network to replicate these resistances.
+    Sections \ref{sect:cpe} and \ref{sect:faradaic} are concerned with the measurement and parameter fitting of displacement currents and Faradaic currents, respectively, across the electrolyte interface.
+Section \ref{sect:in-vivo} compares the results obtained in PBS with measurements in-vivo.
+Finally, in Section \ref{sect:conclusion} we summarise our findings and give concluding comments.
+{\color{red} Is this necessary?
+This is obvious.}
+}
+
 \section{{\color{blue}Bulk Resistivity / Resistor} Network }
 \label{sect:resistorMesh}
-Six solutions ranging from 1.0X to 0.025X the concentration of a stock PBS solution have been examined.
-The ingredients of that stock solution are given in table~\ref{tab:PBSrecipe}.
-The pH level of the stock was measured, using a calibrated EDT Instruments BA-350 pH meter, to have a pH of 7.4. No pH adjustments were made to the derived solutions.
 
@@
 Measurements of the inter-electrode impedance were made using a Tektronix TPS2014 DSO with four fully isolated and floating channels; an Agilent 33220A Function Generator; and a desktop PC controlling the instruments via Python 2.7.
+
+The pH level of the stock was measured, using a calibrated EDT Instruments BA-350 pH meter, to have a pH of 7.4. No pH adjustments were made to the derived solutions.
 
@@
 These measurements were made in still solution and we expect stirring will further reduce settling time.} we concluded that a wait-time of 64 seconds was sufficient.
+
 \begin{figure}
@@
 \section{In-vivo measurements of sheep}
-
+\label{sect:in-vivo}
 \begin{figure}
@@
 \section{Conclusion}
-
+\label{sect:conclusion}
+\label{sect:faradaic}
 We have used the parameters of a compact electrical model of an implantable electrode as a way of objectively comparing scenarios.
@@
         \color{blue}
-        Heading expanded slightly to include model elements.
+        An extra section explaining a bit about the model and the layout of the paper has been added and the section headings have been expanded slightly to include the names of relevant model elements.
     }

### 2014-04-08 paper.tex
Tweaked tables

@@
 The electrical interface model of \cite{Franks2005} {\color{red} (is this true, I can't see a faradaic part in Franks)} and \cite{ScottSingle2013} has two parts, a displacement branch and a Faradaic branch.
-While Scott and Single \cite{ScottSingle2013} incorporate memristors into their model, they has been omitted here for simplicity.
-{
+
+Scott and Single \cite{ScottSingle2013} incorporate memristors into their model. {
     \color{blue}
-    The memristors in \cite{ScottSingle2013} are used to mimic a diffusion limited current conduction mode, i.e., their purpose is to throttle electrical current associated with Faradaic reactions.
-In an implanted setting an electrode should never be operated in a Faradaic counduction mode, and certainly never to the point of becoming diffusion limited.
-It is for this reason the memristors have been removed.
+    These memristors are used to mimic a diffusion limited current conduction mode, i.e., their purpose is to throttle electrical current associated with Faradaic reactions.
+In an implanted setting an electrode should never be operated in a Faradaic counduction mode and certainly never to the point of becoming diffusion limited; for this reason the memristors have been omitted.
 }
@@
 \begin{table}
+    \caption{PBS stock solution ingredients}
+    \label{tab:PBSrecipe}
     \begin{center}
-        \begin{tabular}{|r|l|}
+        \begin{tabular}{r | l}
+            Ingredient & Quantity \\
             \hline
-            $NaCl$ & $8.0\thinspace g$ \\ \hline
-            $KCl$ & $0.2\thinspace g$ \\ \hline
-            $Na_{2}HPO_{4}$ & $1.44\thinspace g$ \\ \hline
-            $KH_{2}PO_{4}$ & $0.24\thinspace g$ \\ \hline
-            Distilled Water & $1.0$\thinspace L \\ \hline
+            $NaCl$ & $8.0\thinspace g$ \\
+            $KCl$ & $0.2\thinspace g$ \\
+            $Na_{2}HPO_{4}$ & $1.44\thinspace g$ \\
+            $KH_{2}PO_{4}$ & $0.24\thinspace g$ \\
+            Distilled Water & $1.0$\thinspace L \\
         \end{tabular}
     \end{center}
-    \caption{PBS stock solution ingredients}
-    \label{tab:PBSrecipe}
 \end{table}
@@
 
-The pH level of the stock was measured, using a calibrated EDT Instruments BA-350 pH meter, to have a pH of 7.4. No pH adjustments were made to the derived solutions.
+The pH level of the stock solution was measured, using a calibrated EDT Instruments BA-350 pH meter, to have a pH of 7.4. No pH adjustments were made to the derived solutions.
+
+{
+    \color{blue}
+
+    In Table \ref{tab:RESparams}, $\sigma$ refers to the conductivity of the solution, measured in units of Siemens per centimeter.
+Solution conductivity was measured using an EDT instruments RE 388 TX Microprocessor Conductivity Meter.
 
@@
 We determine the fixed resistance of a single interface, $R_{S}$, when fitting parameters to the displacement component.
+}
 
@@
 \begin{table}
+    \caption{Resistor mesh parameters.\\ Electrolyte conductivity ($\sigma$) is expressed in units of $S/cm$}
+    \label{tab:RESparams}
     \begin{center}
-        \begin{tabular}{|r|l|}
+        \begin{tabular}{r | l}
+            Parameter & Value \\
             \hline
-            $R_{eri}$ & 0.407 / $\sigma$ \\ \hline
-            $R_{sri}$ & $R_{eri}$ $3/4$ \\ \hline
-            $R_{li}$ & 3.71 / $\sigma$ \\ \hline
-            Depth & 5 layers \\ \hline
-            Padding & 3 layers \\ \hline
+            $R_{eri}$ ($\Omega$)& 0.407/$\sigma\\
+            $R_{sri}$ ($\Omega$)& $R_{eri}\times 3/4\\
+            $R_{li}$ ($\Omega$)& 3.71 / $\sigma$ \\
+            Depth (layers) & 5 \\
+            Padding (layers) & 3 \\
         \end{tabular}
     \end{center}
-    \caption{Resistor mesh parameters. $\sigma$ measured in units of $S/cm$}
-    \label{tab:RESparams}
+\end{table}
+
+\begin{table}
+    \caption{Measured conductivity of PBS solutions. {\color{red} Should I add this?}}
+    \label{tab:PBSconductivity}
+    \begin{center}
+        \begin{tabular}{r | l}
+            Concentration (X-PBS) & Conductivity ($\mu S/cm$)\\
+            \hline
+            1.0 & $15800$ \\
+            0.5 & $4360$\\
+            0.25 & $1860$\\
+            0.05 & $931$\\
+            0.025 & $492$\\
+        \end{tabular}
+    \end{center}
 \end{table}
@@
 \begin{table}
+    \caption{Displacement parameter scaling}
+    \label{tab:CPEparams}
     \begin{center}
-        \begin{tabular}{|r|l|}
+        \begin{tabular}{r | l}
+            Parameter & Value \\
             \hline
-            $m$ & $1.34$ \\ \hline
-            $k$ & $1.773$\\ \hline
-            $|Z|\: @\: 1Hz$& $3284 \times concentration^{-0.158}$ \\ \hline
-            $R_{S}$ & $13.38 \times concentration^{-0.8397} $\\ \hline
+            $m$ & $1.34$ \\
+            $k$ & $1.773$\\
+            $|Z|\: @\: 1Hz$ $(\Omega)$& $3284 \times concentration^{-0.158}$ \\
+            $R_{S}$ $(\Omega)$& $13.38 \times concentration^{-0.8397} $\\
         \end{tabular}
     \end{center}
-    \caption{Displacement parameter scaling}
-    \label{tab:CPEparams}
 \end{table}
@@
 \begin{table}
+    \caption{Faradaic parameters}
+    \label{tab:FaradaicParams}
     \begin{center}
-        \begin{tabular}{|r|l|}
+        \begin{tabular}{r | l}
+            Parameter & Value \\
             \hline
-            $i0$ & 2.757e-12\\ \hline
-            $n$ & 1.36\\ \hline
+            $i0$ & $2.757\thinspace pA$\\
+            $n$ & 1.36\\
         \end{tabular}
     \end{center}
-    \caption{Faradaic parameters}
-    \label{tab:FaradaicParams}
 \end{table}
@@
 
-    {\color{blue}
+    {
+        \color{blue}
         The diodes are there to model the change in current attributed to the first biologically damaging reaction that occurs at the electrode/electrolyte interface.
@@
     3.
-The parameters provided in Table II include reference to an unexplained term sigma (σ).
+The parameters provided in Table II include reference to an unexplained term sigma ($\sigma$).
 I presume this is the conductivity of saline (correct symbol and units for conductivity).

### 2014-04-10 paper.tex
Added graphics, addressed a few reviewer comments

@@
 \author{Mark~H.~Jones and Jonathan~Scott,~\IEEEmembership{Senior Member,~IEEE}
-\thanks{Mark~H.~Jones is with the School of Electronic Engineering, University of Waikato, New Zealand, e-mail: markjones112358@gmail.com.}%
+    \thanks{Mark~H.~Jones is with the School of Electronic Engineering, University of Waikato, New Zealand, e-mail: markjones112358@gmail.com}%
 \thanks{Jonathan Scott is with the School of Electronic Engineering, University of Waikato, New Zealand.}
@@
 
-Six solutions ranging from 1.0X to 0.025X the concentration of a stock PBS solution have been examined.
+Six solutions ranging from 1.0X to 0.025X the concentration of a stock PBS solution (by mass) have been examined.
 The ingredients of that stock solution are given in table~\ref{tab:PBSrecipe}.
@@
 \section{Compact Non-Linear Electrical Model}
-
+\label{sect:resistorNetwork}
 \begin{figure}
@@
 
-This manuscript uses an adapted version of the compact non-linear model presented by Scott and Single \cite{ScottSingle2013}.
+In this manuscript we use an adapted version of the compact non-linear model presented by Scott and Single \cite{ScottSingle2013}.
 The model is compact in that it is suitable for entering into SPICE, i.e., freely available electrical circuit simulation software.
@@
 The mesh depth and padding values of five columns and three rows, respectively, has been taken directly from \cite{ScottSingle2013}.
+{\color{blue} Using these parameters together with an array of 8 electrodes leads to a resistor network having 205 resistors.}
 A numerical fit was made to the two independent scaling parameters $R_{eri}$ and $R_{li}$
@@
 \begin{table}
-    \caption{Resistor mesh parameters.\\ Electrolyte conductivity ($\sigma$) is expressed in units of $S/cm$}
-    \label{tab:RESparams}
-    \begin{center}
-        \begin{tabular}{r | l}
-            Parameter & Value \\
-            \hline
-            $R_{eri}$ ($\Omega$)& 0.407/$\sigma\\
-            $R_{sri}$ ($\Omega$)& $R_{eri}\times 3/4\\
-            $R_{li}$ ($\Omega$)& 3.71 / $\sigma$ \\
-            Depth (layers) & 5 \\
-            Padding (layers) & 3 \\
-        \end{tabular}
-    \end{center}
-\end{table}
-
-\begin{table}
-    \caption{Measured conductivity of PBS solutions. {\color{red} Should I add this?}}
+    \caption{Measured conductivity of PBS solutions. {\color{red} Should I add this? The meter was uncalibrated}}
     \label{tab:PBSconductivity}
@@
 
+\begin{table}
+    \caption{Resistor mesh parameters. Electrolyte conductivity ($\sigma$) is expressed in units of $S / cm$}
+    \label{tab:RESparams}
+    \begin{center}
+        \begin{tabular}{r | l}
+            Parameter & Value \\
+            \hline
+            $R_{eri}$ ($\Omega$)& 0.407 / $\sigma$\\
+            $R_{sri}$ ($\Omega$)& $R_{eri}\cdot 3/4$\\
+            $R_{li}$ ($\Omega$)& 3.71 / $\sigma$ \\
+            Depth (layers) & 5 \\
+            Padding (layers) & 3 \\
+        \end{tabular}
+    \end{center}
+\end{table}
+
+\begin{figure}
+    \begin{center}
+        \includegraphics[width=\columnwidth]{graphics/resistorMesh_sideways}
+    \end{center}
+    \caption{Layout of the generated resistor mesh used to connect each of the interface models. The final mesh for an 8 electrode array contains 205 resistors.}
+    \label{fig:mesh}
+\end{figure}
+
 \section{Displacement Parameters {\color{blue}/ CPE}}
 \label{sect:cpe}
-
+110 elements
 Displacement currents are responsible for capacitive behaviour at interfacial boundaries.
@@
 The placement of R-C pairs within the CPE is determined by Morrison's parameters $m$ and $k$, where $k$ determines the spacing, or density, of R-C branches and $m$ determines the resulting slope.
+{\color{blue} The R-C pairs were generated via Python script for to span 1\thinspace nHz--1\thinspace GHz with a spacing of 3 pairs per decade.
+The final CPE contains 55 branches i.e.
+110 elements are used to create the CPE model.}
+
 We measure displacement currents by sweeping the frequency of a sinusoidal stimulus across electrodes 2 and 7 of the Octrode while measuring the voltage between electrodes 2 and 3 (numbering shown in Fig.~\ref{fig:octrode}).
 This allows for the measurement of a single interface impedance in series with the resistance presented by the bulk solution.
+
 \begin{figure}
@@
 \begin{table}
-    \caption{Displacement parameter scaling}
+    \caption{Displacement parameter scaling.\\ $conc.$ refers to the mass concentration of PBS.}
     \label{tab:CPEparams}
@@
             $k$ & $1.773$\\
-            $|Z|\: @\: 1Hz$ $(\Omega)$& $3284 \times concentration^{-0.158}$ \\
-            $R_{S}$ $(\Omega)$& $13.38 \times concentration^{-0.8397} $\\
+            $|Z|\: @\: 1Hz$ $(\Omega)$& $3284 \times conc^{-0.158}$ \\
+            $R_{S}$ $(\Omega)$& $13.38 \times conc^{-0.8397} $\\
         \end{tabular}
@@
 \end{figure}
+
 Cogan states the main differences between in-vivo and in-vitro responses come down to temperature, the presence of organic species, tortuous diffusion path for charge carriers, physiological responses of the host to a foreign body, and uncertain concentrations of electrolytes and buffers near the electrode surface.\cite{Cogan2008}
@@
 
-The displacement measurements were repeated inside the spinal canal of a live sheep, just outside the dura as shown in figure~\ref{fig:sheepSpine}.
-The sheep were prepared and anaesthetised using the procedures described in \cite{Parker2013} under the Animal Care and Ethics Committee approval of the Royal North Shore Hospital, Sydney.
+{\color{blue} Each of the model characterisation} measurements were repeated inside the spinal canal of living sheep, just outside the dura as shown in figure~\ref{fig:sheepSpine}.
+Two sheep were prepared and anaesthetised using the procedures described in \cite{Parker2013} under the Animal Care and Ethics Committee approval of the Royal North Shore Hospital, Sydney.
 The study complied with the Australian Code of Practice for the Care and Use of Animals for Scientific Purposes.
+
+{
+    \color{blue}
+    Transimpedance measurements in-vivo were done using additional configurations than were carried out in section \ref{sect:resistorNetwork}.
+The same measurements were captured but a more complete stimulus--measure regieme was tried in order to minimise the effect of nearby bone having too large an effect on a small number of measurements.
+}
+\begin{table}
+    \caption{Model parameters fitted to sheep data}
+    \label{tab:sheepParameters}
+    \begin{center}
+        \begin{tabular}{r | l}
+            Parameter & Value \\
+            \hline
+            $R_{eri}$ & $500\thinspace \Omega$\\
+            $R_{sri}$ & $375\thinspace \Omega$\\
+            $R_{li}$  & $176\thinspace \Omega$\\
+            $m$       & $1.34$\\
+            $k$       & $1.77$\\
+            $|Z|\: @\: 1Hz$& $11300\thinspace \Omega$\\
+            $R_{s}$   & $126\thinspace \Omega$
+        \end{tabular}
+    \end{center}
+\end{table}
+
+\begin{figure}
+    \begin{center}
+        \includegraphics{graphics/sheep_transimpedance}
+    \end{center}
+    \caption{Comparison between in-vivo transresistance measurements (blue dots) and simulation results using fitted mesh parameters (red trace).}
+    \label{fig:transimpedance_sheep}
+\end{figure}
+
 Four measurements taken at regular intervals over a period of 30 minutes are presented in figures~\ref{fig:displacement_sheepCPEMagnitude} and~\ref{fig:displacement_sheepCPEPhase} on top of the array of traces for saline taken from figures~\ref{fig:CPE_Magnitude} and~\ref{fig:CPE_Phase}.
@@
 \label{sect:conclusion}
-\label{sect:faradaic}
 We have used the parameters of a compact electrical model of an implantable electrode as a way of objectively comparing scenarios.
@@
 
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{graphics/MarkJones-Aug13.jpg}}]{Mark Jones}
+received the B.Sc. degree in Physics in 2008 and the M.E. degree in Microwave Electronics in 2009 from The University of Waikato, Hamilton, New Zealand.
+He is working towards a Ph.D. in Electrical Engineering, also at The University of Waikato.
+\end{IEEEbiography}
+
 \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{graphics/JBSatNICTA.jpg}}]{Jonathan Scott}
@@
 publications and holds a number of patents.
-\end{IEEEbiography}
-
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{graphics/MarkJones-Aug13.jpg}}]{Mark Jones}
-received the B.Sc. degree in Physics in 2008 and the M.E. degree in Microwave Electronics in 2009 from The University of Waikato, Hamilton, New Zealand.
-He is working towards a Ph.D. in Electrical Engineering, also at The University of Waikato.
 \end{IEEEbiography}
@@
     {
-        \color{blue}
-
+        \color{red}
+        What should I say to this?.
+We measured what we measured, no visible gas evolution.
+The results look consistant.
+We are happy to accept that we may have pushed the electrodes too far in the solution at low frequencies, regardless of this fact we have data here and wish to present it.
     }
@@
 As far as I know, there is no satisfactory explanation yet for the CPE so perhaps this is a significant clue.
+
+   {
+       \color{red}
+       HELP, how do I approach this?
+   }
+
 }
@@
 For completeness, I recommend the authors explain this term, provide the numeric value (or values) that they used, provide how they adjusted this with concentration, and reference the source of their numeric data.
+    {
+        \color{blue}
+        This term has been made clearer by adding a line to the table caption and by adding a paragraph near the end of Section \ref{sect:resistorNetwork} explaining where the source of the values.
+    }
 
@@
 
+    {
+        \color{blue}
+        A diagram showing the layout of the resistor mesh has been added along with the total number of resistors in the mesh for an 8 electrode system.
+    }
+
     5.
@@
 
+    {
+        \color{blue}
+
+    }
+
     6.
@@
 As different readers will have different interpretations (mass concentration=0.9\%, molar concentration = 0.154M), I recommend the authors clearly explain the meaning of this term.
+
+    {
+        \color{blue}
+        Table \ref{tab:CPEparams} has been amended to inclued mention of 'concentration' being that of mass concentration of PBS.
+    }
 
@@
 
+    {
+        \color{blue}
+        That is a very important piece of information we've missed! Thank you for bringing that to our attention.
+
+    }
+
     8.
@@
 
+    {
+        \color{blue}
+        The overall size of the spice file that contains all the elements of the 8 electrode model, one element per line, is 370 lines including some unnecessary formatting lines.
+A standard Dell optiplex workstation can generate that file using the model parameters, simulate the model using ngSPICE, and read the output back from the simulation result in under a second.
+    }
+
     9.
 In their conclusions, I recommend the authors restate any limitations in their model that they mentioned earlier in the text (e.g., 0.9v limitation) and provide an honest discussion regarding the limits of their model.
+    {
+        \color{blue}
+
+    }
 }

### 2014-04-11 paper.tex
Added transimpedance sheep graphs

@@
 \usepackage{url}
+\usepackage{ulem}
 \usepackage[usenames, dvipsnames]{color}
@@
 
-Cogan states the main differences between in-vivo and in-vitro responses come down to temperature, the presence of organic species, tortuous diffusion path for charge carriers, physiological responses of the host to a foreign body, and uncertain concentrations of electrolytes and buffers near the electrode surface.\cite{Cogan2008}
-Nevertheless, electrical engineers use baths of saline as a substitute for in-vivo testing (a ``phantom'') due to its convienience.
-We now test the claim that 0.1X PBS is a reasonable representation of the spine of a living sheep.
-
-{\color{blue} Each of the model characterisation} measurements were repeated inside the spinal canal of living sheep, just outside the dura as shown in figure~\ref{fig:sheepSpine}.
-Two sheep were prepared and anaesthetised using the procedures described in \cite{Parker2013} under the Animal Care and Ethics Committee approval of the Royal North Shore Hospital, Sydney.
-The study complied with the Australian Code of Practice for the Care and Use of Animals for Scientific Purposes.
-
-{
-    \color{blue}
-    Transimpedance measurements in-vivo were done using additional configurations than were carried out in section \ref{sect:resistorNetwork}.
-The same measurements were captured but a more complete stimulus--measure regieme was tried in order to minimise the effect of nearby bone having too large an effect on a small number of measurements.
-}
 \begin{table}
@@
     \begin{center}
-        \includegraphics{graphics/sheep_transimpedance}
+        \includegraphics{graphics/sheep_transimpedance_magnitude}
     \end{center}
-    \caption{Comparison between in-vivo transresistance measurements (blue dots) and simulation results using fitted mesh parameters (red trace).}
-    \label{fig:transimpedance_sheep}
+    \caption{\color{blue} Comparison between the magnitude of in-vivo transresistance measurements (blue dots) and simulation results using fitted mesh parameters (red trace).}
+    \label{fig:transimpedance_sheep_mag}
 \end{figure}
 
-Four measurements taken at regular intervals over a period of 30 minutes are presented in figures~\ref{fig:displacement_sheepCPEMagnitude} and~\ref{fig:displacement_sheepCPEPhase} on top of the array of traces for saline taken from figures~\ref{fig:CPE_Magnitude} and~\ref{fig:CPE_Phase}.
+\begin{figure}
+    \begin{center}
+        \includegraphics{graphics/sheep_transimpedance_phase}
+    \end{center}
+    \caption{\color{blue} Comparison between the phase of in-vivo transresistance measurements (blue dots) and simulation results using fitted mesh parameters (red trace).
+The simulation mesh does not capture any phase relationship due to being purely resistive.}
+    \label{fig:transimpedance_sheep_phase}
+\end{figure}
+
+Cogan states the main differences between in-vivo and in-vitro responses come down to temperature, the presence of organic species, tortuous diffusion path for charge carriers, physiological responses of the host to a foreign body, and uncertain concentrations of electrolytes and buffers near the electrode surface.\cite{Cogan2008}
+Nevertheless, electrical engineers use baths of saline as a substitute for in-vivo testing (a ``phantom'') due to its convienience.
+We now test the claim that 0.1X PBS is a reasonable representation of the spine of a living sheep.
+
+{\color{blue} Each of the model characterisation} measurements were repeated inside the spinal canal of living sheep, just outside the dura as shown in figure~\ref{fig:sheepSpine}.
+Two sheep were prepared and anaesthetised using the procedures described in \cite{Parker2013} under the Animal Care and Ethics Committee approval of the Royal North Shore Hospital, Sydney.
+The study complied with the Australian Code of Practice for the Care and Use of Animals for Scientific Purposes.
+
+{
+    \color{blue}
+    Transimpedance measurements in-vivo were done using additional configurations than were carried out in section \ref{sect:resistorNetwork}.
+The same measurements were captured but a more complete stimulus--measure regieme was tried in order to minimise the effect of nearby bone having too large an effect on a small number of measurements.
+Time constraints with the live animal meant only one dataset was obtained for transimpedance, shown in figures~\ref{fig:displacement_sheepCPEMagnitude} and \ref{fig:displacement_sheepCPEPhase} along with results obtained via simulation using fitted parameters.
+}
+
+{\color{blue}
+    Four measurements of displacement current (CPE element in the model) were} taken at regular intervals over a period fo 30 minutes and have been presented in figures~\ref{fig:displacement_sheepCPEMagnitude} and~\ref{fig:displacement_sheepCPEPhase}.
+{\color{blue} These measurements appear on top of the traces taken from figures~\ref{fig:CPE_Magnitude} and~\ref{fig:CPE_Phase} for comparison.}
+
+{
+    \color{blue}
+    The measured transimpedances shown in figure~\ref{fig:displacement_sheepCPEMagnitude} show {\color{red} show what??? Fig 16 shows how much reactance the tissue has which is enormous.} 
+}
 Although it is clear that there are complications in vivo, a 0.25X PBS saline offers a good approximation to the resistive part of the trace.
@@
     \end{center}
-    \caption{Comparison between the magnitude of CPE in live sheep (blue error bars) against each of the PBS traces from figure~\ref{fig:CPE_Magnitude} (grey lines) and a simulated fit to the sheep data (red trace).}
+    \caption{\color{blue} Comparison between the mean magnitude of measured displacement currents in four live sheep (blue trace), each of the PBS traces from figure~\ref{fig:CPE_Magnitude} (grey lines), and a simulated fit to the sheep data (red trace).
+Error bars have been placed one standard deviation either side of the mean for measured data.}
     \label{fig:displacement_sheepCPEMagnitude}
@@
     \end{center}
-    \caption{Comparison between the phase response of the CPE in live sheep (blue error bars) against each of the PBS traces taken from figure~\ref{fig:CPE_Phase} (grey lines) and a simulated fit to the sheep data (red trace).}
+    \caption{\color{blue} Comparison between the mean phase response of measured displacement currents in four live sheep (blue trace), each of the PBS traces taken from figure~\ref{fig:CPE_Phase} (grey lines), and a simulated fit to the sheep data (red trace).
+Error bars have been placed one standard deviation either side of the mean for measured data.}
     \label{fig:displacement_sheepCPEPhase}
@@
 We have measured how changing the concentration of PBS affects the parameters of this model.
-We have drawn direct relationships with concentration sufficient to predict interface characteristics at arbitrary dilutions of PBS.
+We have drawn direct relationships with concentration {\color{blue} and conductivity} sufficient to predict interface characteristics at arbitrary dilutions of PBS.
 We found that the magnitude of the CPE element moves much more slowly with concentration whereas the resistance moved almost linearly.
-Using DC measurements we conclude that the salinity of the bulk does not affect Faradaic conduction until a threshold voltage is reached.
-We hypothesise that this is because the double-layer sets the effective concentration of ions in a localised volume surrounding each electrode.
-In-vivo measurements of platinum electrodes in sheep spine showed that no single concentration of PBS matches both the CPE and the resistive characteristics at once.
-Nevertheless, 0.1X PBS is a good compromise.
+Using DC measurements we conclude that the {\color{blue} concentration of PBS has no effect on the onset of Faradaic conduction for the range of concentrations investigated.} {\color{Green} \sout{salinity of the bulk does not affect Faradaic conduction until a threshold voltage is reached}}.
+We hypothesise that this is because the double-layer sets the effective concentration of ions {\color{blue}, those involved in the Faradaic reactions,} in a localised volume surrounding each electrode.
+In-vivo measurements of platinum electrodes in sheep spine show that no single concentration of PBS matches both the CPE and the resistive characteristics at once.
+{\color{blue} These measurements also reveal a considerable amount of reactance (see transimpedance measurements in-vivo) that is captured neither by PBS {\color{red} [I'm going to have to include phase data for the results in figure \ref{fig:transresistance} aren't I...; which is dangerous because I don't think I've ever looked at it.]} nor the model presented when using a purely resistive spreading resistance mesh.} Nevertheless, {\color{blue}if a single solution of PBS is to be used as a human phantom, a one-tenth concentration solution (by mass)} is a good compromise.
+
+{
+    \color{blue}
+    The model is limited to predicting only the onset of Faradaic current conduction, i.e.
+it does not model operation in a diffussion limited scenario as it omits the memristors of \cite{ScottSingle2013}.
+}
 
 \section*{Acknowledgment}
-The authors wish to acknowledge the The University of Waikato for financial support and Saluda Medical for the use of facilities and equipment.
+{\color{red} [Can we acknowledge Peter Single's help?]} The authors wish to acknowledge the The University of Waikato for financial support and Saluda Medical for the use of facilities and equipment.
 
@@
 \bibitem{ScottSingle2013}
+{\color{red} HAS THIS BEEN PUBLISHED YET?}
     Jonathan Scott and Peter Single,
@@
         \color{blue}
-        Of course, thank you.
+        Of course, see amended abstract.
     }

### 2014-04-13 paper.tex
Weekend edits

@@
 }
-The electrical interface model of \cite{Franks2005} {\color{red} (is this true, I can't see a faradaic part in Franks)} and \cite{ScottSingle2013} has two parts, a displacement branch and a Faradaic branch.
+The electrical interface model of \cite{Franks2005} and \cite{ScottSingle2013} has two parts, a displacement branch and a Faradaic branch.
 
@@
 Finally, in Section \ref{sect:conclusion} we summarise our findings and give concluding comments.
-{\color{red} Is this necessary?
-This is obvious.}
 }
@@
 
-\begin{table}
-    \caption{Measured conductivity of PBS solutions. {\color{red} Should I add this? The meter was uncalibrated}}
-    \label{tab:PBSconductivity}
-    \begin{center}
-        \begin{tabular}{r | l}
-            Concentration (X-PBS) & Conductivity ($\mu S/cm$)\\
-            \hline
-            1.0 & $15800$ \\
-            0.5 & $4360$\\
-            0.25 & $1860$\\
-            0.05 & $931$\\
-            0.025 & $492$\\
-        \end{tabular}
-    \end{center}
-\end{table}
+% \begin{table}
+%     \caption{Measured conductivity of PBS solutions. {\color{red} Should I add this? The meter was uncalibrated}}
+%     \label{tab:PBSconductivity}
+%     \begin{center}
+%         \begin{tabular}{r | l}
+%             Concentration (X-PBS) & Conductivity ($\mu S/cm$)\\
+%             \hline
+%             1.0 & $15800$ \\
+%             0.5 & $4360$\\
+%             0.25 & $1860$\\
+%             0.05 & $931$\\
+%             0.025 & $492$\\
+%         \end{tabular}
+%     \end{center}
+% \end{table}
 
@@
 \begin{table}
-    \caption{Displacement parameter scaling.\\ $conc.$ refers to the mass concentration of PBS.}
+    \caption{Displacement parameter scaling. $conc.$ refers to the mass concentration of PBS.}
     \label{tab:CPEparams}
@@
 
-{
-    \color{blue}
-    The measured transimpedances shown in figure~\ref{fig:displacement_sheepCPEMagnitude} show {\color{red} show what??? Fig 16 shows how much reactance the tissue has which is enormous.} 
-}
 Although it is clear that there are complications in vivo, a 0.25X PBS saline offers a good approximation to the resistive part of the trace.
@@
 In-vivo measurements of platinum electrodes in sheep spine show that no single concentration of PBS matches both the CPE and the resistive characteristics at once.
-{\color{blue} These measurements also reveal a considerable amount of reactance (see transimpedance measurements in-vivo) that is captured neither by PBS {\color{red} [I'm going to have to include phase data for the results in figure \ref{fig:transresistance} aren't I...; which is dangerous because I don't think I've ever looked at it.]} nor the model presented when using a purely resistive spreading resistance mesh.} Nevertheless, {\color{blue}if a single solution of PBS is to be used as a human phantom, a one-tenth concentration solution (by mass)} is a good compromise.
+{\color{blue} These measurements also reveal a considerable amount of reactance (see transimpedance measurements in-vivo) that is captured neither by PBS nor the model presented when using a purely resistive spreading resistance mesh.} Nevertheless, {\color{blue}if a single solution of PBS is to be used as a human phantom, a one-tenth concentration solution (by mass)} is a good compromise.
 
@@
 \section*{Acknowledgment}
-{\color{red} [Can we acknowledge Peter Single's help?]} The authors wish to acknowledge the The University of Waikato for financial support and Saluda Medical for the use of facilities and equipment.
+The authors wish to acknowledge the The University of Waikato for financial support and Saluda Medical for the use of facilities and equipment.
+Thanks are extended to Peter Single for help conducting in-vivo measurements.
 

### 2014-04-16 paper.tex
Another round of edits

@@
 \usepackage{url}
-\usepackage{ulem}
 \usepackage[usenames, dvipsnames]{color}
@@
 
-Electrodes in the laboratory are typically tested in a saline solution selected to mimic the circumstances in which they will operate when implanted.
-
 \begin{figure}
@@
 
+Electrodes in the laboratory are typically tested in a saline solution selected to mimic the circumstances in which they will operate when implanted.
 In an implanted setting there is no reference electrode and many of the well established electrochemical measurement regimes do not apply.
-In this manuscript we measure the behaviour an electrode/electrolyte situation as it would be seen from an implant device.
+Here we measure the behaviour an electrode/electrolyte situation as it would be seen from an implant device.
 
@@
     \color{blue}
-\section{Compact Non-Linear Electrical Model}
-\label{sect:resistorNetwork}
+
     \begin{figure}
@@
 
-In this manuscript we use an adapted version of the compact non-linear model presented by Scott and Single \cite{ScottSingle2013}.
+    In this manuscript we use an adapted version of the compact non-linear model presented in \cite{ScottSingle2013}.
 The model is compact in that it is suitable for entering into SPICE, i.e., freely available electrical circuit simulation software.
-The schematic for the model used here is presented be seen in Figure \ref{fig:schematic}.
-}
-The electrical interface model of \cite{Franks2005} and \cite{ScottSingle2013} has two parts, a displacement branch and a Faradaic branch.
-
-Scott and Single \cite{ScottSingle2013} incorporate memristors into their model. {
-    \color{blue}
-    These memristors are used to mimic a diffusion limited current conduction mode, i.e., their purpose is to throttle electrical current associated with Faradaic reactions.
-In an implanted setting an electrode should never be operated in a Faradaic counduction mode and certainly never to the point of becoming diffusion limited; for this reason the memristors have been omitted.
+The schematic for the model used here is presented in Figure \ref{fig:schematic}.
 }
 
-% Contribution from memristive elements is limited to situations where diffusion limited Faradaic reactions come into play, a situation that stimulator implants are designed to avoid.{
-%     \color{blue}
-%     Modelling Faradaic current onset allows engineers to predict and avoid such situations in-vivo.
-For this reason the measurements and model fitting are primarily concerned with capturing the onset of Faradaic conduction, as is modelled by diodes.
-The model used here is not intended to model the behaviour of an electrodes operating in a Faradaic conduction mode.
-It is for this reason we have removed the memristors and limit the model to a single pair of diodes, thus capturing only the beginning of the primary Faradaic component.
-% }
+The electrical interface model of \cite{Franks2005} and \cite{ScottSingle2013} has two parts, a displacement branch and a Faradaic branch.
+{
+    \color{blue}
+    Scott and Single incorporate memristors into their model, used to mimic a diffusion limited current conduction mode, i.e., their purpose is to throttle electrical current associated with Faradaic reactions.
+In an implanted setting an electrode should never be operated in a Faradaic conduction mode and certainly never to the point of becoming diffusion limited; for this reason, memristors have been omitted.
+}
 
 It has been suggested that the primary coupling mechanism between platinum electrodes and physiological saline is the reversible evolution of gas, probably oxygen, at the platinum surface, which dissolves without bubble formation.\cite{Greatbatch1969} Understanding the exact mechanism of displacement or Faradaic charge transfer at the electrode surface is beyond the scope of this work.
-Rather we wish to characterise the electrode/electrolyte system in terms of a {\color{blue} small number of} parameters that may be fed into an electrical model.
+Rather, we wish to characterise the electrode/electrolyte system in terms of a {\color{blue} small number of} parameters that may be fed into an electrical model.
 
@@
 The electrical impedance between two electrodes in an electrolyte arises from two interface impedances in series with the resistance due to the bulk of the electrolyte itself.
-To quantify the impedance presented by a single interface we first need to understand the inter-electrode resistances presented by the electrolyte bulk.
-As there are always two interface impedances between any two electrodes, inter-electrode resistances cannot be measured in isolation.
+To quantify the impedance presented by a single interface we first need to determine inter-electrode resistance presented by the electrolyte bulk.
+{\color{blue} Finding these resistances allows us to quantify the interface's impedance via subtraction.} As there are always two interface impedances between any two electrodes, inter-electrode resistances cannot be measured in isolation.
 
 In \cite{ScottSingle2013}, a series of transresistance measurements were used in conjunction with a physical description of the electrode geometry to build up a representative network of resistors.
-The network in that paper was defined using five parameters: $R_{eri}$, $R_{lri}$, $R_{li}$, mesh depth, and edge depth.
+That resistor network was defined using five parameters: $R_{eri}$, $R_{lri}$, $R_{li}$, mesh depth, and edge depth.
 Readers are referred to \cite{ScottSingle2013} for the interpretation of these model parameters.
-Repeating that work, a resistor network that connects each of the eight electrodes is constructed, mimicking the resistances due to the solution bulk.
+Repeating that work, we have created a network of resistors that mimic the resistances due to the solution's bulk conductivity.
 
 The mesh depth and padding values of five columns and three rows, respectively, has been taken directly from \cite{ScottSingle2013}.
-{\color{blue} Using these parameters together with an array of 8 electrodes leads to a resistor network having 205 resistors.}
-A numerical fit was made to the two independent scaling parameters $R_{eri}$ and $R_{li}$
+{\color{blue} These parameters, together with an array of 8 electrodes, leads to a generated network of 205 resistors, the layout of which is presented as figure \ref{fig:mesh}.}
+
+A numerical fit is then made to the two independent scaling parameters $R_{eri}$ and $R_{li}$
 \footnote{The values of $R_{eri}$ and $R_{sri}$ are defined by the lengths of the electrode and inter-electrode spacers respectively as described in \cite{ScottSingle2013}.
@@
 Hence, we define $R_{sri}$ to be 3/4 that of $R_{eri}$ making it a dependant parameter.}.
+The resulting fit and parameter values are presented in figure~\ref{fig:transresistance} and table~\ref{tab:RESparams}.
 
-The resulting fit and parameter values are presented in figure~\ref{fig:transresistance} and table~\ref{tab:RESparams} respectively.
-
-Measurements of the inter-electrode impedance were made using a Tektronix TPS2014 DSO with four fully isolated and floating channels; an Agilent 33220A Function Generator; and a desktop PC controlling the instruments via Python 2.7.
-
-The pH level of the stock solution was measured, using a calibrated EDT Instruments BA-350 pH meter, to have a pH of 7.4. No pH adjustments were made to the derived solutions.
+Measurements of the inter-electrode impedance are made using a Tektronix TPS2014 DSO with four fully isolated and floating channels; an Agilent 33220A Function Generator; and a desktop PC {\color{blue} running Python 2.7 for instrumentation control and result processing.} The pH level of the stock solution is measured using a calibrated EDT Instruments BA-350 pH meter.
+It has a pH of 7.4 and no pH adjustments were made to the derived solutions.
 
@@
     \color{blue}
-
-    In Table \ref{tab:RESparams}, $\sigma$ refers to the conductivity of the solution, measured in units of Siemens per centimeter.
-Solution conductivity was measured using an EDT instruments RE 388 TX Microprocessor Conductivity Meter.
-
-    It should be noted that the resistive mesh created in this step models only the resistivity of the solution bulk.
-This means that no resistive contribution from the electrode/electrolyte interface is included in these measurements as voltage measurements are always across pairs of non-driven electrodes.
-We determine the fixed resistance of a single interface, $R_{S}$, when fitting parameters to the displacement component.
+    To be clear, the resistive mesh created in this step models \textit{only} the resistivity of the solution bulk.
+No contribution from the interface itself appears in these measurements.
+The is because voltages are always measured across pairs of non-driven electrodes and the measurements are of suitably high impedance.
+We determine the resistive component of the interface, $R_{S}$, in the next section.
 }
@@
 \end{figure}
-
-% \begin{table}
-%     \caption{Measured conductivity of PBS solutions. {\color{red} Should I add this? The meter was uncalibrated}}
-%     \label{tab:PBSconductivity}
-%     \begin{center}
-%         \begin{tabular}{r | l}
-%             Concentration (X-PBS) & Conductivity ($\mu S/cm$)\\
-%             \hline
-%             1.0 & $15800$ \\
-%             0.5 & $4360$\\
-%             0.25 & $1860$\\
-%             0.05 & $931$\\
-%             0.025 & $492$\\
-%         \end{tabular}
-%     \end{center}
-% \end{table}
 
@@
 \label{sect:cpe}
-110 elements
 Displacement currents are responsible for capacitive behaviour at interfacial boundaries.
 They are brought about by the redistribution of charge in response to applied fields, i.e.
-a charged electrode will attract or repel $Cl^{-}$ from its surface and reorientate polar molecules in the surrounding solution.\cite{Merrill05} This capacitive behaviour may also be a result of electrode polarisation in the form of reversible Faradaic reactions at the surface of the electrode.
+a charged electrode will attract or repel $Cl^{-}$ from its surface and reorientate polar molecules in the surrounding solution.\cite{Merrill05} This capacitive behaviour may also be the result of electrode polarisation in the form of reversible Faradaic reactions at the surface of the electrode.
 Such reactions involving water and platinum, as identified in \cite{Horch2004,Mohtashami2011,Merrill05}, include:
@@
 
-This displacement mechanism is capable of transferring charge between electrical and biological systems without damaging electrodes or tissue.\cite{Horch2004}
-This behaviour is modelled by way of a Constant Phase Element (CPE); also known as a fractional capacitor.
+Displacement currents are capable of transferring charge between electrical and biological systems without damaging electrodes or tissue.\cite{Horch2004}
+This behaviour is modelled by way of a Constant Phase Element (CPE), also known as a fractional capacitor.
 For simulation purposes this element is realised as an array of R-C branches.~\cite{ScottSingle2013,Morrison59,Elwakil10} where the value of each R-C pair is chosen to set the slope of impedance relative to frequency.
 The placement of R-C pairs within the CPE is determined by Morrison's parameters $m$ and $k$, where $k$ determines the spacing, or density, of R-C branches and $m$ determines the resulting slope.
-{\color{blue} The R-C pairs were generated via Python script for to span 1\thinspace nHz--1\thinspace GHz with a spacing of 3 pairs per decade.
+{\color{blue} The R-C pairs were generated via Python script to span 1\thinspace nHz--1\thinspace GHz with a spacing of 3 pairs per decade.
 The final CPE contains 55 branches i.e.
@@
     \begin{center}
-        \includegraphics{graphics/chargeInjectionVsFrequency_magnitude}
+        \includegraphics{graphics/chargeInjectionEffectiveVsFrequency_magnitude}
     \end{center}
-    \caption{Charge injected per phase during CPE measurement for each of the six concentrations of PBS. Calculated using a geometric surface area of 10\thinspace mm$^{2}$}
+    \caption{\color{blue} Per phase charge injected during CPE measurement in each concentrations of PBS, calculated using an effective surface area of 14\thinspace mm$^{2}$.
+{\color{red} IS THIS CHEATING?
+(I have given the charged injected in terms of effective surface area instead of geometric)}}
     \label{fig:chargeInjectionVsFrequency}
@@
 
-The geometric current density during measurements peaked at 22.6\thinspace mA/cm$^{2}$ at 10000\thinspace kHz in 1.0X PBS and fell as low as 27.6\thinspace $\mu$A/cm$^{2}$ at 50\thinspace mHz in 0.025X PBS.
-Charge injection per phase is shown in figure~\ref{fig:chargeInjectionVsFrequency} for each solution.
+{
+    \color{blue}
+    Current density during measurements, calculated using an effective surface area of $14\thinspace mm^{2}$, peaked at $161\thinspace \mu A/cm^{2}$ at 10\thinspace kHz in 1.0X PBS and fell as low as $197\thinspace nA/cm^{2}$ at 50\thinspace mHz in 0.025X PBS.
+}Charge injection per phase is shown in figure~\ref{fig:chargeInjectionVsFrequency} for each solution.
 The stimulus waveform was set at 300\thinspace mV (peak) at each measurement point. The measurement instruments used are the same as those used to measure the inter-electrode resistance.
@@
 
-Our model uses two reverse connected diodes to represent Faradaic current conduction between electrode and electrolyte.
+Our model uses two reverse-connected diodes to represent Faradaic current conduction between electrode and electrolyte.
 Specifically we use the diodes to model irreversible Faradaic reactions.
 (Any reversible reactions, those producing reactants bound to the surface of the electrode, are encapsulated by the displacement branch (CPE) of the model.)
-Possible irreversible Faradaic reactions for platinum electrodes in saline are:
+Possible irreversible Faradaic reactions for platinum electrodes {\color{blue}(each with a different reaction potential)} in saline are:
 
@@
     \color{blue}
-    It should be noted that each of these reactions (\ref{eqn:ptCl}, \ref{eqn:H20}, \ref{eqn:2H20}, \ref{eqn:Cl} and \ref{eqn:ClH20}) have different reaction potentials.
-It is expected that the situation in-vivo will be much more complex.
+We use a diode to model the electrical current conduction caused by one reaction proceeding in one direction, i.e.
+a diode is the circuit representation of the Butler-Volmer equation for a single reaction proceeding in a single direction.
+    We wish to model the onset of Faradaic current as a way of knowing that an electrode has been pushed ``too far''.
+It is expected that the situation in-vivo will be much more complex and that fitted diode parameters may encapsulate multiple reactions if they occur close together.
 }
 
-The interface model uses the diodes to reproduce the exponential behaviour of Faradaic current conduction implied by the Butler-Volmer equation.
-We wish to measure this conduction by separating it from the displacement behaviour of the CPE.
+We measure Faradaic conduction by separating it from the displacement behaviour of the CPE.
 By using a DC measurement technique, as opposed to cyclic measurements, we are able to separate the effects in time.
@@
 The CPE will draw negligible current once it has settled and in the case of our model we assume the remaining current conduction to be the result of Faradaic processes.
-In \cite{Greatbatch1969} it is shown that the stirring of an air-saturated solution of physiological saline reduces the settling time of platinum electrodes to stimulus transients; with both situations eventually settling to the same impedance.
+
 The equation governing current conduction in a diode where the forward voltage across the diode, $V_{D}$, is small is
@@
 A single measurement run involved stepping the voltage across the electrodes from 0.5\thinspace V to 1.2\thinspace V in increments of 0.05\thinspace V; this range was previously determined to capture the onset of Faradaic conduction.
+
+In \cite{Greatbatch1969} it is shown that the stirring of an air-saturated solution of physiological saline reduces the settling time of platinum electrodes to stimulus transients; with both situations eventually settling to the same impedance.
 
@@
 
-%Parameter values for $i_{0}$ and $n$ are presented in table~\ref{tab:FaradaicParams}.
-These parameters were found by fitting the diode equation to the results shown in figure~\ref{fig:faradaic_currentVsVoltage}.
-
 We attribute the change in behaviour between 0.9\thinspace V and 1.05\thinspace V to a transition to diffusion-controlled conduction.
@@
     \begin{center}
-        \includegraphics{graphics/sheep_transimpedance_magnitude}
+        \includegraphics{graphics/sheep_transimpedance_doubleFit_mag}
     \end{center}
@@
     \begin{center}
-        \includegraphics{graphics/sheep_transimpedance_phase}
+        \includegraphics{graphics/sheep_transimpedance_doubleFit_phase}
     \end{center}
@@
 {\color{blue}
-    Four measurements of displacement current (CPE element in the model) were} taken at regular intervals over a period fo 30 minutes and have been presented in figures~\ref{fig:displacement_sheepCPEMagnitude} and~\ref{fig:displacement_sheepCPEPhase}.
+    Four measurements of displacement current (CPE element in the model) were} taken at regular intervals over a period of 30 minutes and have been presented in figures~\ref{fig:displacement_sheepCPEMagnitude} and~\ref{fig:displacement_sheepCPEPhase}.
 {\color{blue} These measurements appear on top of the traces taken from figures~\ref{fig:CPE_Magnitude} and~\ref{fig:CPE_Phase} for comparison.}
@@
     \end{center}
-    \caption{\color{blue} Comparison between the mean phase response of measured displacement currents in four live sheep (blue trace), each of the PBS traces taken from figure~\ref{fig:CPE_Phase} (grey lines), and a simulated fit to the sheep data (red trace).
-Error bars have been placed one standard deviation either side of the mean for measured data.}
+    \caption{{\color{blue} Comparison between the mean phase response of measured displacement currents in four live sheep (blue trace), each of the PBS traces taken from figure~\ref{fig:CPE_Phase} (grey lines), and a simulated fit to the sheep data (red trace).
+Error bars have been placed one standard deviation either side of the mean for measured data.}}
     \label{fig:displacement_sheepCPEPhase}
@@
 We found that the magnitude of the CPE element moves much more slowly with concentration whereas the resistance moved almost linearly.
-Using DC measurements we conclude that the {\color{blue} concentration of PBS has no effect on the onset of Faradaic conduction for the range of concentrations investigated.} {\color{Green} \sout{salinity of the bulk does not affect Faradaic conduction until a threshold voltage is reached}}.
-We hypothesise that this is because the double-layer sets the effective concentration of ions {\color{blue}, those involved in the Faradaic reactions,} in a localised volume surrounding each electrode.
+Using DC measurements we conclude that the {\color{blue} concentration of PBS has no effect on the onset of Faradaic conduction for the range of concentrations investigated.} We hypothesise that this is because the double-layer sets the effective concentration of ions{\color{blue}, those involved in the Faradaic reactions,} in a localised volume surrounding each electrode.
 In-vivo measurements of platinum electrodes in sheep spine show that no single concentration of PBS matches both the CPE and the resistive characteristics at once.
-{\color{blue} These measurements also reveal a considerable amount of reactance (see transimpedance measurements in-vivo) that is captured neither by PBS nor the model presented when using a purely resistive spreading resistance mesh.} Nevertheless, {\color{blue}if a single solution of PBS is to be used as a human phantom, a one-tenth concentration solution (by mass)} is a good compromise.
+{\color{blue} These measurements also reveal a considerable amount of reactance (see transimpedance measurements in-vivo) that is captured neither by PBS nor the model presented when using a purely resistive spreading resistance.} Nevertheless, {\color{blue}if a single solution of PBS is to be used as a human phantom, a one-tenth concentration solution (by mass)} is a good compromise.
 
@@
     \color{blue}
-    The model is limited to predicting only the onset of Faradaic current conduction, i.e.
-it does not model operation in a diffussion limited scenario as it omits the memristors of \cite{ScottSingle2013}.
+    While the model used is limited to predicting only the onset of Faradaic current conduction, it usefully captures the transition into this biologically destructive stimulus regime sufficient for it to be avoided.
+
+    The final model, including 205 lines of resistive mesh, is represented by a SPICE netlist comprised of 348 lines.
+Simulation of this model, using the freely available ngSpice circuit simulator, at 1000 frequencies between spaced between 50\thinspace mHz to 10\thinspace kHz takes approximately 1 second on a modern CPU.
+}
+{
+    \color{red}
+    How is this last line? It's new information in the conclusion...
 }
@@
 The authors wish to acknowledge the The University of Waikato for financial support and Saluda Medical for the use of facilities and equipment.
-Thanks are extended to Peter Single for help conducting in-vivo measurements.
+{\color{red}Special thanks are expressed to Peter Single of Saluda Medical for help conducting in-vivo measurements.}
 
@@
 \bibitem{ScottSingle2013}
-{\color{red} HAS THIS BEEN PUBLISHED YET?}
     Jonathan Scott and Peter Single,
@@
 We observe that the current increases near exponentially around this point so we use a diode to mimic that.
-We expect this reaction may not be the same in-vivo as it is in-vivo but the properties of a diode can be altered to match where this occurs.
+We expect this reaction may not be the same in-vivo as it is in-vivo but the properties of a diode can be altered to match the situation.
 
-        If there are secondary reactions occurring at higher potentials then we could add a second pair of diodes with the properties of that specific reaction.
-The problem here is that we would then need to include memristors (as used in ScottSingle2013) to account for reactant depletion.
-We don't account for reactant depletion for the same reason we don't account for reactions other than the very first Faradaic reaction to occur.
+        For secondary reactions occurring at higher potentials, a second pair of diodes with the properties of that specific reaction can be added.
+The problem here is that memristors will be needed (as used in ScottSingle2013) to account for reactant depletion.
+We don't account for reactant depletion for the same reason we don't account for reactions other than the onset of the first Faradaic reaction(s) taking place.
 The reason is that we never want biologically damaging reactions to occur due to an implant, so if they happen then something has gone wrong.
 
-        Think of our attempt to model Faradaic reactions as a ``you've pushed this too far'' indicator for an electrical engineer.
+        Think of our model of Faradaic reactions as a ``you've pushed this too far'' indicator for an electrical engineer.
 
-        I think you're essentially right with you're argument, we're not up-front about this and we probably portray more capability in the Faradaic modelling aspect than we are able or aim to achieve.
+        We have added a statement to address this concern directly after equations 5--9 in section \ref{sect:faradaic}.
     }
@@
         \color{blue}
-        Correct, we do not wish to determine exactly what is happening at the electrode surface - we want to create a flexible model that can be used to simulate impedance.
+        That is correct, we are not aiming to determine what is happening at the electrode surface.
+We have a flexible model that can be used to simulate interfacial impedance and we use this model to compare this impedance for electrodes in various electrolytes.
+If the solution changes, the reactions change.
+Since we are only interested in the onset of Faradaic conduction, and we expect this to change when we move to different solutions, we do not want to rely on the exact electrochemistry at play.
 
@@
         This is a good point.
-ScottSingle2013 compare the model prediction to stimulus waveforms.
-Our aim is to see what changes in that model as the concentration of PBS is varied and to compare those measurements to in-vivo measurements using a live sheep.
+ScottSingle2013 compare the models prediction to stimulus waveforms.
+Our aim is to capture how the model parameters change as the concentration of PBS is varied and to compare those changes to parameters obtained from in-vivo measurements using a live sheep.
 Were doing this because 0.1X PBS is commonly used as a phantom for real spine.
-There hasn't been an objective way of determining how accurate that assumption was until we used this model to make that comparison.
+There hasn't been an objective way of determining how accurate that assumption was until we used the model to make this comparison.
+In future we hope to match it against in-vivo stimulus waveforms; at present it is out of scrope.
     }
@@
 3.
-The transimpedance measurements do not measure impedance across an interface that is passing current and therefore any voltage drop across an interface due to $R_{S}$ would vanish.
+The transimpedance measurements do not measure impedance across an interface that is passing current and therefore any voltage drop across an interface due to $R_{S}$ vanishes.
 The displacement measurements take the voltage across interfaces that are passing stimulus currents.
-These measurements see the potential drop across the interface due to the current flow via Ohms law.
+These measurements see the potential drop across the interface due to the current flow (because of Ohms law).
 
@@
     {
+        \color{blue}
+        That is interesting and definitely important to our modelling work.
+We had presented the charge injected in terms of the geometric surface area of each electrode which we know is less than the real (or effective) surface area, estimated to be $14\thinspace mm^{2}$.
+Calculating the charge injection using the effective surface area is more relevant here and gives results consistant with Brummer \& Roblee (Annals New York Academy of Sciences, 159-171, 1983), who also express their values in terms of ``real'' area.
+
+    }
+    {
         \color{red}
-        What should I say to this?.
-We measured what we measured, no visible gas evolution.
-The results look consistant.
-We are happy to accept that we may have pushed the electrodes too far in the solution at low frequencies, regardless of this fact we have data here and wish to present it.
+        How does this read now? In your last comment you said...
+
+        We have to acknowledge that this is anomalous.
+We were stirring, but definitely observed no gas.
+Say just as you say, the results are consistent with it NOT being a problem, although other researchers have observed otherwise.
+We seem to be saying that they are wrong, so we should say just that, we observe something different, yet results are clearly consistent and explicable!
     }
@@
         The RC pairs are generated via a Python script for a given frequency range.
-Simulations in this manuscript used RC pairs spanning 1.0 nHz to 1.0 GHz spaced 3 per decade.
-Adding more RC pairs than necessary came at negligible computation cost and having the circuited constructed in an automated fashion to satisfy the given frequency range adds no extra work.
+The frequency range supplied for all simulations in this manuscript was 1.0 nHz to 1.0 GHz with R-C pairs spaced 3 per decade.
+Adding more pairs than necessary came at negligible computation cost and having the circuit generated in an automated fashion adds no extra work.
+        {
+            \color{red}
+            We would also like to note that the effect of the CPE is far from that of a simple capacitor, i.e.
+far from being exponential.
+This is part of the reason they are so difficult to simulate in a compact circuit simulator.
+        }
     }
@@
     {
+        \color{blue}
+        Yes you are quite right.
+We think the results of the CPE in-vivo vs.
+PBS are intriguing in light of what the previous literature would have you expect.
+We also know of no satisfactory explanation of what the CPE actually is.
+One of the authors came up against this uncertainty while writing \cite{ScottSingle2013}.
+
+        We feel that the in-vivo results will be affected by the significant inhomogeneity of real spine by proximity of bone, change in fluid at dura, etc.
+Perhaps you may know of a way to clarify this issue?
+    }
+
+    {
        \color{red}
-       HELP, how do I approach this?
+       Is this what you were after? 
     }
@@
         \color{blue}
-
+        The 0.9V limitation is rather arbitrary as it was specific to the use of electrodes 2 and 7.
+We have instead clarified that the model only captures the onset of Faradaic conduction sufficient for it to be avoided.
+A sentence to this effect have been added to the end of the conclusion.
     }

### 2014-04-17 paper.tex
Ready for submission

@@
     \color{blue}
-    We measure this response in various solutions with an electrode array as is commonly used with spinal cord stimulation (SCS) implants.
-We match the parameters of a compact non-linear electrode/electrolyte interface model to measured responses at various concentrations of PBS.
+    We measure the response in various dilutions of PBS with an electrode array as is commonly used in spinal cord stimulator (SCS) implants.
+We match the parameters of a non-linear electrode-electrolyte interface model to these measurements.
 }
 We find that the constant phase element of the model scales with approximately the log of concentration, whereas the resistivity is inversely proportional.
-Using a novel DC measurement technique we show that the Faradaic response of a platinum electrode, and thus the safe exposure limit, does not scale with concentration below 900\thinspace mV overpotential across a pair of electrodes.
+Using a novel DC measurement technique we show that the {\color{blue} onset of Faradaic conduction for} a platinum electrode, and thus the safe exposure limit, does not scale with concentration.
 We compare objective measurements made in saline to those made in the spinal cavity of live sheep. We comment upon the appropriateness of using PBS as a substitute for in-vivo measurements.
@@
 \begin{IEEEkeywords}
-    Electrical stimulation, Bioelectric phenomena, Biophysics, Bioimpedance, Biomedical electrodes, Biomedical measurements, Implantable biomedical devices
+    Bioelectric phenomena, Bioimpedance, Biomedical electrodes, Biomedical measurements, Biophysics, Electrical stimulation, Implantable biomedical devices
 \end{IEEEkeywords}
@@
 Another appeal of a compact model stems from the fact that electrode characteristics are succinctly and objectively represented by the model parameters.
-These enable direct comparison of different electrodes, or the change in electrode properties over time.
+These parameters enable direct comparison of different electrodes, or the change in electrode properties over time.
 For example, in \cite{Kane13} changes in chronically-implanted electrodes are observed but there is no standard quantitative way of presenting the changes.
@@
 In an implanted setting there is no reference electrode and many of the well established electrochemical measurement regimes do not apply.
-Here we measure the behaviour an electrode/electrolyte situation as it would be seen from an implant device.
+Here we measure the behaviour in an electrode-electrolyte situation as it would be seen from an implant device.
 
-The electrode used in this work is a commercial linear array of eight platinum electrodes intended for SCS implantation called an ``Octrode''.~\cite{StJudeOctrode} A picture of an Octrode is presented in figure~\ref{fig:octrode}.
-A solution of Phosphate Buffered Saline (PBS) diluted to one-tenth concentration (0.1X) is common in the case of Spinal Cord Stimulators (SCS), while full concentration (1.0X) PBS is considered more representative of the situation in blood.
+The electrode used in this work is a commercial linear array of eight platinum electrodes, called an ``Octrode'', intended for Spinal Cord Stimulator (SCS) implantation.~\cite{StJudeOctrode} A picture of an Octrode is presented in figure~\ref{fig:octrode}.
+A solution of phosphate buffered saline (PBS) diluted to one-tenth concentration (0.1X) is commonly {\color{blue}used as a crude phantom} in the case of SCS, while full concentration (1.0X) PBS is considered more representative of the situation in blood.
 
-% {
-%     \color{red}
-% In this manuscript we report how the parameters of a non-linear model change as the concentration of saline is varied.
-We refine a series of measurements compatible with commercially available medical electrodes in physiological saline that allow us to describe the impedance with minimal parameters.
-We place these parameters in context with a biological measurement made in the spinal cavity of a live sheep.
-
-%     THIS IS IN THE ABSTRACT
-% }
-
-Six solutions ranging from 1.0X to 0.025X the concentration of a stock PBS solution (by mass) have been examined.
-The ingredients of that stock solution are given in table~\ref{tab:PBSrecipe}.
+Six solutions ranging from 1.0X to 0.025X the concentration (by mass) of a stock PBS solution have been examined.
+The ingredients of that stock solution are given in Table~\ref{tab:PBSrecipe}.
 
@@
         \caption{Electrical schematic of the electrode-interface impedance model used in this work.
-$D_{a}$ and $D_{b}$ represent diodes; $CPE$ and $R_{s}$ represent the constant phase element and series resistance respectively.}
+$D_{a}$ and $D_{b}$ represent diodes; CPE and $R_{s}$ represent the constant phase element and series resistance respectively.}
         \label{fig:schematic}
@@
     In this manuscript we use an adapted version of the compact non-linear model presented in \cite{ScottSingle2013}.
-The model is compact in that it is suitable for entering into SPICE, i.e., freely available electrical circuit simulation software.
-The schematic for the model used here is presented in Figure \ref{fig:schematic}.
+The model is compact in that it is suitable for {\color{blue} entering into freely available electrical circuit simulation software}.
+The schematic for the {\color{blue} electrode-electrolyte interface} model used is presented as Figure \ref{fig:schematic}.
 }
@@
 It has been suggested that the primary coupling mechanism between platinum electrodes and physiological saline is the reversible evolution of gas, probably oxygen, at the platinum surface, which dissolves without bubble formation.\cite{Greatbatch1969} Understanding the exact mechanism of displacement or Faradaic charge transfer at the electrode surface is beyond the scope of this work.
-Rather, we wish to characterise the electrode/electrolyte system in terms of a {\color{blue} small number of} parameters that may be fed into an electrical model.
+Rather, we wish to characterise the {electrode-electrolyte interface \color{blue} using a small} {\color{blue} number of} parameters that can be fed into an electrical model.
 
@@
     The remainder of this manuscript is broken into five sections.
-Section \ref{sect:resistorMesh} details the measurement of the inter-electrode resistances and the generation of a resistor network to replicate these resistances.
+Section \ref{sect:resistorMesh} details the measurement of the inter-electrode resistances {\color{blue}(arising from the bulk resistance of the solution)} and the generation of a resistor network to replicate these resistances.
     Sections \ref{sect:cpe} and \ref{sect:faradaic} are concerned with the measurement and parameter fitting of displacement currents and Faradaic currents, respectively, across the electrolyte interface.
-Section \ref{sect:in-vivo} compares the results obtained in PBS with measurements in-vivo.
+Section \ref{sect:in-vivo} compares the results obtained {\color{blue}for} PBS with measurements {\color{blue} made} in-vivo.
 Finally, in Section \ref{sect:conclusion} we summarise our findings and give concluding comments.
@@
 To quantify the impedance presented by a single interface we first need to determine inter-electrode resistance presented by the electrolyte bulk.
-{\color{blue} Finding these resistances allows us to quantify the interface's impedance via subtraction.} As there are always two interface impedances between any two electrodes, inter-electrode resistances cannot be measured in isolation.
+{\color{blue} Finding these resistances allows us to quantify the {\color{blue}series resistance of the interface ($R_{S}$)} via subtraction.} As there are always two interface impedances between any two electrodes, inter-electrode resistances cannot be measured in isolation.
 
 In \cite{ScottSingle2013}, a series of transresistance measurements were used in conjunction with a physical description of the electrode geometry to build up a representative network of resistors.
-That resistor network was defined using five parameters: $R_{eri}$, $R_{lri}$, $R_{li}$, mesh depth, and edge depth.
+That resistor network was defined using five parameters: $R_{eri}$, $R_{sri}$, $R_{li}$, mesh depth, and edge depth.
 Readers are referred to \cite{ScottSingle2013} for the interpretation of these model parameters.
-Repeating that work, we have created a network of resistors that mimic the resistances due to the solution's bulk conductivity.
+Repeating that work, we created a network of resistors that mimic the resistances due to the solution's bulk conductivity.
 
 The mesh depth and padding values of five columns and three rows, respectively, has been taken directly from \cite{ScottSingle2013}.
-{\color{blue} These parameters, together with an array of 8 electrodes, leads to a generated network of 205 resistors, the layout of which is presented as figure \ref{fig:mesh}.}
+{\color{blue} These parameters, together with an array of 8 electrodes, leads to a generated network of 205 resistors, the layout of which is presented in figure \ref{fig:mesh}.}
 
-A numerical fit is then made to the two independent scaling parameters $R_{eri}$ and $R_{li}$
-\footnote{The values of $R_{eri}$ and $R_{sri}$ are defined by the lengths of the electrode and inter-electrode spacers respectively as described in \cite{ScottSingle2013}.
+A numerical fit {\color{blue} has been} made to the two independent scaling parameters $R_{eri}$ and $R_{li}$\footnote{The values of $R_{eri}$ and $R_{sri}$ are defined by the lengths of the electrode and inter-electrode spacers respectively as described in \cite{ScottSingle2013}.
 The two parameters are proportional to each other by the ratio of their lengths.
 Hence, we define $R_{sri}$ to be 3/4 that of $R_{eri}$ making it a dependant parameter.}.
-The resulting fit and parameter values are presented in figure~\ref{fig:transresistance} and table~\ref{tab:RESparams}.
+The resulting fit and parameter values are presented in figure~\ref{fig:transresistance} and Table~\ref{tab:RESparams}.
 
-Measurements of the inter-electrode impedance are made using a Tektronix TPS2014 DSO with four fully isolated and floating channels; an Agilent 33220A Function Generator; and a desktop PC {\color{blue} running Python 2.7 for instrumentation control and result processing.} The pH level of the stock solution is measured using a calibrated EDT Instruments BA-350 pH meter.
-It has a pH of 7.4 and no pH adjustments were made to the derived solutions.
+Measurements of the inter-electrode impedance {\color{blue} were made using} a Tektronix TPS2014 DSO with four fully isolated and floating channels; an Agilent 33220A Function Generator; and a desktop PC {\color{blue} running Python 2.7 for instrumentation control and result processing.} The pH level of the stock solution was measured using a calibrated EDT Instruments BA-350 pH meter.
+It had a pH of 7.4 and no pH adjustments were made to the derived solutions.
+{\color{blue} The conductivity of solutions was measured using an EDT Instruments RE 388 Tx conductivity meter.}
 
@@
 No contribution from the interface itself appears in these measurements.
-The is because voltages are always measured across pairs of non-driven electrodes and the measurements are of suitably high impedance.
-We determine the resistive component of the interface, $R_{S}$, in the next section.
+{\color{blue} This measurement is possible} because voltages are always measured across pairs of non-driven electrodes and the measurements are of suitably high impedance.
+We determine the resistive component of the interface, $R_{S}$, in the {\color{blue} following} section.
 }
@@
 Displacement currents are responsible for capacitive behaviour at interfacial boundaries.
-They are brought about by the redistribution of charge in response to applied fields, i.e.
-a charged electrode will attract or repel $Cl^{-}$ from its surface and reorientate polar molecules in the surrounding solution.\cite{Merrill05} This capacitive behaviour may also be the result of electrode polarisation in the form of reversible Faradaic reactions at the surface of the electrode.
+They are brought about by the redistribution of charge in response to applied fields, {\color{blue}e.g.,} a charged electrode will attract or repel $Cl^{-}$ from its surface and reorientate polar molecules in the surrounding solution.\cite{Merrill05} This capacitive behaviour may also be the result of electrode polarisation in the form of reversible Faradaic reactions at the surface of the electrode.
 Such reactions involving water and platinum, as identified in \cite{Horch2004,Mohtashami2011,Merrill05}, include:
@@
 Displacement currents are capable of transferring charge between electrical and biological systems without damaging electrodes or tissue.\cite{Horch2004}
-This behaviour is modelled by way of a Constant Phase Element (CPE), also known as a fractional capacitor.
-For simulation purposes this element is realised as an array of R-C branches.~\cite{ScottSingle2013,Morrison59,Elwakil10} where the value of each R-C pair is chosen to set the slope of impedance relative to frequency.
+This behaviour is modelled by way of a constant phase element (CPE), also known as a fractional capacitor.
+For simulation purposes this element is realised as an array of R-C branches~\cite{ScottSingle2013,Morrison59,Elwakil10} where the value of each R-C pair is chosen to set the slope of impedance relative to frequency.
 The placement of R-C pairs within the CPE is determined by Morrison's parameters $m$ and $k$, where $k$ determines the spacing, or density, of R-C branches and $m$ determines the resulting slope.
-{\color{blue} The R-C pairs were generated via Python script to span 1\thinspace nHz--1\thinspace GHz with a spacing of 3 pairs per decade.
-The final CPE contains 55 branches i.e.
-110 elements are used to create the CPE model.}
+{\color{blue} R-C pairs were generated using a Python script to span 1\thinspace nHz --1\thinspace GHz with a spacing of 3 pairs per decade.
+The CPE contains 55 branches i.e.
+110 {\color{blue}electrical} elements are used to represent the CPE.}
 
-We measure displacement currents by sweeping the frequency of a sinusoidal stimulus across electrodes 2 and 7 of the Octrode while measuring the voltage between electrodes 2 and 3 (numbering shown in Fig.~\ref{fig:octrode}).
+We measure displacement currents by sweeping the frequency of a sinusoidal stimulus across electrodes 2 and 7 of the Octrode while measuring the voltage between electrodes 2 and 3 (numbering shown in figure~\ref{fig:octrode}).
 This allows for the measurement of a single interface impedance in series with the resistance presented by the bulk solution.
+
+{
+    \color{blue}
+    Current density during measurements, calculated using an effective surface area of $14\thinspace mm^{2}$, peaked at $161\thinspace \mu A/cm^{2}$ at 10\thinspace kHz in 1.0X PBS and fell as low as $197\thinspace nA/cm^{2}$ at 50\thinspace mHz in 0.025X PBS.
+}Charge injection per phase is shown in figure~\ref{fig:chargeInjectionVsFrequency} for each solution.
+The stimulus waveform was set at 300\thinspace mV (peak) at each measurement point.
+The measurement instruments used are the same as those used to measure the inter-electrode resistance in the previous section.
 
@@
     \end{center}
-    \caption{\color{blue} Per phase charge injected during CPE measurement in each concentrations of PBS, calculated using an effective surface area of 14\thinspace mm$^{2}$.
-{\color{red} IS THIS CHEATING?
-(I have given the charged injected in terms of effective surface area instead of geometric)}}
+    \caption{\color{blue} Per phase charge injected during CPE measurement in each concentrations of PBS{\color{blue}, calculated with an effective surface area of 14\thinspace mm$^{2}$.}}
     \label{fig:chargeInjectionVsFrequency}
@@
 
-{
-    \color{blue}
-    Current density during measurements, calculated using an effective surface area of $14\thinspace mm^{2}$, peaked at $161\thinspace \mu A/cm^{2}$ at 10\thinspace kHz in 1.0X PBS and fell as low as $197\thinspace nA/cm^{2}$ at 50\thinspace mHz in 0.025X PBS.
-}Charge injection per phase is shown in figure~\ref{fig:chargeInjectionVsFrequency} for each solution.
-The stimulus waveform was set at 300\thinspace mV (peak) at each measurement point. The measurement instruments used are the same as those used to measure the inter-electrode resistance.
-Figure~\ref{fig:CPE_Magnitude} shows the magnitude of the measured response of each of the six PBS concentrations accompanied by simulation results.
+Figure~\ref{fig:CPE_Magnitude} shows the magnitude of the measured response {\color{blue}for each concentration of PBS} accompanied by simulation results.
 Figure~\ref{fig:CPE_Phase} shows the phase response for the same measurements, again with the simulated response at each concentration.
-The simulated responses are generated using the optimised parameter values presented in Table~\ref{tab:CPEparams}.
-Those values were chosen as they give the closest match to the measured data.
+The simulated responses are generated using fitted parameter values for {\color{blue} $m$, $k$, $|Z|\thinspace @\thinspace 1Hz$, and $R_S$, which are} presented in Table~\ref{tab:CPEparams}.
 
@@
 Figure~\ref{fig:CPE_Scaling} shows measured data and the corresponding fits for both the CPE magnitude at 0.05\thinspace Hz and $R_{S+bulk}$.
-The model parameters $m$, $k$, $|Z|\thinspace @\thinspace 1Hz$, and $R_S$ are shown in table~\ref{tab:CPEparams}, with $|Z|\thinspace @\thinspace 1Hz$, and $R_S$ given as functions of concentration.
 Here we express the CPE offset parameter as $|Z|\thinspace @ \thinspace 1Hz$, but the fits used $|Z|\thinspace @ \thinspace 0.05Hz$, as data points at this frequency are outside the transitional zone where the impedance of the CPE and that of $R_{S+bulk}$ overlap.
 
-The data presented in Fig.~\ref{fig:CPE_Magnitude} show a large, linear, relative shift of $|Z|$ with salinity at higher frequencies, where the resistive component of the solution dominates.
-Conversely, at lower frequencies where the $|Z|$ changes with frequency, the relative change is closer to logarithmic. This region is modeled by the CPE.
+The data presented in figure~\ref{fig:CPE_Magnitude} shows a large, linear, relative shift of $|Z|$ with salinity at higher frequencies, where the resistive component of the solution dominates.
+Conversely, at lower frequencies where $|Z|$ changes with frequency, the relative change is closer to being logarithmic. It is this region that is modelled by the CPE.
 This suggests that the CPE does not chiefly rely on the added salt ions, but they do have some effect.
-Instead, the constant-phase charge effect must arise from phenomena not associated with the salt ions.
+Instead, the constant-phase effect must arise from phenomena not associated with the salt ions.
 
@@
     \end{center}
-    \caption{Simulated and measured values of CPE parameters versus concentration of PBS. $|Z|$ is compared at 0.05\thinspace Hz as measured data is unaffected by $R_{S}$ at this frequency.}
+    \caption{Simulated and measured values of CPE parameters versus concentration of PBS. $|Z|$ is compared at 0.05\thinspace Hz as measured data is unaffected by $R_{S+bulk}$ at this frequency.}
     \label{fig:CPE_Scaling}
@@
 \begin{table}
-    \caption{Displacement parameter scaling. $conc.$ refers to the mass concentration of PBS.}
+    \caption{Displacement parameter scaling.\hspace{\textwidth}$conc$ refers to the mass concentration of PBS.}
     \label{tab:CPEparams}
@@
 Our model uses two reverse-connected diodes to represent Faradaic current conduction between electrode and electrolyte.
-Specifically we use the diodes to model irreversible Faradaic reactions.
-(Any reversible reactions, those producing reactants bound to the surface of the electrode, are encapsulated by the displacement branch (CPE) of the model.)
-Possible irreversible Faradaic reactions for platinum electrodes {\color{blue}(each with a different reaction potential)} in saline are:
+Specifically, we use the diodes to model irreversible Faradaic reactions.
+(Any reversible reactions, those producing reactants bound to the surface of the electrode, are encapsulated by the displacement branch of the model.)
+Possible irreversible Faradaic reactions for platinum electrodes {\color{blue}(each with differing reaction potentials)} in saline are:
 
@@
 
-We measure Faradaic conduction by separating it from the displacement behaviour of the CPE.
-By using a DC measurement technique, as opposed to cyclic measurements, we are able to separate the effects in time.
-Like a conventional capacitor, when the voltage across the CPE changes, it responds by absorbing or ejecting charge, causing a spike in current.
+{\color{blue} To measure Faradaic conduction we must separate its contribution from any displacement behaviour.} By using a DC measurement technique, as opposed to cyclic measurements, we are able to separate the effects in time.
+Like a conventional capacitor, the CPE responds {\color{blue} to a change in voltage by absorbing or ejecting charge, causing a spike in current}.
 The CPE will draw negligible current once it has settled and in the case of our model we assume the remaining current conduction to be the result of Faradaic processes.
@@
 
-Measurements commenced with a 4.5 litre solution of 1.0X PBS which was progressively diluted in factors of two between each measurement.
+Measurements commenced with a 4.5 litre solution of 1.0X PBS which was progressively diluted in factors of two between measurements.
 The solution was mixed continuously using a standard laboratory grade magnetic stirrer.
@@
 At overpotential steps for higher voltages, the settling time is further reduced.
-These measurements were made in still solution and we expect stirring will further reduce settling time.} we concluded that a wait-time of 64 seconds was sufficient.
+These measurements were made in still solution and we expect stirring will further reduce settling time.} we concluded that a wait-time of 64 seconds is sufficient.
 
@@
 
-In figure~\ref{fig:StepResponse_Faradaic}, electrical current measurements are plotted against time (solid lines).
+In figure~\ref{fig:StepResponse_Faradaic}, electrical current measurements (solid lines) are plotted against time.
 Each spike marks the point at which the voltage is incremented by 50\thinspace mV.
@@
 Dotted lines have been added that link the electrical current measurements taken 10 seconds after each increment for 0.125X PBS (lower trace) and 1.0X PBS (upper trace).
-These dotted traces show results typical of cyclic methods, where the electrode overpotential is never constant.
+These dotted traces show results typical of cyclic {\color{blue} measurement} methods, where the electrode overpotential is never constant.
 This illustrates the benefit of using DC measurements when measuring Faradaic currents.
 
-Figure~\ref{fig:faradaic_logCurrentVsVoltage} shows the settled currents plotted on a log scale, versus the voltage applied across the electrodes.
+Figure~\ref{fig:faradaic_logCurrentVsVoltage} shows the settled currents plotted on a log scale, versus the voltage applied across the electrode {\color{blue} pair}.
 This uses the same data as the previous figure but has been processed so that each point represents the average of the final 24 current measurements at each step.
@@
 The point at which this transition occurs is determined by the concentration of saline, with lower concentrations transitioning earlier.
-A concentration of 0.0625X PBS causes a transition at around 0.95\thinspace V whereas electrodes in the 1.0X PBS solution transition somewhere between 1.0\thinspace and 1.05\thinspace V.
+A concentration of 0.0625X PBS causes a transition at around 0.95\thinspace V whereas electrodes in the 1.0X PBS solution transition somewhere between 1.0\thinspace V and 1.05\thinspace V.
 The effect of transition can be seen in the green trace at 1.0\thinspace V where the error bar is wide due to the current shift being captured in the measurement at that voltage.
@@
 For the purposes of our model, we are content with placing a limit of 0.9\thinspace V across the pair of interfaces and using the assumption that Faradaic conduction does not change with concentration.
+{\color{blue} As we are primarily interested with capturing only the onset of Faradaic conduction, this limitation does not degrade the usefulness of the model for implant modelling purposes.}
 
-    Figure~\ref{fig:faradaic_currentVsTime} shows a subset of the data used in Fig.~\ref{fig:StepResponse_Faradaic} (the 1.0X PBS trace) to show the fit between simulated and measured data in the time domain.
-Here the simulation contains fitted diode parameters, shown in table~\ref{tab:FaradaicParams}, which give rise to the exponentially increasing steady state current.
+    Figure~\ref{fig:faradaic_currentVsTime} shows a subset of the data used in figure~\ref{fig:StepResponse_Faradaic} (the 1.0X PBS trace) to show the fit between simulated and measured data in the time domain.
+Here the simulation contains fitted diode parameters, shown in Table~\ref{tab:FaradaicParams}, which give rise to the exponentially increasing steady state current.
 It is apparent from this trace that the temporal response of the CPE does not match the transient decay curves seen in the Faradaic measurements, something the CPE should predict.
 These transient decay curves appear to have a time-constant\footnote{We use the term ``time-constant'' although a CPE does not have a simple exponential time-domain response.} that decreases with each subsequent measurement.
-This variable time-constant phenomena is especially clear when looking back at figure~\ref{fig:CPE_currentVsTime}.
+This variable time-constant phenomena is especially clear when looking at figure~\ref{fig:CPE_currentVsTime}.
 Although the Faradaic response transients appear to approach the time-constant predicted by the CPE, there is still behaviour not completely described by the CPE.
@@
 Cogan states the main differences between in-vivo and in-vitro responses come down to temperature, the presence of organic species, tortuous diffusion path for charge carriers, physiological responses of the host to a foreign body, and uncertain concentrations of electrolytes and buffers near the electrode surface.\cite{Cogan2008}
-Nevertheless, electrical engineers use baths of saline as a substitute for in-vivo testing (a ``phantom'') due to its convienience.
+Nevertheless, electrical engineers use baths of saline as a substitute for in-vivo testing (a ``phantom'') due to its convenience.
 We now test the claim that 0.1X PBS is a reasonable representation of the spine of a living sheep.
@@
     \color{blue}
-    Transimpedance measurements in-vivo were done using additional configurations than were carried out in section \ref{sect:resistorNetwork}.
-The same measurements were captured but a more complete stimulus--measure regieme was tried in order to minimise the effect of nearby bone having too large an effect on a small number of measurements.
-Time constraints with the live animal meant only one dataset was obtained for transimpedance, shown in figures~\ref{fig:displacement_sheepCPEMagnitude} and \ref{fig:displacement_sheepCPEPhase} along with results obtained via simulation using fitted parameters.
+    Transimpedance measurements in-vivo were {\color{blue} conducted with} additional configurations than were carried out in Section \ref{sect:resistorMesh}.
+The same measurements were captured {\color{blue} except this time using} a more complete stimulus--measure regime in order to minimise the effect of nearby bone.
+Time constraints with the live animal meant only {\color{blue} a single} dataset was obtained for transimpedance.
+{\color{blue} This data is} shown in figures~\ref{fig:displacement_sheepCPEMagnitude} and \ref{fig:displacement_sheepCPEPhase} along with results obtained {\color{blue} from} simulation {\color{blue} with} fitted parameters.
 }
+{\color{blue} In these measurements a phase deviation of approximately 30 degrees is observed, visible in figure~\ref{fig:transimpedance_sheep_phase}.
+There was no measurable phase deviation for these measurements in PBS.
+These results indicate that the sheep itself presents a significant reactive component.}
 
 {\color{blue}
-    Four measurements of displacement current (CPE element in the model) were} taken at regular intervals over a period of 30 minutes and have been presented in figures~\ref{fig:displacement_sheepCPEMagnitude} and~\ref{fig:displacement_sheepCPEPhase}.
+    Four measurements of displacement currents (CPE element in the model) were} taken at regular intervals over a period of 30 minutes and have been presented in figures~\ref{fig:displacement_sheepCPEMagnitude} and~\ref{fig:displacement_sheepCPEPhase}.
 {\color{blue} These measurements appear on top of the traces taken from figures~\ref{fig:CPE_Magnitude} and~\ref{fig:CPE_Phase} for comparison.}
 
-Although it is clear that there are complications in vivo, a 0.25X PBS saline offers a good approximation to the resistive part of the trace.
-The reactive part would be better modelled by a solution of less than 0.025X concentration.
+Although it is clear that there are complications in vivo, a 0.25X PBS {\color{blue} solution} offers a good approximation to the resistive part of the  trace.
+The reactive part {\color{blue} (that of the CPE)} would be better modelled by a solution of less than 0.025X concentration.
 
+{
+    \color{blue}
+    Faradaic measurements on the live animal were abandoned as they were likely to cause potentially violent muscle contraction.
+Attempts to measure the response at low stimulus potentials yielded unsatisfactory results and were subsequently discarded.
+}
 \begin{figure}
@@
     \end{center}
-    \caption{{\color{blue} Comparison between the mean phase response of measured displacement currents in four live sheep (blue trace), each of the PBS traces taken from figure~\ref{fig:CPE_Phase} (grey lines), and a simulated fit to the sheep data (red trace).
+    \caption{{\color{blue} Comparison of the mean phase response of measured displacement currents in live sheep (blue trace), each of the PBS traces taken from figure~\ref{fig:CPE_Phase} (grey lines), and a simulated fit to the sheep data (red trace).
 Error bars have been placed one standard deviation either side of the mean for measured data.}}
@@
 We found that the magnitude of the CPE element moves much more slowly with concentration whereas the resistance moved almost linearly.
-Using DC measurements we conclude that the {\color{blue} concentration of PBS has no effect on the onset of Faradaic conduction for the range of concentrations investigated.} We hypothesise that this is because the double-layer sets the effective concentration of ions{\color{blue}, those involved in the Faradaic reactions,} in a localised volume surrounding each electrode.
+Using DC measurements we conclude that the {\color{blue} concentration of PBS has no effect on the onset of Faradaic conduction for the range of concentrations {\color{blue} measured}.} We hypothesise that this is because the double-layer sets the effective concentration of ions{\color{blue}, those involved in the Faradaic reactions,} in a localised volume surrounding each electrode.
+
 In-vivo measurements of platinum electrodes in sheep spine show that no single concentration of PBS matches both the CPE and the resistive characteristics at once.
-{\color{blue} These measurements also reveal a considerable amount of reactance (see transimpedance measurements in-vivo) that is captured neither by PBS nor the model presented when using a purely resistive spreading resistance.} Nevertheless, {\color{blue}if a single solution of PBS is to be used as a human phantom, a one-tenth concentration solution (by mass)} is a good compromise.
+{\color{blue} These measurements also reveal a considerable amount of reactance (see transimpedance measurements in vivo) that is captured neither by PBS nor the model presented when using a purely resistive spreading resistance.} Nevertheless, {\color{blue}if a single solution of PBS is to be used as a human phantom, a one-tenth concentration solution (by mass)} is a good compromise.
 
@@
 
-    The final model, including 205 lines of resistive mesh, is represented by a SPICE netlist comprised of 348 lines.
-Simulation of this model, using the freely available ngSpice circuit simulator, at 1000 frequencies between spaced between 50\thinspace mHz to 10\thinspace kHz takes approximately 1 second on a modern CPU.
-}
-{
-    \color{red}
-    How is this last line? It's new information in the conclusion...
+    {\color{blue}The final model, including 205 lines of resistive mesh, is represented by a SPICE netlist comprised of 348 lines.
+Simulation of this model, using the freely available ngSpice circuit simulator, at 1000 frequencies takes approximately 1 second on a modern CPU.}
 }
 
-\section*{Acknowledgment}
-The authors wish to acknowledge the The University of Waikato for financial support and Saluda Medical for the use of facilities and equipment.
-{\color{red}Special thanks are expressed to Peter Single of Saluda Medical for help conducting in-vivo measurements.}
+\section*{Acknowledgement}
+The authors acknowledge The University of Waikato for financial support and Saluda Medical for the use of facilities and equipment.
+{\color{blue}Special thanks are expressed to Peter Single of Saluda Medical for help conducting in-vivo measurements.}
 
@@
     vol.~52 no.~7, July 2005, pp1295--1302.
-
-\bibitem{Mohtashami2011}
-    Saba~Mohtashami,
-    ``Electrochemical Properties of Flexible Electrodes for Implanted Neuromuscular Excitation Applications'',
-    Open Acess Dissertations and Theses (2011), Paper 6152
-
-\bibitem{Horch2004}
-    K.~W.~Horsch and G.~S.~Gurpreet,
-    ``Neuroprosthetics: theory and practice'',
-    World Scientific, 2004.
 
@@
 
+\bibitem{Mohtashami2011}
+    Saba~Mohtashami,
+    ``Electrochemical Properties of Flexible Electrodes for Implanted Neuromuscular Excitation Applications'',
+    Open Acess Dissertations and Theses (2011), Paper 6152
+
+\bibitem{Horch2004}
+    K.~W.~Horsch and G.~S.~Gurpreet,
+    ``Neuroprosthetics: theory and practice'',
+    World Scientific, 2004.
+
  \bibitem{Morrison59}
@@
 
-\bibitem{Weiland2000}
-    Weiland~James~D. and Anderson~David~J.,
-    ``Chronic Neural Stimulation with Thin-Film, Iridium Oxide Electrodes'',
-    {\em IEEE Transactions on Biomedical Circuits and Systems},
-    vol.~47 no.~7, July 2000, pp911--918
+%\bibitem{Weiland2000}
+%    Weiland~James~D. and Anderson~David~J.,
+%    ``Chronic Neural Stimulation with Thin-Film, Iridium Oxide Electrodes'',
+%    {\em IEEE Transactions on Biomedical Circuits and Systems},
+%    vol.~47 no.~7, July 2000, pp911--918
 
@@
         \color{blue}
-        The diodes are there to model the change in current attributed to the first biologically damaging reaction that occurs at the electrode/electrolyte interface.
+        The diodes are there to model the change in current attributed to the first biologically damaging reaction that occurs at the electrode-electrolyte interface.
 Whatever reaction occurs first in the relevant electrolyte is the reaction that diode aims to mimic.
 We observe that the current increases near exponentially around this point so we use a diode to mimic that.
-We expect this reaction may not be the same in-vivo as it is in-vivo but the properties of a diode can be altered to match the situation.
+We expect this reaction may not be the same in-vivo as it is in-vitro but the properties of a diode can be altered to match the situation.
 
@@
 Our aim is to capture how the model parameters change as the concentration of PBS is varied and to compare those changes to parameters obtained from in-vivo measurements using a live sheep.
-Were doing this because 0.1X PBS is commonly used as a phantom for real spine.
+We're doing this because 0.1X PBS is commonly used as a phantom for real spine.
 There hasn't been an objective way of determining how accurate that assumption was until we used the model to make this comparison.
-In future we hope to match it against in-vivo stimulus waveforms; at present it is out of scrope.
+In future we hope to match it against in-vivo stimulus waveforms; at present it is out of scope.
     }
@@
         \color{blue}
-        We need this because it represents the resistance of the interface itself, separate from that of the fluid.
+        We need this because it represents the resistance seen by charge crossing the interface, separate from that of the fluid.
         We measure the impedance magnitude of the displacement currents at high frequency (flattened part of Fig.
@@
 
-        The transimpedance measurements give us an interelectrode resistance.
-The displacement measurements at high frequency give us an interelectrode impedance plus an interface impedance.
+        The transimpedance measurements give us an inter-electrode resistance.
+The displacement measurements at high frequency give us an inter-electrode impedance plus an interface impedance.
 Subtracting one from the other gives us a value of resistance that only appears as we pass current through an interface, which we include as $R_{S}$.
+We have added a paragraph at the end of Section \ref{sect:resistorMesh} to clarify the purpose of $R_{S}$.
     }
@@
 We had presented the charge injected in terms of the geometric surface area of each electrode which we know is less than the real (or effective) surface area, estimated to be $14\thinspace mm^{2}$.
-Calculating the charge injection using the effective surface area is more relevant here and gives results consistant with Brummer \& Roblee (Annals New York Academy of Sciences, 159-171, 1983), who also express their values in terms of ``real'' area.
+Calculating the charge injection using the effective surface area is more relevant here and gives results consistent with Brummer \& Roblee (Annals New York Academy of Sciences, 159-171, 1983), who also express their values in terms of ``real'' area.
 
-    }
-    {
-        \color{red}
-        How does this read now? In your last comment you said...
-
-        We have to acknowledge that this is anomalous.
-We were stirring, but definitely observed no gas.
-Say just as you say, the results are consistent with it NOT being a problem, although other researchers have observed otherwise.
-We seem to be saying that they are wrong, so we should say just that, we observe something different, yet results are clearly consistent and explicable!
     }
@@
 Adding more pairs than necessary came at negligible computation cost and having the circuit generated in an automated fashion adds no extra work.
-        {
-            \color{red}
+Extending the CPE's R-C pairs into the lower frequency area did not improve the fit.
+We suspect there is another mechanism at play here.
         We would also like to note that the effect of the CPE is far from that of a simple capacitor, i.e.
@@
 This is part of the reason they are so difficult to simulate in a compact circuit simulator.
-        }
     }
@@
 Perhaps you may know of a way to clarify this issue?
-    }
-
-    {
-       \color{red}
-       Is this what you were after? 
     }
@@
         \color{blue}
-        An extra section explaining a bit about the model and the layout of the paper has been added and the section headings have been expanded slightly to include the names of relevant model elements.
+        An extra paragraph explaining the layout of the paper has been added to the end of the introduction.
+Also, section headings have been expanded slightly to include the names of relevant model elements as per your recommendation.
     }
@@
 For completeness, I recommend the authors explain this term, provide the numeric value (or values) that they used, provide how they adjusted this with concentration, and reference the source of their numeric data.
+
     {
         \color{blue}
-        This term has been made clearer by adding a line to the table caption and by adding a paragraph near the end of Section \ref{sect:resistorNetwork} explaining where the source of the values.
+        The title of Table \ref{tab:RESparams} has been amended to make use of the term sigma ($\sigma$) as electrolyte conductivity clear.
+The source of conductivity measurements has been added at the end of the second to last paragraph of Section \ref{sect:resistorMesh}.
     }
@@
         \color{blue}
-        A diagram showing the layout of the resistor mesh has been added along with the total number of resistors in the mesh for an 8 electrode system.
+        A diagram showing the layout of the resistor mesh has been added along with the total number of resistors in the mesh for an 8 electrode system in Section \ref{sect:resistorMesh}.
     }
@@
         \color{blue}
-
+        A statement as recommended has been added to Section \ref{sect:cpe} detailing the number of R-C branches and the total number of elements in the CPE model.
     }
@@
         \color{blue}
-        Table \ref{tab:CPEparams} has been amended to inclued mention of 'concentration' being that of mass concentration of PBS.
+        Table \ref{tab:CPEparams} has been amended to include mention of 'concentration' being that of mass concentration of PBS.
+Also, clarification of this concentration (by mass) has been added throughout the paper where appropriate.
     }
@@
         \color{blue}
-        That is a very important piece of information we've missed! Thank you for bringing that to our attention.
-
+        That is a very important piece of information we've missed!
+Thank you for bringing that to our attention.
+We have revised Section \ref{sect:in-vivo} to more fully explain and bring in more in-vivo measurements.
     }
@@
         \color{blue}
-        The overall size of the spice file that contains all the elements of the 8 electrode model, one element per line, is 370 lines including some unnecessary formatting lines.
-A standard Dell optiplex workstation can generate that file using the model parameters, simulate the model using ngSPICE, and read the output back from the simulation result in under a second.
+        Following your recommendation a paragraph has been added to the end of the conclusion stating the model size and approximate execution speed.
     }
@@
         The 0.9V limitation is rather arbitrary as it was specific to the use of electrodes 2 and 7.
-We have instead clarified that the model only captures the onset of Faradaic conduction sufficient for it to be avoided.
-A sentence to this effect have been added to the end of the conclusion.
+We have instead clarified that the model only captures the onset of Faradaic conduction sufficient for it to be avoided (this has been done throughout the paper).
+This limitation has been brought up in the conclusion.
     }

### 2014-04-17 paper.tex
Figures to Fig.

@@
 
-The electrode used in this work is a commercial linear array of eight platinum electrodes, called an ``Octrode'', intended for Spinal Cord Stimulator (SCS) implantation.~\cite{StJudeOctrode} A picture of an Octrode is presented in figure~\ref{fig:octrode}.
+The electrode used in this work is a commercial linear array of eight platinum electrodes, called an ``Octrode'', intended for Spinal Cord Stimulator (SCS) implantation.~\cite{StJudeOctrode} A picture of an Octrode is presented in Fig.~\ref{fig:octrode}.
 A solution of phosphate buffered saline (PBS) diluted to one-tenth concentration (0.1X) is commonly {\color{blue}used as a crude phantom} in the case of SCS, while full concentration (1.0X) PBS is considered more representative of the situation in blood.
@@
 The model is compact in that it is suitable for {\color{blue} entering into freely available electrical circuit simulation software}.
-The schematic for the {\color{blue} electrode-electrolyte interface} model used is presented as Figure \ref{fig:schematic}.
+The schematic for the {\color{blue} electrode-electrolyte interface} model used is presented as Fig.~\ref{fig:schematic}.
 }
@@
 The mesh depth and padding values of five columns and three rows, respectively, has been taken directly from \cite{ScottSingle2013}.
-{\color{blue} These parameters, together with an array of 8 electrodes, leads to a generated network of 205 resistors, the layout of which is presented in figure \ref{fig:mesh}.}
+{\color{blue} These parameters, together with an array of 8 electrodes, leads to a generated network of 205 resistors, the layout of which is presented in Fig.~\ref{fig:mesh}.}
 
@@
 Hence, we define $R_{sri}$ to be 3/4 that of $R_{eri}$ making it a dependant parameter.}.
-The resulting fit and parameter values are presented in figure~\ref{fig:transresistance} and Table~\ref{tab:RESparams}.
+The resulting fit and parameter values are presented in Fig.~\ref{fig:transresistance} and Table~\ref{tab:RESparams}.
 
@@
 
-We measure displacement currents by sweeping the frequency of a sinusoidal stimulus across electrodes 2 and 7 of the Octrode while measuring the voltage between electrodes 2 and 3 (numbering shown in figure~\ref{fig:octrode}).
+We measure displacement currents by sweeping the frequency of a sinusoidal stimulus across electrodes 2 and 7 of the Octrode while measuring the voltage between electrodes 2 and 3 (numbering shown in Fig.~\ref{fig:octrode}).
 This allows for the measurement of a single interface impedance in series with the resistance presented by the bulk solution.
@@
     Current density during measurements, calculated using an effective surface area of $14\thinspace mm^{2}$, peaked at $161\thinspace \mu A/cm^{2}$ at 10\thinspace kHz in 1.0X PBS and fell as low as $197\thinspace nA/cm^{2}$ at 50\thinspace mHz in 0.025X PBS.
-}Charge injection per phase is shown in figure~\ref{fig:chargeInjectionVsFrequency} for each solution.
+}Charge injection per phase is shown in Fig.~\ref{fig:chargeInjectionVsFrequency} for each solution.
 The stimulus waveform was set at 300\thinspace mV (peak) at each measurement point.
@@
 
-Figure~\ref{fig:CPE_Magnitude} shows the magnitude of the measured response {\color{blue}for each concentration of PBS} accompanied by simulation results.
-Figure~\ref{fig:CPE_Phase} shows the phase response for the same measurements, again with the simulated response at each concentration.
+Fig.~\ref{fig:CPE_Magnitude} shows the magnitude of the measured response {\color{blue}for each concentration of PBS} accompanied by simulation results.
+Fig.~\ref{fig:CPE_Phase} shows the phase response for the same measurements, again with the simulated response at each concentration.
 The simulated responses are generated using fitted parameter values for {\color{blue} $m$, $k$, $|Z|\thinspace @\thinspace 1Hz$, and $R_S$, which are} presented in Table~\ref{tab:CPEparams}.
 
-As shown in the interface model schematic (figure~\ref{fig:schematic}), the interface contains its own internal series resistance ($R_{S}$).
+As shown in the interface model schematic (Fig.~\ref{fig:schematic}), the interface contains its own internal series resistance ($R_{S}$).
 The resistance seen in series with the CPE will therefore be the sum of both the resistance due to the bulk resistivity of the fluid and $R_{S}$, to which we will refer as $R_{S+bulk}$.
-In figure~\ref{fig:CPE_Magnitude}, the slope and magnitude of the CPE are visible below 1\thinspace Hz whereas $R_{S+bulk}$  dominates above 1\thinspace kHz; it is clear that the two do not scale similarly.
+In Fig.~\ref{fig:CPE_Magnitude}, the slope and magnitude of the CPE are visible below 1\thinspace Hz whereas $R_{S+bulk}$  dominates above 1\thinspace kHz; it is clear that the two do not scale similarly.
 As the impedance of the CPE and $R_{S+bulk}$ are separable with frequency, these measurements can be used to determine the CPE parameters and $R_{S}$.
 
-Figure~\ref{fig:CPE_Scaling} shows measured data and the corresponding fits for both the CPE magnitude at 0.05\thinspace Hz and $R_{S+bulk}$.
+Fig.~\ref{fig:CPE_Scaling} shows measured data and the corresponding fits for both the CPE magnitude at 0.05\thinspace Hz and $R_{S+bulk}$.
 Here we express the CPE offset parameter as $|Z|\thinspace @ \thinspace 1Hz$, but the fits used $|Z|\thinspace @ \thinspace 0.05Hz$, as data points at this frequency are outside the transitional zone where the impedance of the CPE and that of $R_{S+bulk}$ overlap.
 
-The data presented in figure~\ref{fig:CPE_Magnitude} shows a large, linear, relative shift of $|Z|$ with salinity at higher frequencies, where the resistive component of the solution dominates.
+The data presented in Fig.~\ref{fig:CPE_Magnitude} shows a large, linear, relative shift of $|Z|$ with salinity at higher frequencies, where the resistive component of the solution dominates.
 Conversely, at lower frequencies where $|Z|$ changes with frequency, the relative change is closer to being logarithmic. It is this region that is modelled by the CPE.
@@
 Our measurements were repeated using wait-times of 4, 16, 32 and 64 seconds between voltage increments, allowing us to determine the effect of sweep rate.
-From these measurements and those of a separate investigation\footnote{We took measurements of the interface's response to voltage steps when left to settle for 10 000 seconds, of which the first 250\thinspace seconds are shown in figure~\ref{fig:CPE_currentVsTime}.
+From these measurements and those of a separate investigation\footnote{We took measurements of the interface's response to voltage steps when left to settle for 10 000 seconds, of which the first 250\thinspace seconds are shown in Fig.~\ref{fig:CPE_currentVsTime}.
 Those measurements show a trend of decreasing current stabilisation time as the overpotential steps increase.
@@
 
-In figure~\ref{fig:StepResponse_Faradaic}, electrical current measurements (solid lines) are plotted against time.
+In Fig.~\ref{fig:StepResponse_Faradaic}, electrical current measurements (solid lines) are plotted against time.
 Each spike marks the point at which the voltage is incremented by 50\thinspace mV.
@@
 
-Figure~\ref{fig:faradaic_logCurrentVsVoltage} shows the settled currents plotted on a log scale, versus the voltage applied across the electrode {\color{blue} pair}.
+Fig.~\ref{fig:faradaic_logCurrentVsVoltage} shows the settled currents plotted on a log scale, versus the voltage applied across the electrode {\color{blue} pair}.
 This uses the same data as the previous figure but has been processed so that each point represents the average of the final 24 current measurements at each step.
@@
 The effect of transition can be seen in the green trace at 1.0\thinspace V where the error bar is wide due to the current shift being captured in the measurement at that voltage.
-Part of a transition with respect to time is visible in figure~\ref{fig:StepResponse_Faradaic} where the red trace drops uncharacteristically after the increment at around 600 seconds.
+Part of a transition with respect to time is visible in Fig.~\ref{fig:StepResponse_Faradaic} where the red trace drops uncharacteristically after the increment at around 600 seconds.
 
@@
 
-    Figure~\ref{fig:faradaic_currentVsTime} shows a subset of the data used in figure~\ref{fig:StepResponse_Faradaic} (the 1.0X PBS trace) to show the fit between simulated and measured data in the time domain.
+    Fig.~\ref{fig:faradaic_currentVsTime} shows a subset of the data used in Fig.~\ref{fig:StepResponse_Faradaic} (the 1.0X PBS trace) to show the fit between simulated and measured data in the time domain.
 Here the simulation contains fitted diode parameters, shown in Table~\ref{tab:FaradaicParams}, which give rise to the exponentially increasing steady state current.
@@
 These transient decay curves appear to have a time-constant\footnote{We use the term ``time-constant'' although a CPE does not have a simple exponential time-domain response.} that decreases with each subsequent measurement.
-This variable time-constant phenomena is especially clear when looking at figure~\ref{fig:CPE_currentVsTime}.
+This variable time-constant phenomena is especially clear when looking at Fig.~\ref{fig:CPE_currentVsTime}.
 Although the Faradaic response transients appear to approach the time-constant predicted by the CPE, there is still behaviour not completely described by the CPE.
 
-The match between fitted diode parameters ($n$ and $i_{0}$) and the measurement data 64 seconds after each voltage increment has been plotted in figure~\ref{fig:faradaic_currentVsVoltage}.
+The match between fitted diode parameters ($n$ and $i_{0}$) and the measurement data 64 seconds after each voltage increment has been plotted in Fig.~\ref{fig:faradaic_currentVsVoltage}.
 
@@
 
-{\color{blue} Each of the model characterisation} measurements were repeated inside the spinal canal of living sheep, just outside the dura as shown in figure~\ref{fig:sheepSpine}.
+{\color{blue} Each of the model characterisation} measurements were repeated inside the spinal canal of living sheep, just outside the dura as shown in Fig.~\ref{fig:sheepSpine}.
 Two sheep were prepared and anaesthetised using the procedures described in \cite{Parker2013} under the Animal Care and Ethics Committee approval of the Royal North Shore Hospital, Sydney.
@@
 Time constraints with the live animal meant only {\color{blue} a single} dataset was obtained for transimpedance.
-{\color{blue} This data is} shown in figures~\ref{fig:displacement_sheepCPEMagnitude} and \ref{fig:displacement_sheepCPEPhase} along with results obtained {\color{blue} from} simulation {\color{blue} with} fitted parameters.
+{\color{blue} This data is} shown in Figs.~\ref{fig:displacement_sheepCPEMagnitude} and \ref{fig:displacement_sheepCPEPhase} along with results obtained {\color{blue} from} simulation {\color{blue} with} fitted parameters.
 }
-{\color{blue} In these measurements a phase deviation of approximately 30 degrees is observed, visible in figure~\ref{fig:transimpedance_sheep_phase}.
+{\color{blue} In these measurements a phase deviation of approximately 30 degrees is observed, visible in Fig.~\ref{fig:transimpedance_sheep_phase}.
 There was no measurable phase deviation for these measurements in PBS.
@@
 {\color{blue}
-    Four measurements of displacement currents (CPE element in the model) were} taken at regular intervals over a period of 30 minutes and have been presented in figures~\ref{fig:displacement_sheepCPEMagnitude} and~\ref{fig:displacement_sheepCPEPhase}.
-{\color{blue} These measurements appear on top of the traces taken from figures~\ref{fig:CPE_Magnitude} and~\ref{fig:CPE_Phase} for comparison.}
+    Four measurements of displacement currents (CPE element in the model) were} taken at regular intervals over a period of 30 minutes and have been presented in Figs.~\ref{fig:displacement_sheepCPEMagnitude} and~\ref{fig:displacement_sheepCPEPhase}.
+{\color{blue} These measurements appear on top of the traces taken from Figs.~\ref{fig:CPE_Magnitude} and~\ref{fig:CPE_Phase} for comparison.}
 
@@
     \end{center}
-    \caption{\color{blue} Comparison between the mean magnitude of measured displacement currents in four live sheep (blue trace), each of the PBS traces from figure~\ref{fig:CPE_Magnitude} (grey lines), and a simulated fit to the sheep data (red trace).
+    \caption{\color{blue} Comparison between the mean magnitude of measured displacement currents in four live sheep (blue trace), each of the PBS traces from Fig.~\ref{fig:CPE_Magnitude} (grey lines), and a simulated fit to the sheep data (red trace).
 Error bars have been placed one standard deviation either side of the mean for measured data.}
@@
     \end{center}
-    \caption{{\color{blue} Comparison of the mean phase response of measured displacement currents in live sheep (blue trace), each of the PBS traces taken from figure~\ref{fig:CPE_Phase} (grey lines), and a simulated fit to the sheep data (red trace).
+    \caption{{\color{blue} Comparison of the mean phase response of measured displacement currents in live sheep (blue trace), each of the PBS traces taken from Fig.~\ref{fig:CPE_Phase} (grey lines), and a simulated fit to the sheep data (red trace).
 Error bars have been placed one standard deviation either side of the mean for measured data.}}

### 2014-04-17 paper.tex
Jonathans final edits

@@
     In this manuscript we use an adapted version of the compact non-linear model presented in \cite{ScottSingle2013}.
-The model is compact in that it is suitable for {\color{blue} entering into freely available electrical circuit simulation software}.
-The schematic for the {\color{blue} electrode-electrolyte interface} model used is presented as Fig.~\ref{fig:schematic}.
+The model is compact in that it is suitable for {\color{blue} entry into freely available electrical circuit simulation software}.
+The schematic of the {\color{blue} electrode-electrolyte interface} model that we have used is presented as Fig.~\ref{fig:schematic}.
 }
 
-The electrical interface model of \cite{Franks2005} and \cite{ScottSingle2013} has two parts, a displacement branch and a Faradaic branch.
+The electrical interface models of \cite{Franks2005} and \cite{ScottSingle2013} have two parts, a displacement branch and a Faradaic branch.
 {
@@
 With parameters fitted for the scaling of both the CPE and $R_{S}$ with PBS concentration, we turn to Faradaic conduction.
-
 Our model uses two reverse-connected diodes to represent Faradaic current conduction between electrode and electrolyte.
@@
     Transimpedance measurements in-vivo were {\color{blue} conducted with} additional configurations than were carried out in Section \ref{sect:resistorMesh}.
-The same measurements were captured {\color{blue} except this time using} a more complete stimulus--measure regime in order to minimise the effect of nearby bone.
+The same measurements were captured {\color{blue} except this time using a larger number of stimulus--measure configurations} in order to minimise the effect of nearby bone.
 Time constraints with the live animal meant only {\color{blue} a single} dataset was obtained for transimpedance.
@@
 {\color{blue}
-    Four measurements of displacement currents (CPE element in the model) were} taken at regular intervals over a period of 30 minutes and have been presented in Figs.~\ref{fig:displacement_sheepCPEMagnitude} and~\ref{fig:displacement_sheepCPEPhase}.
+    Four measurements of displacement current (CPE element in the model) were} taken at regular intervals over a period of 30 minutes, {\color{blue} the mean response is presented} in Figs.~\ref{fig:displacement_sheepCPEMagnitude} and~\ref{fig:displacement_sheepCPEPhase}.
 {\color{blue} These measurements appear on top of the traces taken from Figs.~\ref{fig:CPE_Magnitude} and~\ref{fig:CPE_Phase} for comparison.}
@@
 The authors acknowledge The University of Waikato for financial support and Saluda Medical for the use of facilities and equipment.
-{\color{blue}Special thanks are expressed to Peter Single of Saluda Medical for help conducting in-vivo measurements.}
+{\color{blue}Special thanks are expressed to Peter Single of Saluda Medical for help conducting in-vivo measurements and to the anonymous reviewer whose detailed comments lead to a much more rigorous manuscript.}
 
@@
         \color{blue}
-        That is interesting and definitely important to our modelling work.
+        That is interesting and definitely important to our modelling work, thank you for picking that up.
 We had presented the charge injected in terms of the geometric surface area of each electrode which we know is less than the real (or effective) surface area, estimated to be $14\thinspace mm^{2}$.
@@
 This is part of the reason they are so difficult to simulate in a compact circuit simulator.
+The CPE is an imperfect model of the interface, as can be seen from the phase deviation at very low frequencies between measured and simulated data.
     }
@@
         We feel that the in-vivo results will be affected by the significant inhomogeneity of real spine by proximity of bone, change in fluid at dura, etc.
-Perhaps you may know of a way to clarify this issue?
+Perhaps you may know a way that we might use to clarify this issue in the future?
     }

### 2014-06-19 paper.tex
Removed reviewers comments and blue edit highlighting

--- 2014-04-17 paper.tex
@@
 We report how the impedance presented by a platinum electrode scales with the concentration of phosphate buffered saline (PBS).
-{
-    \color{blue}
 We measure the response in various dilutions of PBS with an electrode array as is commonly used in spinal cord stimulator (SCS) implants.
 We match the parameters of a non-linear electrode-electrolyte interface model to these measurements.
-}
 We find that the constant phase element of the model scales with approximately the log of concentration, whereas the resistivity is inversely proportional.
-Using a novel DC measurement technique we show that the {\color{blue} onset of Faradaic conduction for} a platinum electrode, and thus the safe exposure limit, does not scale with concentration.
+Using a novel DC measurement technique we show that the onset of Faradaic conduction for a platinum electrode, and thus the safe exposure limit, does not scale with concentration.
 We compare objective measurements made in saline to those made in the spinal cavity of live sheep. We comment upon the appropriateness of using PBS as a substitute for in-vivo measurements.
@@
 The electrode used in this work is a commercial linear array of eight platinum electrodes, called an ``Octrode'', intended for Spinal Cord Stimulator (SCS) implantation.~\cite{StJudeOctrode} A picture of an Octrode is presented in Fig.~\ref{fig:octrode}.
-A solution of phosphate buffered saline (PBS) diluted to one-tenth concentration (0.1X) is commonly {\color{blue}used as a crude phantom} in the case of SCS, while full concentration (1.0X) PBS is considered more representative of the situation in blood.
+A solution of phosphate buffered saline (PBS) diluted to one-tenth concentration (0.1X) is commonly used as a crude phantom in the case of SCS, while full concentration (1.0X) PBS is considered more representative of the situation in blood.
 
@@
 The ingredients of that stock solution are given in Table~\ref{tab:PBSrecipe}.
-
-{
-    \color{blue}
 
@@
     In this manuscript we use an adapted version of the compact non-linear model presented in \cite{ScottSingle2013}.
-The model is compact in that it is suitable for {\color{blue} entering into freely available electrical circuit simulation software}.
-The schematic for the {\color{blue} electrode-electrolyte interface} model used is presented as Fig.~\ref{fig:schematic}.
-}
+The model is compact in that it is suitable for entry into freely available electrical circuit simulation software.
+The schematic of the electrode-electrolyte interface model that we have used is presented as Fig.~\ref{fig:schematic}.
 
-The electrical interface model of \cite{Franks2005} and \cite{ScottSingle2013} has two parts, a displacement branch and a Faradaic branch.
-{
-    \color{blue}
+The electrical interface models of \cite{Franks2005} and \cite{ScottSingle2013} have two parts, a displacement branch and a Faradaic branch.
     Scott and Single incorporate memristors into their model, used to mimic a diffusion limited current conduction mode, i.e., their purpose is to throttle electrical current associated with Faradaic reactions.
 In an implanted setting an electrode should never be operated in a Faradaic conduction mode and certainly never to the point of becoming diffusion limited; for this reason, memristors have been omitted.
-}
 
 It has been suggested that the primary coupling mechanism between platinum electrodes and physiological saline is the reversible evolution of gas, probably oxygen, at the platinum surface, which dissolves without bubble formation.\cite{Greatbatch1969} Understanding the exact mechanism of displacement or Faradaic charge transfer at the electrode surface is beyond the scope of this work.
-Rather, we wish to characterise the {electrode-electrolyte interface \color{blue} using a small} {\color{blue} number of} parameters that can be fed into an electrical model.
+Rather, we wish to characterise the electrode-electrolyte interface using a small number of parameters that can be fed into an electrical model.
 
-{
-    \color{blue}
 The remainder of this manuscript is broken into five sections.
-Section \ref{sect:resistorMesh} details the measurement of the inter-electrode resistances {\color{blue}(arising from the bulk resistance of the solution)} and the generation of a resistor network to replicate these resistances.
+Section \ref{sect:resistorMesh} details the measurement of the inter-electrode resistances (arising from the bulk resistance of the solution) and the generation of a resistor network to replicate these resistances.
+
 Sections \ref{sect:cpe} and \ref{sect:faradaic} are concerned with the measurement and parameter fitting of displacement currents and Faradaic currents, respectively, across the electrolyte interface.
-Section \ref{sect:in-vivo} compares the results obtained {\color{blue}for} PBS with measurements {\color{blue} made} in-vivo.
+Section \ref{sect:in-vivo} compares the results obtained for PBS with measurements made in-vivo.
 Finally, in Section \ref{sect:conclusion} we summarise our findings and give concluding comments.
-}
 
-\section{{\color{blue}Bulk Resistivity / Resistor} Network }
+\section{Bulk Resistivity / Resistor Network }
 \label{sect:resistorMesh}
@@
 To quantify the impedance presented by a single interface we first need to determine inter-electrode resistance presented by the electrolyte bulk.
-{\color{blue} Finding these resistances allows us to quantify the {\color{blue}series resistance of the interface ($R_{S}$)} via subtraction.} As there are always two interface impedances between any two electrodes, inter-electrode resistances cannot be measured in isolation.
+Finding these resistances allows us to quantify the series resistance of the interface ($R_{S}$) via subtraction.
+As there are always two interface impedances between any two electrodes, inter-electrode resistances cannot be measured in isolation.
 
@@
 The mesh depth and padding values of five columns and three rows, respectively, has been taken directly from \cite{ScottSingle2013}.
-{\color{blue} These parameters, together with an array of 8 electrodes, leads to a generated network of 205 resistors, the layout of which is presented in Fig.~\ref{fig:mesh}.}
+These parameters, together with an array of 8 electrodes, leads to a generated network of 205 resistors, the layout of which is presented in Fig.~\ref{fig:mesh}.
 
-A numerical fit {\color{blue} has been} made to the two independent scaling parameters $R_{eri}$ and $R_{li}$\footnote{The values of $R_{eri}$ and $R_{sri}$ are defined by the lengths of the electrode and inter-electrode spacers respectively as described in \cite{ScottSingle2013}.
+A numerical fit has been made to the two independent scaling parameters $R_{eri}$ and $R_{li}$\footnote{The values of $R_{eri}$ and $R_{sri}$ are defined by the lengths of the electrode and inter-electrode spacers respectively as described in \cite{ScottSingle2013}.
 The two parameters are proportional to each other by the ratio of their lengths.
@@
 
-Measurements of the inter-electrode impedance {\color{blue} were made using} a Tektronix TPS2014 DSO with four fully isolated and floating channels; an Agilent 33220A Function Generator; and a desktop PC {\color{blue} running Python 2.7 for instrumentation control and result processing.} The pH level of the stock solution was measured using a calibrated EDT Instruments BA-350 pH meter.
+Measurements of the inter-electrode impedance were made using a Tektronix TPS2014 DSO with four fully isolated and floating channels; an Agilent 33220A Function Generator; and a desktop PC running Python 2.7 for instrumentation control and result processing.
+The pH level of the stock solution was measured using a calibrated EDT Instruments BA-350 pH meter.
 It had a pH of 7.4 and no pH adjustments were made to the derived solutions.
-{\color{blue} The conductivity of solutions was measured using an EDT Instruments RE 388 Tx conductivity meter.}
+The conductivity of solutions was measured using an EDT Instruments RE 388 Tx conductivity meter.
 
-{
-    \color{blue}
 To be clear, the resistive mesh created in this step models \textit{only} the resistivity of the solution bulk.
 No contribution from the interface itself appears in these measurements.
-{\color{blue} This measurement is possible} because voltages are always measured across pairs of non-driven electrodes and the measurements are of suitably high impedance.
-We determine the resistive component of the interface, $R_{S}$, in the {\color{blue} following} section.
-}
+This measurement is possible because voltages are always measured across pairs of non-driven electrodes and the measurements are of suitably high impedance.
+We determine the resistive component of the interface, $R_{S}$, in the following section.
 
@@
 
-\section{Displacement Parameters {\color{blue}/ CPE}}
+\section{Displacement Parameters / CPE}
 \label{sect:cpe}
 Displacement currents are responsible for capacitive behaviour at interfacial boundaries.
-They are brought about by the redistribution of charge in response to applied fields, {\color{blue}e.g.,} a charged electrode will attract or repel $Cl^{-}$ from its surface and reorientate polar molecules in the surrounding solution.\cite{Merrill05} This capacitive behaviour may also be the result of electrode polarisation in the form of reversible Faradaic reactions at the surface of the electrode.
+They are brought about by the redistribution of charge in response to applied fields, e.g., a charged electrode will attract or repel $Cl^{-}$ from its surface and reorientate polar molecules in the surrounding solution.\cite{Merrill05} This capacitive behaviour may also be the result of electrode polarisation in the form of reversible Faradaic reactions at the surface of the electrode.
 Such reactions involving water and platinum, as identified in \cite{Horch2004,Mohtashami2011,Merrill05}, include:
@@
 The placement of R-C pairs within the CPE is determined by Morrison's parameters $m$ and $k$, where $k$ determines the spacing, or density, of R-C branches and $m$ determines the resulting slope.
-{\color{blue} R-C pairs were generated using a Python script to span 1\thinspace nHz --1\thinspace GHz with a spacing of 3 pairs per decade.
+R-C pairs were generated using a Python script to span 1\thinspace nHz --1\thinspace GHz with a spacing of 3 pairs per decade.
 The CPE contains 55 branches i.e.
-110 {\color{blue}electrical} elements are used to represent the CPE.}
+110 electrical elements are used to represent the CPE.
 
@@
 
-{
-    \color{blue}
 Current density during measurements, calculated using an effective surface area of $14\thinspace mm^{2}$, peaked at $161\thinspace \mu A/cm^{2}$ at 10\thinspace kHz in 1.0X PBS and fell as low as $197\thinspace nA/cm^{2}$ at 50\thinspace mHz in 0.025X PBS.
-}Charge injection per phase is shown in Fig.~\ref{fig:chargeInjectionVsFrequency} for each solution.
+Charge injection per phase is shown in Fig.~\ref{fig:chargeInjectionVsFrequency} for each solution.
 The stimulus waveform was set at 300\thinspace mV (peak) at each measurement point.
@@
     \end{center}
-    \caption{\color{blue} Per phase charge injected during CPE measurement in each concentrations of PBS{\color{blue}, calculated with an effective surface area of 14\thinspace mm$^{2}$.}}
+    \caption{Per phase charge injected during CPE measurement in each concentrations of PBS, calculated with an effective surface area of 14\thinspace mm$^{2}$.}
     \label{fig:chargeInjectionVsFrequency}
@@
 
-Fig.~\ref{fig:CPE_Magnitude} shows the magnitude of the measured response {\color{blue}for each concentration of PBS} accompanied by simulation results.
+Fig.~\ref{fig:CPE_Magnitude} shows the magnitude of the measured response for each concentration of PBS accompanied by simulation results.
 Fig.~\ref{fig:CPE_Phase} shows the phase response for the same measurements, again with the simulated response at each concentration.
-The simulated responses are generated using fitted parameter values for {\color{blue} $m$, $k$, $|Z|\thinspace @\thinspace 1Hz$, and $R_S$, which are} presented in Table~\ref{tab:CPEparams}.
+The simulated responses are generated using fitted parameter values for $m$, $k$, $|Z|\thinspace @\thinspace 1Hz$, and $R_S$, which are presented in Table~\ref{tab:CPEparams}.
 
@@
 
-\section{Faradaic Parameters {\color{blue}/ Diodes}}
+\section{Faradaic Parameters / Diodes}
 \label{sect:faradaic}
@@
 (Any reversible reactions, those producing reactants bound to the surface of the electrode, are encapsulated by the displacement branch of the model.)
-Possible irreversible Faradaic reactions for platinum electrodes {\color{blue}(each with differing reaction potentials)} in saline are:
+Possible irreversible Faradaic reactions for platinum electrodes (each with differing reaction potentials) in saline are:
 
@@
 
-{
-    \color{blue}
 We use a diode to model the electrical current conduction caused by one reaction proceeding in one direction, i.e.
@@
 It is expected that the situation in-vivo will be much more complex and that fitted diode parameters may encapsulate multiple reactions if they occur close together.
-}
 
-{\color{blue} To measure Faradaic conduction we must separate its contribution from any displacement behaviour.} By using a DC measurement technique, as opposed to cyclic measurements, we are able to separate the effects in time.
-Like a conventional capacitor, the CPE responds {\color{blue} to a change in voltage by absorbing or ejecting charge, causing a spike in current}.
+To measure Faradaic conduction we must separate its contribution from any displacement behaviour.
+By using a DC measurement technique, as opposed to cyclic measurements, we are able to separate the effects in time.
+Like a conventional capacitor, the CPE responds to a change in voltage by absorbing or ejecting charge, causing a spike in current.
 The CPE will draw negligible current once it has settled and in the case of our model we assume the remaining current conduction to be the result of Faradaic processes.
@@
 Dotted lines have been added that link the electrical current measurements taken 10 seconds after each increment for 0.125X PBS (lower trace) and 1.0X PBS (upper trace).
-These dotted traces show results typical of cyclic {\color{blue} measurement} methods, where the electrode overpotential is never constant.
+These dotted traces show results typical of cyclic measurement methods, where the electrode overpotential is never constant.
 This illustrates the benefit of using DC measurements when measuring Faradaic currents.
 
-Fig.~\ref{fig:faradaic_logCurrentVsVoltage} shows the settled currents plotted on a log scale, versus the voltage applied across the electrode {\color{blue} pair}.
+Fig.~\ref{fig:faradaic_logCurrentVsVoltage} shows the settled currents plotted on a log scale, versus the voltage applied across the electrode pair.
 This uses the same data as the previous figure but has been processed so that each point represents the average of the final 24 current measurements at each step.
@@
 We hypothesise that the charging of the CPE draws available ions to the electrode, creating a layer of high ionic concentration at the surface irrespective of that of the solution bulk.
-It is this layer that is subsequently consumed by the Faradaic reactions at a {\color{blue} rate that increases exponentially with} electrode overpotential.
+It is this layer that is subsequently consumed by the Faradaic reactions at a rate that increases exponentially with electrode overpotential.
 The effect of bulk solution concentration while this layer has formed is negligible until the point at which the layer is consumed faster than it can be replenished.
@@
 For the purposes of our model, we are content with placing a limit of 0.9\thinspace V across the pair of interfaces and using the assumption that Faradaic conduction does not change with concentration.
-{\color{blue} As we are primarily interested with capturing only the onset of Faradaic conduction, this limitation does not degrade the usefulness of the model for implant modelling purposes.}
+As we are primarily interested with capturing only the onset of Faradaic conduction, this limitation does not degrade the usefulness of the model for implant modelling purposes.
 
@@
     \end{center}
-    \caption{\color{blue} Comparison between the magnitude of in-vivo transresistance measurements (blue dots) and simulation results using fitted mesh parameters (red trace).}
+    \caption{Comparison between the magnitude of in-vivo transresistance measurements (blue dots) and simulation results using fitted mesh parameters (red trace).}
     \label{fig:transimpedance_sheep_mag}
@@
     \end{center}
-    \caption{\color{blue} Comparison between the phase of in-vivo transresistance measurements (blue dots) and simulation results using fitted mesh parameters (red trace).
+    \caption{Comparison between the phase of in-vivo transresistance measurements (blue dots) and simulation results using fitted mesh parameters (red trace).
 The simulation mesh does not capture any phase relationship due to being purely resistive.}
@@
 
-{\color{blue} Each of the model characterisation} measurements were repeated inside the spinal canal of living sheep, just outside the dura as shown in Fig.~\ref{fig:sheepSpine}.
+Each of the model characterisation measurements were repeated inside the spinal canal of living sheep, just outside the dura as shown in Fig.~\ref{fig:sheepSpine}.
 Two sheep were prepared and anaesthetised using the procedures described in \cite{Parker2013} under the Animal Care and Ethics Committee approval of the Royal North Shore Hospital, Sydney.
@@
 
-{
-    \color{blue}
-    Transimpedance measurements in-vivo were {\color{blue} conducted with} additional configurations than were carried out in Section \ref{sect:resistorMesh}.
-The same measurements were captured {\color{blue} except this time using} a more complete stimulus--measure regime in order to minimise the effect of nearby bone.
-Time constraints with the live animal meant only {\color{blue} a single} dataset was obtained for transimpedance.
-{\color{blue} This data is} shown in Figs.~\ref{fig:displacement_sheepCPEMagnitude} and \ref{fig:displacement_sheepCPEPhase} along with results obtained {\color{blue} from} simulation {\color{blue} with} fitted parameters.
-}
-{\color{blue} In these measurements a phase deviation of approximately 30 degrees is observed, visible in Fig.~\ref{fig:transimpedance_sheep_phase}.
+Transimpedance measurements in-vivo were conducted with additional configurations than were carried out in Section \ref{sect:resistorMesh}.
+The same measurements were captured except this time using a larger number of stimulus--measure configurations in order to minimise the effect of nearby bone.
+Time constraints with the live animal meant only a single dataset was obtained for transimpedance.
+This data is shown in Figs.~\ref{fig:displacement_sheepCPEMagnitude} and \ref{fig:displacement_sheepCPEPhase} along with results obtained from simulation with fitted parameters.
+
+In these measurements a phase deviation of approximately 30 degrees is observed, visible in Fig.~\ref{fig:transimpedance_sheep_phase}.
 There was no measurable phase deviation for these measurements in PBS.
-These results indicate that the sheep itself presents a significant reactive component.}
+These results indicate that the sheep itself presents a significant reactive component.
 
-{\color{blue}
-    Four measurements of displacement currents (CPE element in the model) were} taken at regular intervals over a period of 30 minutes and have been presented in Figs.~\ref{fig:displacement_sheepCPEMagnitude} and~\ref{fig:displacement_sheepCPEPhase}.
-{\color{blue} These measurements appear on top of the traces taken from Figs.~\ref{fig:CPE_Magnitude} and~\ref{fig:CPE_Phase} for comparison.}
+Four measurements of displacement current (CPE element in the model) were taken at regular intervals over a period of 30 minutes, the mean response is presented in Figs.~\ref{fig:displacement_sheepCPEMagnitude} and~\ref{fig:displacement_sheepCPEPhase}.
+These measurements appear on top of the traces taken from Figs.~\ref{fig:CPE_Magnitude} and~\ref{fig:CPE_Phase} for comparison.
 
-Although it is clear that there are complications in vivo, a 0.25X PBS {\color{blue} solution} offers a good approximation to the resistive part of the  trace.
-The reactive part {\color{blue} (that of the CPE)} would be better modelled by a solution of less than 0.025X concentration.
+Although it is clear that there are complications in vivo, a 0.25X PBS solution offers a good approximation to the resistive part of the  trace.
+The reactive part (that of the CPE) would be better modelled by a solution of less than 0.025X concentration.
 
-{
-    \color{blue}
 Faradaic measurements on the live animal were abandoned as they were likely to cause potentially violent muscle contraction.
 Attempts to measure the response at low stimulus potentials yielded unsatisfactory results and were subsequently discarded.
-}
+
 \begin{figure}
@@
     \end{center}
-    \caption{\color{blue} Comparison between the mean magnitude of measured displacement currents in four live sheep (blue trace), each of the PBS traces from Fig.~\ref{fig:CPE_Magnitude} (grey lines), and a simulated fit to the sheep data (red trace).
+    \caption{Comparison between the mean magnitude of measured displacement currents in four live sheep (blue trace), each of the PBS traces from Fig.~\ref{fig:CPE_Magnitude} (grey lines), and a simulated fit to the sheep data (red trace).
 Error bars have been placed one standard deviation either side of the mean for measured data.}
@@
     \end{center}
-    \caption{{\color{blue} Comparison of the mean phase response of measured displacement currents in live sheep (blue trace), each of the PBS traces taken from Fig.~\ref{fig:CPE_Phase} (grey lines), and a simulated fit to the sheep data (red trace).
-Error bars have been placed one standard deviation either side of the mean for measured data.}}
+    \caption{Comparison of the mean phase response of measured displacement currents in live sheep (blue trace), each of the PBS traces taken from Fig.~\ref{fig:CPE_Phase} (grey lines), and a simulated fit to the sheep data (red trace).
+Error bars have been placed one standard deviation either side of the mean for measured data.}
     \label{fig:displacement_sheepCPEPhase}
@@
 We have measured how changing the concentration of PBS affects the parameters of this model.
-We have drawn direct relationships with concentration {\color{blue} and conductivity} sufficient to predict interface characteristics at arbitrary dilutions of PBS.
+We have drawn direct relationships with concentration and conductivity sufficient to predict interface characteristics at arbitrary dilutions of PBS.
 We found that the magnitude of the CPE element moves much more slowly with concentration whereas the resistance moved almost linearly.
-Using DC measurements we conclude that the {\color{blue} concentration of PBS has no effect on the onset of Faradaic conduction for the range of concentrations {\color{blue} measured}.} We hypothesise that this is because the double-layer sets the effective concentration of ions{\color{blue}, those involved in the Faradaic reactions,} in a localised volume surrounding each electrode.
+Using DC measurements we conclude that the concentration of PBS has no effect on the onset of Faradaic conduction for the range of concentrations measured.
+We hypothesise that this is because the double-layer sets the effective concentration of ions those involved in the Faradaic reactions, in a localised volume surrounding each electrode.
 
 In-vivo measurements of platinum electrodes in sheep spine show that no single concentration of PBS matches both the CPE and the resistive characteristics at once.
-{\color{blue} These measurements also reveal a considerable amount of reactance (see transimpedance measurements in vivo) that is captured neither by PBS nor the model presented when using a purely resistive spreading resistance.} Nevertheless, {\color{blue}if a single solution of PBS is to be used as a human phantom, a one-tenth concentration solution (by mass)} is a good compromise.
+These measurements also reveal a considerable amount of reactance (see transimpedance measurements in vivo) that is captured neither by PBS nor the model presented when using a purely resistive spreading resistance.
+Nevertheless, a single solution of PBS is to be used as a human phantom, a one-tenth concentration solution (by mass) is a good compromise.
 
-{
-    \color{blue}
     While the model used is limited to predicting only the onset of Faradaic current conduction, it usefully captures the transition into this biologically destructive stimulus regime sufficient for it to be avoided.
 
-    {\color{blue}The final model, including 205 lines of resistive mesh, is represented by a SPICE netlist comprised of 348 lines.
-Simulation of this model, using the freely available ngSpice circuit simulator, at 1000 frequencies takes approximately 1 second on a modern CPU.}
-}
+final model, including 205 lines of resistive mesh, is represented by a SPICE netlist comprised of 348 lines.
+Simulation of this model, using the freely available ngSpice circuit simulator, at 1000 frequencies takes approximately 1 second on a modern CPU.
 
@@
 The authors acknowledge The University of Waikato for financial support and Saluda Medical for the use of facilities and equipment.
-{\color{blue}Special thanks are expressed to Peter Single of Saluda Medical for help conducting in-vivo measurements.}
+Special thanks are expressed to Peter Single of Saluda Medical for help conducting in-vivo measurements and to the anonymous reviewer whose detailed comments lead to a much more rigorous manuscript.
 
@@
 
-\section*{Reviewers' Comments to the Authors:}
-
-\subsection*{Reviewer: 1}
-
-Comments to the Author
-
-{
-    \color{OliveGreen}
-    My comments have been sufficiently addressed.
-}
-
-{
-    \color{blue}
-    Thank you.
-}
-
-\subsection*{Reviewer: 2}
-
-Comments to the Author
-
-{
-    \color{OliveGreen}
-    Required modification done and manuscript now significantly improved.
-}
-
-{
-    \color{blue}
-    Thank you.
-}
-
-\subsection*{Reviewer: 3}
-
-Comments to the Author
-
-{\color{OliveGreen}
-    I am sorry to say that the revised version of the paper is still quite unsatisfactory.
-You have added electrochemical reactions (5)-(9) but do not acknowledge that these all have different reaction potentials, will have different charge transfer coefficients ( alpha in the Butler Volmer equation http://en.wikipedia.org/wiki/Butler\%E2\%80\%93Volmer\_equation), and will by limited by mass transfer to different extents.
-Therefore the use of diodes in the model is not obviously appropriate.
-
-    {
-        \color{blue}
-        The diodes are there to model the change in current attributed to the first biologically damaging reaction that occurs at the electrode-electrolyte interface.
-Whatever reaction occurs first in the relevant electrolyte is the reaction that diode aims to mimic.
-We observe that the current increases near exponentially around this point so we use a diode to mimic that.
-We expect this reaction may not be the same in-vivo as it is in-vitro but the properties of a diode can be altered to match the situation.
-
-        For secondary reactions occurring at higher potentials, a second pair of diodes with the properties of that specific reaction can be added.
-The problem here is that memristors will be needed (as used in ScottSingle2013) to account for reactant depletion.
-We don't account for reactant depletion for the same reason we don't account for reactions other than the onset of the first Faradaic reaction(s) taking place.
-The reason is that we never want biologically damaging reactions to occur due to an implant, so if they happen then something has gone wrong.
-
-        Think of our model of Faradaic reactions as a ``you've pushed this too far'' indicator for an electrical engineer.
-
-        We have added a statement to address this concern directly after equations 5--9 in section \ref{sect:faradaic}.
-    }
-
-    My interpretation of your data in Fig 10 is this.
-Above 1.05V, the electrolysis reactions (6) and (7) are occurring and the current will partly depend on the conductivity (therefore concentration) of the electrolyte.
-Below about 1.05V, the direct current may indeed be due to oxygen reduction at the cathode and oxygen evolution at the anode, which you cite (page 1, col 2, line 53) from ref 10 (c.f.
-Clark Oxygen Electrode).
-In that case, dissolved oxygen will have to diffuse to the cathode because it is not charged, so this will be diffusion-limited, which explains why the current is independent of concentration.
-Maybe you disagree with me but it is unsatisfactory that this is speculative and no doubt you will say that you did not want to get involved in electrochemistry, you just wanted to construct a model.
-
-    {
-        \color{blue}
-        That is correct, we are not aiming to determine what is happening at the electrode surface.
-We have a flexible model that can be used to simulate interfacial impedance and we use this model to compare this impedance for electrodes in various electrolytes.
-If the solution changes, the reactions change.
-Since we are only interested in the onset of Faradaic conduction, and we expect this to change when we move to different solutions, we do not want to rely on the exact electrochemistry at play.
-
-    }
-
-    Even as a model, however, your case is not very convincing.
-
-    1.
-You state in the Introduction that you aim for a model suitable for stimulation yet there are no results comparing the model with experiment when the electrodes are used in this way.
-All the results are with sinusoidal excitation (which are of low amplitude at high frequencies), or DC with steps.
-
-    {
-        \color{blue}
-        This is a good point.
-ScottSingle2013 compare the models prediction to stimulus waveforms.
-Our aim is to capture how the model parameters change as the concentration of PBS is varied and to compare those changes to parameters obtained from in-vivo measurements using a live sheep.
-We're doing this because 0.1X PBS is commonly used as a phantom for real spine.
-There hasn't been an objective way of determining how accurate that assumption was until we used the model to make this comparison.
-In future we hope to match it against in-vivo stimulus waveforms; at present it is out of scope.
-    }
-
-    2.
-Your model of the interface (Fig 2) has a series resistor Rs.
-I do not see why you need this and how you can measure it: how do you separate it from the volume resistance (``Resistive Network'')?
-(You mention this on p3 col 1, line 55 without casting any light.)
-
-    {
-        \color{blue}
-        We need this because it represents the resistance seen by charge crossing the interface, separate from that of the fluid.
-        We measure the impedance magnitude of the displacement currents at high frequency (flattened part of Fig.
-5).
-For each concentration the impedance magnitude at 10kHz is higher than is predicted by the transimpedance measurements made in Fig.
-3.
-The transimpedance measurements do not measure impedance across an interface that is passing current and therefore any voltage drop across an interface due to $R_{S}$ vanishes.
-The displacement measurements take the voltage across interfaces that are passing stimulus currents.
-These measurements see the potential drop across the interface due to the current flow (because of Ohms law).
-
-        The transimpedance measurements give us an inter-electrode resistance.
-The displacement measurements at high frequency give us an inter-electrode impedance plus an interface impedance.
-Subtracting one from the other gives us a value of resistance that only appears as we pass current through an interface, which we include as $R_{S}$.
-We have added a paragraph at the end of Section \ref{sect:resistorMesh} to clarify the purpose of $R_{S}$.
-    }
-
-    3.
-The maximum charge limit for Pt was given by Brummer \& Turner (IEEE Trans BME, 24, 436-9, 1977) as 320 microcoulombs per cm\^2, and later authors revised this downward.
-If you really applied the charge density that you show in Fig 4, you exceeded this limit at frequencies below ~50Hz and I would expect that your electrodes would have been gassing.
-In that case it is surprising that the impedance curves in Figs 5 \& 6 do not show a deviation from pure CPE behaviour.
-This is an important anomaly.
-
-    {
-        \color{blue}
-        That is interesting and definitely important to our modelling work.
-We had presented the charge injected in terms of the geometric surface area of each electrode which we know is less than the real (or effective) surface area, estimated to be $14\thinspace mm^{2}$.
-Calculating the charge injection using the effective surface area is more relevant here and gives results consistent with Brummer \& Roblee (Annals New York Academy of Sciences, 159-171, 1983), who also express their values in terms of ``real'' area.
-
-    }
-
-    4.
-The time constants seen in Figs 8, 9 \& 11 are interesting.
-Fig 11 shows that the model does not fit well because its time constant is too short.
-But is this surprising?
-Your impedance spectra go down to 0.05Hz (Figs 4-6) and I suppose that you chose RC pairs for your CPE model that go down to that frequency.
-But that is only to a time constant of ~3s (1/2*pi*f) which is much less that the 250s in Fig 8.
-It would be interesting to know whether, if you extended the spectrum far enough down, the time constants from step changes to the RC network that approximates the CPE would be similar to those seen in Fig 8.
-
-    {
-        \color{blue}
-        The RC pairs are generated via a Python script for a given frequency range.
-The frequency range supplied for all simulations in this manuscript was 1.0 nHz to 1.0 GHz with R-C pairs spaced 3 per decade.
-Adding more pairs than necessary came at negligible computation cost and having the circuit generated in an automated fashion adds no extra work.
-Extending the CPE's R-C pairs into the lower frequency area did not improve the fit.
-We suspect there is another mechanism at play here.
-        We would also like to note that the effect of the CPE is far from that of a simple capacitor, i.e.
-far from being exponential.
-This is part of the reason they are so difficult to simulate in a compact circuit simulator.
-    }
-
-    5. p 6, col 1, line 11. ``rate dependent on the log'' should be ``rate varies exponentially''. i.e. Tafel equation.
-
-    {
-        \color{blue}
-        Correct, change made.
-    }
-
-    6.
-Figs 14 \& 15 are intriguing.
-For reason given in 3 above, I discount the results below 50Hz, yet it does look as if the slope of the CPE is the same in vivo but with an offset that would correspond to a very weak solution of PBS.
-As far as I know, there is no satisfactory explanation yet for the CPE so perhaps this is a significant clue.
-
-    {
-        \color{blue}
-        Yes you are quite right.
-We think the results of the CPE in-vivo vs.
-PBS are intriguing in light of what the previous literature would have you expect.
-We also know of no satisfactory explanation of what the CPE actually is.
-One of the authors came up against this uncertainty while writing \cite{ScottSingle2013}.
-
-        We feel that the in-vivo results will be affected by the significant inhomogeneity of real spine by proximity of bone, change in fluid at dura, etc.
-Perhaps you may know of a way to clarify this issue?
-    }
-
-}
-
-\subsection*{Reviewer: 4}
-
-Comments to the Author
-
-{
-    \color{OliveGreen}
-    In this manuscript, the authors studied the impedance of a commercial electrode array as a function of concentration of phosphate buffered saline (PBS), both through simulation and empirical measurements, and compared those results to the impedance measured when the electrode array was implanted into a sheep's spinal cavity.
-From this comparison, they concluded that the current practice of testing spinal cord stimulator in 0.1x of physiologically normal saline is adequate but suggest that no single concentration of PBS captures the frequency dependence of the in vivo measured impedance.
-Although not a very compelling conclusion, this manuscript does provide value to the field as a single source for creation of a compact, SPICE model of an electrode.
-Hence, my review is cast in the light of using this paper as a guide in developing a model of a different electrode.
-
-    1. As much of the paper involves development of the model, I recommend that the authors add some reference to modeling in the abstract.
-
-    {
-        \color{blue}
-        Of course, see amended abstract.
-    }
-
-    2.
-Sections 2, 3, and 4 detail the measurement and simulation of measurements of parameters associated with the bulk solution, CPE and Rs, and the diodes of the model in Figure 2.
-I recommend that the authors expand the introduction to explain this organization to help the reader's understanding.
-Additionally, I propose that the authors expand the section headings to include this information.
-
-    {
-        \color{blue}
-        An extra paragraph explaining the layout of the paper has been added to the end of the introduction.
-Also, section headings have been expanded slightly to include the names of relevant model elements as per your recommendation.
-    }
-
-    3.
-The parameters provided in Table II include reference to an unexplained term sigma ($\sigma$).
-I presume this is the conductivity of saline (correct symbol and units for conductivity).
-For completeness, I recommend the authors explain this term, provide the numeric value (or values) that they used, provide how they adjusted this with concentration, and reference the source of their numeric data.
-
-    {
-        \color{blue}
-        The title of Table \ref{tab:RESparams} has been amended to make use of the term sigma ($\sigma$) as electrolyte conductivity clear.
-The source of conductivity measurements has been added at the end of the second to last paragraph of Section \ref{sect:resistorMesh}.
-    }
-
-    4.
-From the parameters provided in Table II, I can guess how many elements are in the SPICE model arising from these parameters but it would be much more valuable to the reader to have a clear statement of the true size of the associated SPICE model.
-I recommend the authors provide a clear statement at the end of this section of how many resistors are in their SPICE model as a result of this parameterization.
-
-    {
-        \color{blue}
-        A diagram showing the layout of the resistor mesh has been added along with the total number of resistors in the mesh for an 8 electrode system in Section \ref{sect:resistorMesh}.
-    }
-
-    5.
-In Section 3, the authors state that the CPE is modeled as an array of R-C branches but at no time do they state the actual number of branches used in their model.
-I recommend the authors provide a clear statement at the end of this section of how many capacitors and resistors are in their SPICE model because of this parameterization.
-
-    {
-        \color{blue}
-        A statement as recommended has been added to Section \ref{sect:cpe} detailing the number of R-C branches and the total number of elements in the CPE model.
-    }
-
-    6.
-The parameters provided in Table II include reference to `concentration'.
-As different readers will have different interpretations (mass concentration=0.9\%, molar concentration = 0.154M), I recommend the authors clearly explain the meaning of this term.
-
-    {
-        \color{blue}
-        Table \ref{tab:CPEparams} has been amended to include mention of 'concentration' being that of mass concentration of PBS.
-Also, clarification of this concentration (by mass) has been added throughout the paper where appropriate.
-    }
-
-    7.
-Given the authors details 3 different parts of their model in Sections 2, 3, and 4, I found it surprising that they only chose to characterize CPE in their in vivo experiment.
-In other words, if the complete model is important to performing simulation studies of a stimulation system, why did they not do such in their in vivo model and how valuable is their conclusion regarding the applicability of using 0.1xPBS as an in vitro of an animal.
-At minimum, I recommend the authors explain why they only characterized CPE in vivo.
-
-    {
-        \color{blue}
-        That is a very important piece of information we've missed!
-Thank you for bringing that to our attention.
-We have revised Section \ref{sect:in-vivo} to more fully explain and bring in more in-vivo measurements.
-    }
-
-    8.
-In the conclusions, I recommend the authors provide details on the overall size of their SPICE model.
-Knowing this information, a reader can compare the compactness of the complete model to that of using a finite element model.
-
-    {
-        \color{blue}
-        Following your recommendation a paragraph has been added to the end of the conclusion stating the model size and approximate execution speed.
-    }
-
-    9.
-In their conclusions, I recommend the authors restate any limitations in their model that they mentioned earlier in the text (e.g., 0.9v limitation) and provide an honest discussion regarding the limits of their model.
-    {
-        \color{blue}
-        The 0.9V limitation is rather arbitrary as it was specific to the use of electrodes 2 and 7.
-We have instead clarified that the model only captures the onset of Faradaic conduction sufficient for it to be avoided (this has been done throughout the paper).
-This limitation has been brought up in the conclusion.
-    }
-}
-
 \end{document}

### 2014-06-25 paper.tex
Added two new references from TBioCas as requested

@@
 
-\IEEEPARstart{T}{here} is considerable interest in the electrical modelling of electrodes. \cite{Cogan2008,Troy2006}
+\IEEEPARstart{T}{here} is considerable interest in the electrical modelling of electrodes. \cite{Cogan2008,Brown2008,Guo2012,Troy2006}
 In \cite{Franks2005} a linearised model was presented, and in \cite{ScottSingle2013} a non-linear model
@@
 
+\bibitem{Brown2008}
+    Edgar~A.~Brown, James~D.~Ross, Richard~A.~Blum, Yoonkey~Nam, Bruce~C.~Wheeler and Stephen~P.~DeWeerth,
+    ``Stimulus-Artifact Elimination in a Multi-Electrode System'',
+    {\em IEEE Transactions on Biomedical Circuits and Systems},
+    vol.~2 no.~1, March 2008, pp10--21.
+
+\bibitem{Guo2012}
+    Jing~Guo, Jie~Yuan and Mansun~Chan,
+    {\em IEEE Transactions on Biomedical Circuits and Systems},
+    vol.~6 no.~6, December 2012, pp605--613.
+
 \bibitem{Franks2005}

### 2014-06-25 paper.tex
Added new reference and example in introduction

@@
 
+\usepackage[utf8]{inputenc}
 \usepackage{cite}
@@
 In \cite{Franks2005} a linearised model was presented, and in \cite{ScottSingle2013} a non-linear model
-suitable for use with the SPICE circuit simulator was presented. The SPICE model usefully characterises an electrode in a given electrolyte with a small number of parameters.
+suitable for use with the SPICE circuit simulator was presented.
+The SPICE model usefully characterises an electrode in a given electrolyte with a small number of parameters.
 One major reason for the interest in the electrical impedance of electrodes concerns the design of electronics intended for integration into pacemakers, cochlear implants, spinal cord stimulators, etc.
@@
 Having a compact model of an electrode in the appropriate electrolyte allows circuit designers to simulate their designs with valid loads.
+{
+    \color{blue}
+For example, the authors of \cite{Ethier2011} are concerned with the impedance presented by their electrode loads, and calculate power efficiency of their circuits.
+This value is affected by the load impedance assumed.
+Nevertheless, it is clear that they do not have a good idea of, nor a good way to simulate with, the load truly presented by an electrode in vivo or in vitro.
+}
 Knowing the effect upon the model of changes in the electrode or electrolyte would allow designers to anticipate circumstances that will affect the load seen by their circuits.
+
 Another appeal of a compact model stems from the fact that electrode characteristics are succinctly and objectively represented by the model parameters.
@@
 Using DC measurements we conclude that the concentration of PBS has no effect on the onset of Faradaic conduction for the range of concentrations measured.
-We hypothesise that this is because the double-layer sets the effective concentration of ions those involved in the Faradaic reactions, in a localised volume surrounding each electrode.
+We hypothesise that this is because the double-layer sets the effective concentration of the species involved in the Faradaic reactions, in a localised volume surrounding each electrode.
 
@@
 
-final model, including 205 lines of resistive mesh, is represented by a SPICE netlist comprised of 348 lines.
+The final model, including 205 lines of resistive mesh, is represented by a SPICE netlist comprised of 348 lines.
 Simulation of this model, using the freely available ngSpice circuit simulator, at 1000 frequencies takes approximately 1 second on a modern CPU.
@@
     to be published in
-    {\em IEEE Transactions on Biomedical Circuits and Systems},
+    \emph{IEEE Transactions on Biomedical Circuits and Systems},
     DOI: 10.1109/TBCAS.2013.2270179, 2013.
+
+\bibitem{Ethier2011}
+    Sébastien Ethier and Mohamad Sawan,
+    ``Exponential Current Pulse Generation for Efficient Very High-Impedance Multisite Stimulation'',
+    \emph{IEEE Transactions on Biomedical Circuits and Systems},
+    vol.~5 no.~1, February 2011, pp30--38.
 

### 2014-06-26 paper.tex
Edits

@@
 
-\IEEEPARstart{T}{here} is considerable interest in the electrical modelling of electrodes. \cite{Cogan2008,Brown2008,Guo2012,Troy2006}
-In \cite{Franks2005} a linearised model was presented, and in \cite{ScottSingle2013} a non-linear model
-suitable for use with the SPICE circuit simulator was presented.
+\IEEEPARstart{T}{here} is considerable interest in the electrical modelling of electrodes.~\cite{Cogan2008,Brown2008,Guo2012,Troy2006}
+In \cite{Franks2005} a linearised model was presented, and in \cite{ScottSingle2013} a non-linear model suitable for use with the SPICE circuit simulator was presented.
 The SPICE model usefully characterises an electrode in a given electrolyte with a small number of parameters.
@@
 Having a compact model of an electrode in the appropriate electrolyte allows circuit designers to simulate their designs with valid loads.
-{
-    \color{blue}
 For example, the authors of \cite{Ethier2011} are concerned with the impedance presented by their electrode loads, and calculate power efficiency of their circuits.
@@
 Nevertheless, it is clear that they do not have a good idea of, nor a good way to simulate with, the load truly presented by an electrode in vivo or in vitro.
-}
 Knowing the effect upon the model of changes in the electrode or electrolyte would allow designers to anticipate circumstances that will affect the load seen by their circuits.
@@
 
-The electrode used in this work is a commercial linear array of eight platinum electrodes, called an ``Octrode'', intended for Spinal Cord Stimulator (SCS) implantation.~\cite{StJudeOctrode} A picture of an Octrode is presented in Fig.~\ref{fig:octrode}.
+The electrode used in this work is a commercial linear array of eight platinum electrodes, called an ``Octrode'', intended for Spinal Cord Stimulator (SCS) implantation.~\cite{StJudeOctrode}
+A picture of an Octrode is presented in Fig.~\ref{fig:octrode}.
 A solution of phosphate buffered saline (PBS) diluted to one-tenth concentration (0.1X) is commonly used as a crude phantom in the case of SCS, while full concentration (1.0X) PBS is considered more representative of the situation in blood.
@@
 
-It has been suggested that the primary coupling mechanism between platinum electrodes and physiological saline is the reversible evolution of gas, probably oxygen, at the platinum surface, which dissolves without bubble formation.\cite{Greatbatch1969} Understanding the exact mechanism of displacement or Faradaic charge transfer at the electrode surface is beyond the scope of this work.
+It has been suggested that the primary coupling mechanism between platinum electrodes and physiological saline is the reversible evolution of gas, probably oxygen, at the platinum surface, which dissolves without bubble formation.~\cite{Greatbatch1969}
+Understanding the exact mechanism of displacement or Faradaic charge transfer at the electrode surface is beyond the scope of this work.
 Rather, we wish to characterise the electrode-electrolyte interface using a small number of parameters that can be fed into an electrical model.
@@
 Displacement currents are responsible for capacitive behaviour at interfacial boundaries.
-They are brought about by the redistribution of charge in response to applied fields, e.g., a charged electrode will attract or repel $Cl^{-}$ from its surface and reorientate polar molecules in the surrounding solution.\cite{Merrill05} This capacitive behaviour may also be the result of electrode polarisation in the form of reversible Faradaic reactions at the surface of the electrode.
+They are brought about by the redistribution of charge in response to applied fields, e.g., a charged electrode will attract or repel $Cl^{-}$ from its surface and reorientate polar molecules in the surrounding solution.
+\cite{Merrill05}
+This capacitive behaviour may also be the result of electrode polarisation in the form of reversible Faradaic reactions at the surface of the electrode.
 Such reactions involving water and platinum, as identified in \cite{Horch2004,Mohtashami2011,Merrill05}, include:
@@
 Using DC measurements we conclude that the concentration of PBS has no effect on the onset of Faradaic conduction for the range of concentrations measured.
-We hypothesise that this is because the double-layer sets the effective concentration of the species involved in the Faradaic reactions, in a localised volume surrounding each electrode.
+We hypothesise that this is because the double-layer sets the concentration of species involved in the Faradaic reactions within a volume surrounding each electrode.
 
-In-vivo measurements of platinum electrodes in sheep spine show that no single concentration of PBS matches both the CPE and the resistive characteristics at once.
+In-vivo measurements using platinum electrodes in sheep spine show that no single concentration of PBS matches both the CPE and the resistive characteristics at once.
 These measurements also reveal a considerable amount of reactance (see transimpedance measurements in vivo) that is captured neither by PBS nor the model presented when using a purely resistive spreading resistance.
-Nevertheless, a single solution of PBS is to be used as a human phantom, a one-tenth concentration solution (by mass) is a good compromise.
+Nevertheless, if a single solution of PBS is to be used as a human phantom, a one-tenth concentration solution (by mass) is a good compromise.
 
@@
 The final model, including 205 lines of resistive mesh, is represented by a SPICE netlist comprised of 348 lines.
-Simulation of this model, using the freely available ngSpice circuit simulator, at 1000 frequencies takes approximately 1 second on a modern CPU.
+A simulation of this model, using the freely available ngSpice circuit simulator, at 1000 frequencies takes approximately 1 second on a modern CPU.
 
@@
 
-%\bibitem{Weiland2000}
-%    Weiland~James~D. and Anderson~David~J.,
-%    ``Chronic Neural Stimulation with Thin-Film, Iridium Oxide Electrodes'',
-%    {\em IEEE Transactions on Biomedical Circuits and Systems},
-%    vol.~47 no.~7, July 2000, pp911--918
-
 \end{thebibliography}

### 2014-06-26 paper.tex
Cleaned up graphics folder

@@
 Section \ref{sect:resistorMesh} details the measurement of the inter-electrode resistances (arising from the bulk resistance of the solution) and the generation of a resistor network to replicate these resistances.
-
 Sections \ref{sect:cpe} and \ref{sect:faradaic} are concerned with the measurement and parameter fitting of displacement currents and Faradaic currents, respectively, across the electrolyte interface.
@@
 
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{graphics/MarkJones-Aug13.jpg}}]{Mark Jones}
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{graphics/MarkJones-Aug13.png}}]{Mark Jones}
 received the B.Sc. degree in Physics in 2008 and the M.E. degree in Microwave Electronics in 2009 from The University of Waikato, Hamilton, New Zealand.
@@
 
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{graphics/JBSatNICTA.jpg}}]{Jonathan Scott}
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{graphics/JBSatNICTA.png}}]{Jonathan Scott}
 (M'80--SM'99) is the Foundation Professor in
